---
title: "st_408"
output: html_notebook
---

Written by Aunoy Poddar
July 21st, 2022

# Process the puncta quantified raw data
```{r eval=FALSE}
current_file <- rstudioapi::getActiveDocumentContext()$path
output_file <- stringr::str_replace(current_file, '.Rmd', '.R')
knitr::purl(current_file, output = output_file)
file.edit(output_file)
```

## Import packages and functions
```{r}
library(Seurat)
library(tictoc)
library(ggplot2)
library(patchwork)
library(pheatmap)
library(RColorBrewer)
library(tidyverse)
library(gridExtra)
library(png)
library(cowplot)
library(magick)
library(scales)
```

## Load the data
```{r}
data_dir = '/home/aunoy/st/arc_profiling/st_analysis/hand_annotated_data/rethresholded'
meta_dir = '/home/aunoy/st/arc_profiling/st_analysis/hand_annotated_data/overlay'
output_dir_plot = '/home/aunoy/st/arc_profiling/st_analysis/results/plots'
output_dir_tbls = '/home/aunoy/st/arc_profiling/st_analysis/results/tables'
```


### Merge both datasets and generate a metadata column that corresponds
### to the cell #
```{r}
df_408 = data.frame()
for (file_name in list.files(data_dir)){
  print(file_name)
  if(grepl('164', file_name)){
    next
  }
  #if(grepl('408_TC', file_name) | grepl('408_vMS', file_name)){
  #  next
  #}
  df_to_append <- read.table(file.path(data_dir, file_name), sep = ',', header = TRUE)
  while(length(ind <- which(df_to_append$Image.Name == "")) > 0){
    df_to_append$Image.Name[ind] <- df_to_append$Image.Name[ind -1]
  }
  
  colnames(df_to_append) <- toupper(colnames(df_to_append))
  df_to_append <- df_to_append %>%
    mutate(area = strsplit(file_name, '.csv')[[1]])
  
  ## Add relative_XY_position
  
  if(!is_empty(df_408)){
    df_to_append <- df_to_append %>%
          dplyr::select(colnames(df_408))
  }
  df_408 <- rbind(df_408, df_to_append)
}
```
```{r}
df_408$IMAGE.NAME = unlist(lapply(df_408$IMAGE.NAME, gsub, pattern='_Cluster', replacement=''))
df_408$IMAGE.NAME = unlist(lapply(df_408$IMAGE.NAME, gsub, pattern='[*]', replacement=''))
df_408$IMAGE.NAME = unlist(lapply(df_408$IMAGE.NAME, gsub, pattern='X', replacement=''))
df_408$IMAGE.NAME = unlist(lapply(df_408$IMAGE.NAME, gsub, pattern='L2_', replacement='L2-'))
df_408$IMAGE.NAME = unlist(lapply(df_408$IMAGE.NAME, gsub, pattern='-L2', replacement='_L2'))
df_408$IMAGE.NAME = unlist(lapply(df_408$IMAGE.NAME, gsub, pattern='Tc_12', replacement='TC_12'))
## Missing
df_408 = df_408[df_408$IMAGE.NAME != 'Layer1', ]
df_408 = df_408[df_408$IMAGE.NAME != 'TC_1', ]
df_408 = df_408[df_408$IMAGE.NAME != 'TC_18', ]
df_408 = df_408[df_408$IMAGE.NAME != 'TC_19', ]
#df_408$IMAGE.NAME = toupper(df_408$IMAGE.NAME)
unique(df_408$IMAGE.NAME)
```
## Now we know that everything is equal to one another, we should load the variable

```{r}
images_ordered = c('TC_20', 'TC_17', 'TC_16', 'TC_15', 'TC_14', 'TC_13', 'TC_12', 'TC_11', 'TC_10', 'TC_9', 'TC_8', 'TC_7', 'TC_6', 'TC_5',
                   'TC_4', 'TC_3', 'TC_2', 'CC_4', 'CC_5', 'CC_6', 'CC_7', 'CC_8', 'CC_9', 'CC_10', 'CC_11', 'CC_12', 'CC_L2-3', 'CC_L2-2', 'CC_L2-1', 'CC_Cortical1', 'CC_Cortical2')
```

```{r}
x_horz = 1:length(images_ordered) * 35
y_horz = rep(0, length(images_ordered))
horz_embedding = data.frame()
df_408$X_horz = -1
df_408$Y_horz = -1
IMAGE_SIZE = 1024
## This is the size of an image in the global coordinate space
IMAGE_LEN = 25

images = list.files(meta_dir)
for(i in 1:length(images_ordered)){
    image_name = images_ordered[i]
    print(image_name)
    split_names = strsplit(image_name, '_')
    cortex = toupper(split_names[[1]][1])
    number = split_names[[1]][2]
    number_csv = paste0('_', number, '.csv')
    filename = images[grepl(cortex, images) & grepl(number_csv, images) & grepl('408', images)]
    coordinates = read.table(file.path(meta_dir, filename), sep = ',', header = TRUE)
    ## checked already that lists are equal, missing 1, 18, 19 for now, layer 1 and others
 
    ## so this is a little tricky, so need to get it right
    ## Remember, it is the top right that the coordinate is coming from, but
    ## the bottom right is the new coordinate space.
    ## so first when we get the original coordinate space, to set to relative
    ## of bottom would be the same X, but 1024 - Y
    
    ## push out the coordinates for better visualization
    #x_repelled <- (512 - coordinates$X_Coordinate_In_pixels)
    
    
    df_408[df_408$IMAGE.NAME == image_name, 'X_horz'] = (coordinates$X_Coordinate_In_pixels / 
                                                      IMAGE_SIZE * IMAGE_LEN) + y_horz[i]
    df_408[df_408$IMAGE.NAME == image_name, 'Y_horz'] = ((1024-coordinates$Y_Coordinate_In_pixels) / 
                                                      IMAGE_SIZE * IMAGE_LEN) + x_horz[i]
}
```

## We have the coordinates for 408_TC and others
```{r}
rownames(df_408) = 1:nrow(df_408)
jy_408 = df_408 %>%
  dplyr::select(-c(area, IMAGE.NAME, X_horz, Y_horz)) %>%
  t() %>%
  CreateSeuratObject()
```

## just set everything from below 1 in ratio to zero
```{r}
jy_408 <- NormalizeData(jy_408, scale.factor = 1e5) ###
normed = GetAssayData(jy_408, slot = 'data')
normed[normed < 3] = 0
jy_408 <- SetAssayData(jy_408, slot = 'data', normed)
```

```{r}
jy_408$gad1_true = normed['GAD1',] != 0 #& normed['SATB2',] == 0
```

```{r}
DimPlot(jy_408, #cells = grepl('CC', df_408$area), 
        cols = c('purple', 'grey'), reduction = "XY", pt.size = 0.2, group.by = 'gad1_true', order = which(jy_408$gad1_true)) + coord_fixed(ratio = 1)
```
```{r}
jy_408 <- FindVariableFeatures(jy_408, selection.method = "vst")
all.genes <- rownames(jy_408)
jy_408 <- ScaleData(jy_408, features = all.genes)
jy_408 <- RunPCA(jy_408, approx = FALSE)
jy_408 <- FindNeighbors(jy_408, dims = 1:30)
jy_408 <- FindClusters(jy_408, resolution = 1.5)
jy_408 <- RunUMAP(jy_408, dims = 1:30)

DimPlot(jy_408,  reduction = "umap", group.by = 'seurat_clusters') + NoAxes()
```

```{r}
DimPlot(jy_408, reduction = "H", pt.size = 1, split.by = 'seurat_clusters') + NoAxes() + NoLegend()
```
```{r}
jy_408.markers <- FindAllMarkers(jy_408, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
jy_408.markers %>%
   group_by(cluster) %>%
   slice_max(n = 32, order_by = avg_log2FC)
```
```{r}
jy_408_0v4.markers <- FindMarkers(jy_408, ident.1 = 10, ident.2 = 9, only.pos = TRUE)
# view results
head(jy_408_0v4.markers)
```


```{r}
breakpoints = 1:20/10+0.3
plots = list()
jy_408 <- FindNeighbors(jy_408, dims = 1:30)
i = 1
for (breakpoint in breakpoints){
  jy_408 <- FindClusters(jy_408, resolution = breakpoint)
  jy_408 <- RunUMAP(jy_408, dims = 1:30)
  jy_408.markers <- FindAllMarkers(jy_408, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
  labels = jy_408.markers %>%
   group_by(cluster) %>%
   slice_max(n = 1, order_by = avg_log2FC)
  new.cluster.ids <- labels$gene
  names(new.cluster.ids) <- levels(jy_408)
  jy_408 <- RenameIdents(jy_408, new.cluster.ids)
  plots[[i]] = DimPlot(jy_408, reduction = "umap", pt.size = 1, label = TRUE) + NoAxes() + NoLegend() + ggtitle(breakpoint)
  i = i + 1
}

marrangeGrob(plots, nrow=2, ncol=2)
ml <- marrangeGrob(plots, nrow=2, ncol=2)
ggsave(filename = '408_sequential_clustering_umaps.pdf', path = file.path(output_dir_plot, '20220721_1'), ml)
```

```{r}
plot_features_umap <- function(sobj, gene, pt.size = 3, space = "umap")
{
  coordinates <- Embeddings(sobj, reduction = space)
  expmat <- as.matrix(FetchData(sobj, gene))
  gene_df <- as.data.frame(cbind(coordinates, expmat))
  colnames(gene_df) <- c('X', 'Y', 'expr')
  gene_df <- gene_df %>% dplyr::arrange(!is.na(expr), expr)
  colors = c('grey90', 'grey90', '#CB2A55')
  gene_df$expr[gene_df$expr == 0] = NA
  plot <- ggplot(gene_df, aes(x = X, y = Y, color = expr)) + geom_point(size = pt.size, alpha = 0.8)+  
            theme_classic() + ggtitle(gene) + NoAxes() + NoLegend() +  scale_color_gradient(na.value = colors[1], low = colors[2], high = colors[3], labels = NULL)  + theme(title = element_text(face = 'bold', size = rel(1), hjust = 1)) 
  return(plot)
}
plot_features_umap(jy_408, 'VIP')
```
```{r fig.height=8, fig.width=18}
genes = rownames(jy_408)
plots <- lapply(1:length(genes), function(i){
    plot_features_umap(jy_408, genes[i], pt.size = 1)
  })
umaps = plot_grid(plotlist = plots, label_size = 10)
ggsave(plot = umaps, filename = 'test_408_umapl_expr_plots_size1_alpha1.png', path = file.path(output_dir_plot, '20220721_1'), width = 18, height = 8, dpi = 150)

```
```{r}
plot_features_xy <- function(sobj, gene, pt.size = 12, space = "XY")
{
  coordinates <- Embeddings(sobj, reduction = space)
  expmat <- as.matrix(FetchData(sobj, gene))
  gene_df <- as.data.frame(cbind(coordinates, expmat))
  colnames(gene_df) <- c('X', 'Y', 'expr')
  gene_df <- gene_df %>% dplyr::arrange(!is.na(expr), expr)
  colors = c('grey90', 'grey90', '#CB2A55')
  gene_df$expr[gene_df$expr == 0] = NA
  plot <- ggplot(gene_df, aes(x = X, y = Y, color = expr)) + geom_point(size = pt.size, alpha = 0.8)+  
            theme_classic() + ggtitle(gene) + NoAxes() + NoLegend() +  scale_color_gradient(na.value = colors[1], low = colors[2], high = colors[3], labels = NULL)  + theme(title = element_text(face = 'bold', size = rel(1), hjust = 1)) 
  return(plot)
}
plot_features_xy(jy_408[,df_408$IMAGE.NAME == 'TC_1'], 'GSX2')
```
## Order the images
```{r}
unique(df_408$IMAGE.NAME)
images_ordered = c('TC_Cortical3', 'TC_Cortical2', 'TC_Cortical1', 'TC_10', 'TC_9', 'TC_8', 'TC_7', 'TC_6', 'TC_5', 'TC_4', 'TC_3', 'TC_2','TC_1','CC_2','CC_3',
           'CC_4', 'CC_5', 'CC_6', 'CC_7', 'CC_8', 'CC_9', 'CC_10',
           'CC_L2-1', 'CC_L2-2', 'CC_L2-3', 'CC_Cortical1', 'CC_Cortical2')
```

```{r}
x_horz = 1:length(images_ordered) * 35
y_horz = rep(0, length(images_ordered))
horz_embedding = data.frame()
df_408$X_horz = -1
df_408$Y_horz = -1

images = list.files(meta_dir)
for(i in 1:length(images_ordered)){
    image_name = images_ordered[i]
    print(image_name)
    split_names = strsplit(image_name, '_')
    cortex = toupper(split_names[[1]][1])
    number = split_names[[1]][2]
    number_csv = paste0('_', number, '.csv')
    filename = images[grepl(cortex, images) & grepl(number_csv, images) & grepl('164', images)]
    coordinates = read.table(file.path(meta_dir, filename), sep = ',', header = TRUE)
    if(image_name == "CC_L2-1"){
      coordinates = coordinates[c(1:37, 39:nrow(coordinates)), ]
    }
    ## checked already that lists are equal, missing 1, 18, 19 for now, layer 1 and others
 
    ## so this is a little tricky, so need to get it right
    ## Remember, it is the top right that the coordinate is coming from, but
    ## the bottom right is the new coordinate space.
    ## so first when we get the original coordinate space, to set to relative
    ## of bottom would be the same X, but 1024 - Y
    
    ## push out the coordinates for better visualization
    #x_repelled <- (512 - coordinates$X_Coordinate_In_pixels)
    
    
    df_408[df_408$IMAGE.NAME == image_name, 'X_horz'] = (coordinates$X_Coordinate_In_pixels / 
                                                      IMAGE_SIZE * IMAGE_LEN) + y_horz[i]
    df_408[df_408$IMAGE.NAME == image_name, 'Y_horz'] = ((1024-coordinates$Y_Coordinate_In_pixels) / 
                                                      IMAGE_SIZE * IMAGE_LEN) + x_horz[i]
}
```

```{r}
hcoords = df_408 %>% dplyr::select(c('X_horz', 'Y_horz')) %>% as.matrix()
colnames(hcoords) <- c('pixel_1', 'pixel_2')

jy_408[["H"]] <- CreateDimReducObject(embeddings = hcoords, key = "pixel_", assay = DefaultAssay(jy_408))
```

```{r}
plot_features_vertical_spatial <- function(sobj, gene, pt.size = 0.5, space = "H", arc = TRUE)
{
  coordinates <- Embeddings(sobj, reduction = space)
  expmat <- as.matrix(FetchData(sobj, gene))
  gene_df <- as.data.frame(cbind(coordinates, expmat))
  colnames(gene_df) <- c('X', 'Y', 'expr')
  gene_df <- gene_df %>% dplyr::arrange(!is.na(expr), expr)
  colors = c('grey90', 'grey90', '#0f4c5c')
  gene_df$expr[gene_df$expr == 0] = NA
  plot <- ggplot(gene_df, aes(x = X, y = Y, color = expr)) + geom_point(size = pt.size, alpha = 1)+  
            theme_classic() + ggtitle(gene) + NoAxes() + NoLegend() + 
    coord_fixed(ratio = 0.5) + scale_color_gradient(na.value = colors[1], low = colors[2], high = colors[3], labels = NULL)  + theme(title = element_text(face = 'bold', size = rel(0.5), hjust = 1)) 
  if(arc){plot = plot + geom_hline(yintercept=660, linetype = "dashed",color = colors[3])}
  return(plot)
}
plot_features_vertical_spatial(jy_408, gene = 'GSX2')
```

```{r}
plot_features_vertical_spatial_smoothed <- function(sobj, gene, pt.size = 0.5, space = "H", arc = TRUE)
{
  coordinates <- Embeddings(sobj, reduction = space)
  expmat <- as.matrix(FetchData(sobj, gene))
  gene_df <- as.data.frame(cbind(coordinates, expmat))
  colnames(gene_df) <- c('X', 'Y', 'expr')
  gene_df <- gene_df %>% dplyr::arrange(!is.na(expr), expr)
  colors = c('grey90', 'grey90', '#0f4c5c')
  gene_df$expr[gene_df$expr == 0] = NA
  plot <- gene_df %>%
    filter(!is.na(expr)) %>%
    ggplot(aes(x = X, y = Y, color = expr)) +stat_density_2d(aes(fill = ..density..), geom = "raster", n = 400,contour = FALSE, interpolate = TRUE) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
#geom_bin2d(bins = 10) + #geom_point(size = pt.size, alpha = 1)+  
            theme_classic() + ggtitle(gene) + NoAxes() + NoLegend() + 
    coord_fixed(ratio = 0.5) + scale_color_gradient(na.value = colors[1], low = colors[2], high = colors[3], labels = NULL)  + theme(title = element_text(face = 'bold', size = rel(0.5), hjust = 1)) 
  if(arc){plot = plot + geom_hline(yintercept=660, linetype = "dashed",color = colors[3])}
  return(plot)
}
plot_features_vertical_spatial_smoothed(jy_408, gene = 'PAX6')
```


```{r fig.height=8, fig.width=18}
genes = rownames(jy_408)
plots <- lapply(1:length(genes), function(i){
    plot_features_vertical_spatial_smoothed(jy_408, genes[i], pt.size = 1)
  })
verts= plot_grid(plotlist = plots, label_size = 10, nrow = 1)
verts
#ggsave(plot = verts, filename = 'test_408_vertical_expr_plots_size1_alpha1.png', path = file.path(output_dir_plot, '20220721_1'), width = 18, height = 8, dpi = 150)
```

## Do the clustering stuff here 
```{r}
plot_clusters_vertical_spatial <- function(sobj, cluster, clustering = NULL, anterior = FALSE, cluster_color =  '#CB2A55', pt.size = 1, space = "H", arc = TRUE)
{
  cluster_identity = as.numeric(unlist(ifelse(is.null(clustering),
                                              Idents(sobj),sobj[[clustering]]))) == (cluster)
  coordinates <- Embeddings(sobj, reduction = space)
  gene_df <- as.data.frame(cbind(coordinates, cluster_identity))
  colnames(gene_df) <- c('X', 'Y', 'clust')
  gene_df <- gene_df %>% dplyr::arrange(clust)
  plot <- ggplot(gene_df, aes(x = X, y = Y, color = factor(clust))) + geom_point(size = pt.size, alpha = 1) +  
            theme_classic() + ggtitle(cluster) + NoAxes() + NoLegend() + 
    coord_fixed(ratio = 0.5)  + theme(title = element_text(face = 'bold', size = rel(0.8), hjust = 1)) 
  cluster_color = scales::hue_pal()(nrow(unique(sobj[[clustering]])))[cluster]
  plot = plot + scale_colour_manual(values = c('grey90', cluster_color))
  intercept = ifelse(anterior, 660, 484)
  if(arc){plot = plot + geom_hline(yintercept=484, linetype = "dashed",color = cluster_color)}
  return(plot)
}
plot_clusters_vertical_spatial(jy_408, pt.size = 1, cluster = 1, clustering = 'RNA_snn_res.1.5')
```


```{r}
clusters = as.numeric(sort(unique(jy_408$RNA_snn_res.1.5)))
plots <- lapply(1:length(clusters), function(i){
    plot_clusters_vertical_spatial(jy_408, cluster = clusters[i], pt.size = 1, clustering = 'RNA_snn_res.1.5')
  })
verts= plot_grid(plotlist = plots, label_size = 10, nrow = 1)
ggsave(plot = verts, filename = 'test_408_vertical_cluster_plots_size1_alpha1.png', path = file.path(output_dir_plot, '20220721_1'), width = 6, height = 8, dpi = 150)
```

```{r}
plot_clusters_umap <- function(sobj, clustering, pt.size = 3, space = "umap")
{
  coordinates <- Embeddings(sobj, reduction = space)
  #expmat <- sobj[[clustering]]
  expmat  = Idents(sobj)
  gene_df <- as.data.frame(cbind(coordinates, expmat))
  colnames(gene_df) <- c('X', 'Y', 'expr')
  gene_df$X = as.numeric(gene_df$X)
  gene_df$Y = as.numeric(gene_df$Y)
  summary_gene_df = gene_df %>% dplyr::group_by(expr) %>% dplyr::summarise(xmean = mean(X), ymean = mean(Y))
  plot <- ggplot(gene_df, aes(x = X, y = Y, color = as.factor(expr))) + geom_point(size = pt.size, alpha = 0.8)+ geom_label(data = summary_gene_df,
                                                                                                                 mapping = aes(x = xmean, 
                           y = ymean), 
                           label = summary_gene_df$expr) +
            theme_classic() + ggtitle(clustering) + NoAxes() + NoLegend()  + theme(title = element_text(face = 'bold', size = rel(1), hjust = 1)) 
  cluster_colors = scales::hue_pal()(nrow(unique(expmat)))
  plot = plot + scale_colour_manual(values = cluster_colors)
  return(plot)
}
p = plot_clusters_umap(jy_408, clustering ='RNA_snn_res.1.5')
p
```

```{r}
scales::hue_pal()(3)
```

```{r}
DimPlot(jy_408, cells.highlight = list('migratory' = which(grepl('MS', df_408$area))), cols.highlight = '#CB2A55')
```

```{r fig.height=3, fig.width=12}
small_dimplot <- function(sobj, grep_pattern){
  dp = DimPlot(jy_408, cells.highlight = list(imp = which(grepl(grep_pattern, df_408$area))))
  dp <- dp + scale_color_manual(values = c('grey90', '#1982c4'), labels=c('other', grep_pattern)) + NoAxes()
}

patterns = c('408_CC', 'MS_CC', 'vMS_TC', 'dMS_TC', '408_TC')
plots <- lapply(1:length(patterns), function(i){
    small_dimplot(jy_408, grep_pattern = patterns[i])
  })
areas = plot_grid(plotlist = plots, label_size = 10, nrow = 2)
ggsave(plot = areas, filename = 'test_408_area_plots_size1_alpha1.png', path = file.path(output_dir_plot, '20220721_1'), width = 12, height = 3, dpi = 150)
```
```{r}
DimPlot(jy_408, cells.highlight = list('CC' = which(grepl('CC', df_408$area))), cols.highlight = '#CB2A55')
```

```{r}
jy_164<- RenameCells(jy_164, c(outer('164_', 1:ncol(jy_164), FUN=paste0)))
jy_164$area = df_164$area
jy_408<- RenameCells(jy_408, c(outer('408_', 1:ncol(jy_408), FUN=paste0)))
jy_408$area = df_408$area
jy_all <- merge(jy_164, jy_408)
```
```{r}
jy_all <- NormalizeData(jy_all, scale.factor = 1e5) ###
normed = GetAssayData(jy_all, slot = 'data')
normed[normed < 3] = 0
jy_all <- SetAssayData(jy_all, slot = 'data', normed)
```

```{r}
jy_all <- FindVariableFeatures(jy_all, selection.method = "vst")
all.genes <- rownames(jy_all)
jy_all <- ScaleData(jy_all, features = all.genes)
jy_all <- RunPCA(jy_all, approx = FALSE)
jy_all <- FindNeighbors(jy_all, dims = 1:30)
jy_all <- FindClusters(jy_all, resolution = 1.5)
jy_all <- RunUMAP(jy_all, dims = 1:30)

DimPlot(jy_all,  reduction = "umap", group.by = 'seurat_clusters') + NoAxes()
```
```{r}
breakpoints = 1:20/10 + 0.1
plots = list()
jy_all <- FindNeighbors(jy_all, dims = 1:30)
i = 1
for (breakpoint in breakpoints){
  jy_all <- FindClusters(jy_all, resolution = breakpoint)
  jy_all <- RunUMAP(jy_all, dims = 1:30)
  jy_all.markers <- FindAllMarkers(jy_all, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
  labels = jy_all.markers %>%
   group_by(cluster) %>%
   slice_max(n = 1, order_by = avg_log2FC)
  new.cluster.ids <- labels$gene
  names(new.cluster.ids) <- levels(jy_all)
  jy_all <- RenameIdents(jy_all, new.cluster.ids)
  plots[[i]] = DimPlot(jy_all, reduction = "umap", pt.size = 1, label = TRUE) + NoAxes() + NoLegend() + ggtitle(breakpoint)
  i = i + 1
}

marrangeGrob(plots, nrow=2, ncol=2)
ml <- marrangeGrob(plots, nrow=2, ncol=2)
ggsave(filename = 'all_sequential_clustering_umaps.pdf', path = file.path(output_dir_plot, '20220721_1'), ml)
```
```{r fig.height=8, fig.width=14}
big_dimplot <- function(sobj, grep_pattern){
  dp = DimPlot(sobj, cells.highlight = list(imp = which(grepl(grep_pattern, sobj$area))))
  dp <- dp + scale_color_manual(values = c('grey90', '#1982c4'), labels=c('other', grep_pattern)) + NoAxes()
}
patterns = c('408_CC', '408_MS_CC', 'vMS_TC', 'dMS_TC', '408_TC', '164_CC', '164_MS_CC', '164_MS_TC',  '164_TC')
plots <- lapply(1:length(patterns), function(i){
    big_dimplot(jy_all, grep_pattern = patterns[i])
  })
areas = plot_grid(plotlist = plots, label_size = 10, nrow = 3)
areas
ggsave(plot = areas, filename = 'test_all_area_plots_size1_alpha1.png', path = file.path(output_dir_plot, '20220721_1'), width = 14, height = 8, dpi = 150)
```
```{r}

plot_clusters_umap(jy_all, clustering ='RNA_snn_res.1.5', pt.size = 2.0)
```

```{r}
jy_all.markers <- FindAllMarkers(jy_all, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
jy_all.markers %>%
   group_by(cluster) %>%
   slice_max(n = 32, order_by = avg_log2FC)
```


```{r}
clusters_164 = jy_all$RNA_snn_res.1.5[1:ncol(jy_164)]
jy_164$unified_clusters = clusters_164
clusters_408 = jy_all$RNA_snn_res.1.5[(ncol(jy_164)+1):ncol(jy_all)]
jy_408$unified_clusters = clusters_408
```

```{r fig.height=8, fig.width=4}
clusters = as.numeric(sort(unique(jy_408$unified_clusters)))
plots <- lapply(1:length(clusters), function(i){
    plot_clusters_vertical_spatial(jy_408, cluster = clusters[i], pt.size = 1, clustering = 'unified_clusters', anterior = FALSE)
  })
verts= plot_grid(plotlist = plots, label_size = 10, nrow = 1)
ggsave(plot = verts, filename = 'test_408_unified_vertical_cluster_plots_size1_alpha1.png', path = file.path(output_dir_plot, '20220721_1'), width = 5, height = 8, dpi = 150)
```
```{r fig.height=8, fig.width=5}
clusters = as.numeric(sort(unique(jy_164$unified_clusters)))
plots <- lapply(1:length(clusters), function(i){
    plot_clusters_vertical_spatial(jy_164, cluster = clusters[i], pt.size = 1, clustering = 'unified_clusters', anterior = TRUE)
  })
verts= plot_grid(plotlist = plots, label_size = 10, nrow = 1)
ggsave(plot = verts, filename = 'test_164_unified_vertical_cluster_plots_size1_alpha1.png', path = file.path(output_dir_plot, '20220721_1'), width = 5, height = 8, dpi = 150)
```

```{r fig.height=1, fig.width=8}
genes = rownames(markers2)
plots <- lapply(1:length(genes), function(i){
    plot_features_umap(jy_all, genes[i], pt.size = 0.5)
  })
umaps = plot_grid(plotlist = plots, label_size = 10, nrow = 1)
umaps
ggsave(plot = umaps, filename = 'cluster7_markers_all_umapl_expr_plots_size1_alpha1.png', path = file.path(output_dir_plot, '20220721_1'), width = 8, height = 1, dpi = 150)

```

```{r}
jy_all_7.markers <- FindMarkers(jy_all, ident.1 = 7, ident.2 = NULL, only.pos = FALSE)
markers2 = jy_all_7.markers %>%
   slice_max(n = 5, order_by = avg_log2FC)
markers2
```
```{r}
new.cluster.ids = c('TBR1+/LRP8+ MS to TC', 
              'PROX1 and NKX2.1 Immature INs',
'Immature CALB2+ CGE interneuron',
 'Excitatory CXCL12+ Neurons',
'Cajal Retzius Cells',
'Mature, SST+ MGE INs',
 'Mature, VIP+ CGE INs',
 'MAF1+/TSHZ1+ Immature INs',
 'Layer 2 Excitatory Neurons',
 'CXCR4+ Posterior, MS to TC INs',
'EMX1+/NKX2.1+ Anterior, MS to CC INs',
 'EMX1+/LHX6+ Posterior, MS to CC INs',
 'GSX2+/RELN+/PAX6+ Clump')

```

```{r}
names(new.cluster.ids) <- levels(jy_all)
jy_all <- RenameIdents(jy_all, new.cluster.ids)
```

```{r}
library(ggrepel)
plot_clusters_umap <- function(sobj, clustering, pt.size = 3, space = "umap")
{
  coordinates <- Embeddings(sobj, reduction = space)
  #expmat <- sobj[[clustering]]
  expmat  = as.character(Idents(jy_all))
  gene_df <- as.data.frame(cbind(coordinates, expmat))
  colnames(gene_df) <- c('X', 'Y', 'expr')
  gene_df$X = as.numeric(gene_df$X)
  gene_df$Y = as.numeric(gene_df$Y)
  summary_gene_df = gene_df %>% dplyr::group_by(expr) %>% dplyr::summarise(xmean = mean(X), ymean = mean(Y))
  plot <- ggplot(gene_df, aes(x = X, y = Y, color = as.factor(expr))) + geom_point(size = pt.size, alpha = 0.8) + #+ geom_label_repel(data = summary_gene_df,
                                                                                                                # mapping = aes(x = xmean, 
                           #y = ymean), 
                           #label = summary_gene_df$expr) +
            theme_classic() + ggtitle(clustering) + NoAxes() + #NoLegend()  + 
    theme(title = element_text(face = 'bold', size = rel(1), hjust = 1)) 
  cluster_colors = scales::hue_pal()(length(unique(expmat)))
  plot = plot + scale_colour_manual(values = cluster_colors)
  return(plot)
}

plot_clusters_umap(jy_all, clustering = '', pt.size = 2.0)
```

```{r}
genes = rownames(jy_408)
plots <- lapply(1:length(genes), function(i){
    plot_features_vertical_spatial(jy_408, genes[i], pt.size = 1)
  })
verts= plot_grid(plotlist = plots, label_size = 10, nrow = 1)
ggsave(plot = verts, filename = 'test_408_vertical_expr_plots_size1_alpha1.png', path = file.path(output_dir_plot, '20220721_1'), width = 18, height = 8, dpi = 150)
```

