---
title: "st_all"
output: html_notebook
---

Written by Aunoy Poddar
July 21st, 2022

# Process the puncta quantified raw data
```{r eval=FALSE}
current_file <- rstudioapi::getActiveDocumentContext()$path
output_file <- stringr::str_replace(current_file, '.Rmd', '.R')
knitr::purl(current_file, output = output_file)
file.edit(output_file)
```

## Import packages and functions
```{r}
library(Seurat)
library(tictoc)
library(ggplot2)
library(patchwork)
library(pheatmap)
library(RColorBrewer)
library(tidyverse)
library(gridExtra)
library(png)
library(cowplot)
library(magick)
library(scales)
```

## Load the data
```{r}
data_dir = '/home/aunoy/st/arc_profiling/st_analysis/hand_annotated_data/rethresholded'
meta_dir = '/home/aunoy/st/arc_profiling/st_analysis/hand_annotated_data/overlay'
output_dir_plot = '/home/aunoy/st/arc_profiling/st_analysis/results/plots'
output_dir_tbls = '/home/aunoy/st/arc_profiling/st_analysis/results/tables'
```


### Merge both datasets and generate a metadata column that corresponds
### to the cell #
```{r}
df_408 = data.frame()
for (file_name in list.files(data_dir)){
  print(file_name)
  if(grepl('164', file_name)){
    next
  }
  #if(grepl('408_TC', file_name) | grepl('408_vMS', file_name)){
  #  next
  #}
  df_to_append <- read.table(file.path(data_dir, file_name), sep = ',', header = TRUE)
  while(length(ind <- which(df_to_append$Image.Name == "")) > 0){
    df_to_append$Image.Name[ind] <- df_to_append$Image.Name[ind -1]
  }
  
  colnames(df_to_append) <- toupper(colnames(df_to_append))
  df_to_append <- df_to_append %>%
    mutate(area = strsplit(file_name, '.csv')[[1]])
  
  ## Add relative_XY_position
  
  if(!is_empty(df_408)){
    df_to_append <- df_to_append %>%
          dplyr::select(colnames(df_408))
  }
  df_408 <- rbind(df_408, df_to_append)
}
```
```{r}
df_408$IMAGE.NAME = unlist(lapply(df_408$IMAGE.NAME, gsub, pattern='_Cluster', replacement=''))
df_408$IMAGE.NAME = unlist(lapply(df_408$IMAGE.NAME, gsub, pattern='[*]', replacement=''))
df_408$IMAGE.NAME = unlist(lapply(df_408$IMAGE.NAME, gsub, pattern='X', replacement=''))
df_408$IMAGE.NAME = unlist(lapply(df_408$IMAGE.NAME, gsub, pattern='L2_', replacement='L2-'))
df_408$IMAGE.NAME = unlist(lapply(df_408$IMAGE.NAME, gsub, pattern='-L2', replacement='_L2'))
df_408$IMAGE.NAME = unlist(lapply(df_408$IMAGE.NAME, gsub, pattern='Tc_12', replacement='TC_12'))
## Missing
df_408 = df_408[df_408$IMAGE.NAME != 'Layer1', ]
df_408 = df_408[df_408$IMAGE.NAME != 'TC_1', ]
df_408 = df_408[df_408$IMAGE.NAME != 'TC_18', ]
df_408 = df_408[df_408$IMAGE.NAME != 'TC_19', ]
#df_408$IMAGE.NAME = toupper(df_408$IMAGE.NAME)
unique(df_408$IMAGE.NAME)
```


## Order the images
```{r}
unique(df_408$IMAGE.NAME)
images_ordered = c('TC_20', 'TC_17', 'TC_16', 'TC_15', 'TC_14', 'TC_13', 'TC_12', 'TC_11', 'TC_10', 'TC_9', 'TC_8', 'TC_7', 'TC_6', 'TC_5',
                   'TC_4', 'TC_3', 'TC_2', 'CC_4', 'CC_5', 'CC_6', 'CC_7', 'CC_8', 'CC_9', 'CC_10', 'CC_11', 'CC_12', 'CC_L2-3', 'CC_L2-2', 'CC_L2-1', 'CC_Cortical1', 'CC_Cortical2')
```

```{r}
x_horz = 1:length(images_ordered) * 35
y_horz = rep(0, length(images_ordered))
horz_embedding = data.frame()
df_408$X_horz = -1
df_408$Y_horz = -1
IMAGE_SIZE = 1024
## This is the size of an image in the global coordinate space
IMAGE_LEN = 25

images = list.files(meta_dir)
for(i in 1:length(images_ordered)){
    image_name = images_ordered[i]
    print(image_name)
    split_names = strsplit(image_name, '_')
    cortex = toupper(split_names[[1]][1])
    number = split_names[[1]][2]
    number_csv = paste0('_', number, '.csv')
    filename = images[grepl(cortex, images) & grepl(number_csv, images) & grepl('408', images)]
    coordinates = read.table(file.path(meta_dir, filename), sep = ',', header = TRUE)
    ## checked already that lists are equal, missing 1, 18, 19 for now, layer 1 and others
 
    ## so this is a little tricky, so need to get it right
    ## Remember, it is the top right that the coordinate is coming from, but
    ## the bottom right is the new coordinate space.
    ## so first when we get the original coordinate space, to set to relative
    ## of bottom would be the same X, but 1024 - Y
    
    ## push out the coordinates for better visualization
    #x_repelled <- (512 - coordinates$X_Coordinate_In_pixels)
    
    
    df_408[df_408$IMAGE.NAME == image_name, 'X_horz'] = (coordinates$X_Coordinate_In_pixels / 
                                                      IMAGE_SIZE * IMAGE_LEN) + y_horz[i]
    df_408[df_408$IMAGE.NAME == image_name, 'Y_horz'] = ((1024-coordinates$Y_Coordinate_In_pixels) / 
                                                      IMAGE_SIZE * IMAGE_LEN) + x_horz[i]
}
```

## We have the coordinates for 408_TC and others
```{r}
rownames(df_408) = 1:nrow(df_408)
jy_408 = df_408 %>%
  dplyr::select(-c(area, IMAGE.NAME, X_horz, Y_horz)) %>%
  t() %>%
  CreateSeuratObject()
```

## just set everything from below 1 in ratio to zero
```{r}
jy_408 <- NormalizeData(jy_408, scale.factor = 1e5) ###
normed = GetAssayData(jy_408, slot = 'data')
normed[normed < 3] = 0
jy_408 <- SetAssayData(jy_408, slot = 'data', normed)
```

```{r}
jy_408 <- FindVariableFeatures(jy_408, selection.method = "vst")
all.genes <- rownames(jy_408)
jy_408 <- ScaleData(jy_408, features = all.genes)
jy_408 <- RunPCA(jy_408, approx = FALSE)
jy_408 <- FindNeighbors(jy_408, dims = 1:30)
jy_408 <- FindClusters(jy_408, resolution = 1.5)
jy_408 <- RunUMAP(jy_408, dims = 1:30)

DimPlot(jy_408,  reduction = "umap", group.by = 'seurat_clusters') + NoAxes()
```

```{r}
hcoords = df_408 %>% dplyr::select(c('X_horz', 'Y_horz')) %>% as.matrix()
colnames(hcoords) <- c('pixel_1', 'pixel_2')

jy_408[["H"]] <- CreateDimReducObject(embeddings = hcoords, key = "pixel_", assay = DefaultAssay(jy_408))
```

### Merge both datasets and generate a metadata column that corresponds
### to the cell #
```{r}
df_164 = data.frame()
for (file_name in list.files(data_dir)){
  print(file_name)
  if(grepl('408', file_name)){
    next
  }
  #if(grepl('408_TC', file_name) | grepl('408_vMS', file_name)){
  #  next
  #}
  df_to_append <- read.table(file.path(data_dir, file_name), sep = ',', header = TRUE)
  while(length(ind <- which(df_to_append$Image.Name == "")) > 0){
    df_to_append$Image.Name[ind] <- df_to_append$Image.Name[ind -1]
  }
  
  colnames(df_to_append) <- toupper(colnames(df_to_append))
  df_to_append <- df_to_append %>%
    mutate(area = strsplit(file_name, '.csv')[[1]])
  
  ## Add relative_XY_position
  
  if(!is_empty(df_164)){
    df_to_append <- df_to_append %>%
          dplyr::select(colnames(df_164))
  }
  df_164 <- rbind(df_164, df_to_append)
}
```
```{r}
df_164$IMAGE.NAME = unlist(lapply(df_164$IMAGE.NAME, gsub, pattern='CC-', replacement='CC_'))
df_164$IMAGE.NAME = unlist(lapply(df_164$IMAGE.NAME, gsub, pattern='[*]', replacement=''))
df_164$IMAGE.NAME = unlist(lapply(df_164$IMAGE.NAME, gsub, pattern='X', replacement=''))
df_164$IMAGE.NAME = unlist(lapply(df_164$IMAGE.NAME, gsub, pattern='L2', replacement='CC_L2'))
df_164$IMAGE.NAME = unlist(lapply(df_164$IMAGE.NAME, gsub, pattern='L2_', replacement='L2-'))
df_164$IMAGE.NAME = unlist(lapply(df_164$IMAGE.NAME, gsub, pattern='-L2', replacement='_L2'))
tc_cortical_names_bad = df_164[grepl('TC', df_164$area) & grepl('Cortical', df_164$IMAGE.NAME), 'IMAGE.NAME']
df_164[grepl('TC', df_164$area) & grepl('Cortical', df_164$IMAGE.NAME), 'IMAGE.NAME'] = unlist(lapply(tc_cortical_names_bad, gsub, pattern='Cort', replacement='TC_Cort'))
cc_cortical_names_bad = df_164[grepl('CC', df_164$area) & grepl('Cortical', df_164$IMAGE.NAME), 'IMAGE.NAME']
df_164[grepl('CC', df_164$area) & grepl('Cortical', df_164$IMAGE.NAME), 'IMAGE.NAME'] = unlist(lapply(cc_cortical_names_bad, gsub, pattern='Cort', replacement='CC_Cort'))
#df_164$IMAGE.NAME = unlist(lapply(df_164$IMAGE.NAME, gsub, pattern='Tc_12', replacement='TC_12'))
## Missing
#df_164 = df_164[df_164$IMAGE.NAME != 'Layer1', ]
#df_164 = df_164[df_164$IMAGE.NAME != 'TC_1', ]
#df_164 = df_164[df_164$IMAGE.NAME != 'TC_18', ]
#df_164 = df_164[df_164$IMAGE.NAME != 'TC_19', ]
#df_164$IMAGE.NAME = toupper(df_164$IMAGE.NAME)
unique(df_164$IMAGE.NAME)
```
## Now we know that everything is equal to one another, we should load the variable

```{r}
image_names = unique(df_164$IMAGE.NAME)
# Preset these variables to negative values so I can easily check if they were updated later
df_164$X = -1
df_164$Y = -1
# set some normalization variables
## This is the size of the image when the pixel values are taken from top left down
IMAGE_SIZE = 1024
## This is the size of an image in the global coordinate space
IMAGE_LEN = 32
TC_IMAGE_HEIGHT = 410
TC_IMAGE_WIDTH = 446
CC_IMAGE_HEIGHT= 422
CC_IMAGE_WIDTH = 214

# Load the dataframe with global and relative coordinates
img_cords = read.table(file.path(meta_dir, '164_pixel_coordinates.csv'), sep = ',', header = TRUE)

images = list.files(meta_dir)
for(image_name in image_names){
    if(grepl('408', image_name)){
      next
    }
    print(image_name)
    split_names = strsplit(image_name, '_')
    cortex = toupper(split_names[[1]][1])
    number = split_names[[1]][2]
    number_csv = paste0('_', number, '.csv')
    filename = images[grepl(cortex, images) & grepl(number_csv, images) & grepl('164', images)]
    coordinates = read.table(file.path(meta_dir, filename), sep = ',', header = TRUE)
    if(image_name == "CC_L2-1"){
      coordinates = coordinates[c(1:37, 39:nrow(coordinates)), ]
    }
    if(cortex == 'CC'){ 
      print(paste('cc', filename, image_name))
      ## So if CC, we add the coordinates for TC_1 to overall image coordinates
      x_adj = img_cords[img_cords$Name == 'TC_1', 'x'] + 
                img_cords[img_cords$Name == 'G_CC1_to_TC1', 'x']
      ## Start from bottom, add the height, subtract TC_1 height, and then global CC1 to TC1
      y_adj = TC_IMAGE_HEIGHT - img_cords[img_cords$Name == 'TC_1', 'y'] +
                img_cords[img_cords$Name == 'G_CC1_to_TC1', 'y'] + CC_IMAGE_HEIGHT
    }else{
      print(paste('tc', filename, image_name))
      x_adj = 0
      y_adj = TC_IMAGE_HEIGHT
    }
    
    ## So don't do repelled for now
    #x_repelled <- (512 - coordinates$X_Coordinate_In_pixels)
    
    ## so the resized x distance is from left, so just add to the box location and adj
    df_164[df_164$IMAGE.NAME == image_name, 'X'] = (coordinates$X_Coordinate_In_pixels / 
                                                      IMAGE_SIZE * IMAGE_LEN) + 
                                                    img_cords[img_cords$Name == image_name, 'x'] + x_adj
    ## resized y distance
    df_164[df_164$IMAGE.NAME == image_name, 'Y'] = y_adj - img_cords[img_cords$Name == image_name, 'y'] - 
                                                      (coordinates$Y_Coordinate_In_pixels / IMAGE_SIZE * 
                                                      IMAGE_LEN)  
}
```



## We have the coordinates for 408_TC and others
```{r}
rownames(df_164) = 1:nrow(df_164)
jy_164 = df_164 %>%
  dplyr::select(-c(area, IMAGE.NAME, X, Y)) %>%
  t() %>%
  CreateSeuratObject()
```

## just set everything from below 1 in ratio to zero
```{r}
jy_164 <- NormalizeData(jy_164, scale.factor = 1e5) ###
normed = GetAssayData(jy_164, slot = 'data')
normed[normed < 3] = 0
jy_164 <- SetAssayData(jy_164, slot = 'data', normed)
```

```{r}
jy_164 <- FindVariableFeatures(jy_164, selection.method = "vst")
all.genes <- rownames(jy_164)
jy_164 <- ScaleData(jy_164, features = all.genes)
jy_164 <- RunPCA(jy_164, approx = FALSE)
jy_164 <- FindNeighbors(jy_164, dims = 1:30)
jy_164 <- FindClusters(jy_164, resolution = 0.8)
jy_164 <- RunUMAP(jy_164, dims = 1:30)

DimPlot(jy_164,  reduction = "umap", group.by = 'seurat_clusters') + NoAxes()
```

```{r}
unique(df_164$IMAGE.NAME)
images_ordered = c('TC_Cortical3', 'TC_Cortical2', 'TC_Cortical1', 'TC_10', 'TC_9', 'TC_8', 'TC_7', 'TC_6', 'TC_5', 'TC_4', 'TC_3', 'TC_2','TC_1','CC_2','CC_3',
           'CC_4', 'CC_5', 'CC_6', 'CC_7', 'CC_8', 'CC_9', 'CC_10',
           'CC_L2-1', 'CC_L2-2', 'CC_L2-3', 'CC_Cortical1', 'CC_Cortical2')
```

```{r}
x_horz = 1:length(images_ordered) * 35
y_horz = rep(0, length(images_ordered))
horz_embedding = data.frame()
df_164$X_horz = -1
df_164$Y_horz = -1

images = list.files(meta_dir)
for(i in 1:length(images_ordered)){
    image_name = images_ordered[i]
    print(image_name)
    split_names = strsplit(image_name, '_')
    cortex = toupper(split_names[[1]][1])
    number = split_names[[1]][2]
    number_csv = paste0('_', number, '.csv')
    filename = images[grepl(cortex, images) & grepl(number_csv, images) & grepl('164', images)]
    coordinates = read.table(file.path(meta_dir, filename), sep = ',', header = TRUE)
    if(image_name == "CC_L2-1"){
      coordinates = coordinates[c(1:37, 39:nrow(coordinates)), ]
    }
    ## checked already that lists are equal, missing 1, 18, 19 for now, layer 1 and others
 
    ## so this is a little tricky, so need to get it right
    ## Remember, it is the top right that the coordinate is coming from, but
    ## the bottom right is the new coordinate space.
    ## so first when we get the original coordinate space, to set to relative
    ## of bottom would be the same X, but 1024 - Y
    
    ## push out the coordinates for better visualization
    #x_repelled <- (512 - coordinates$X_Coordinate_In_pixels)
    
    
    df_164[df_164$IMAGE.NAME == image_name, 'X_horz'] = (coordinates$X_Coordinate_In_pixels / 
                                                      IMAGE_SIZE * IMAGE_LEN) + y_horz[i]
    df_164[df_164$IMAGE.NAME == image_name, 'Y_horz'] = ((1024-coordinates$Y_Coordinate_In_pixels) / 
                                                      IMAGE_SIZE * IMAGE_LEN) + x_horz[i]
}
```

```{r}
hcoords = df_164 %>% dplyr::select(c('X_horz', 'Y_horz')) %>% as.matrix()
colnames(hcoords) <- c('pixel_1', 'pixel_2')

jy_164[["H"]] <- CreateDimReducObject(embeddings = hcoords, key = "pixel_", assay = DefaultAssay(jy_164))
```


```{r}
jy_164<- RenameCells(jy_164, c(outer('164_', 1:ncol(jy_164), FUN=paste0)))
jy_164$area = df_164$area
jy_408<- RenameCells(jy_408, c(outer('408_', 1:ncol(jy_408), FUN=paste0)))
jy_408$area = df_408$area
jy_all <- merge(jy_164, jy_408)
```
```{r}
jy_all <- NormalizeData(jy_all, scale.factor = 1e5) ###
normed = GetAssayData(jy_all, slot = 'data')
normed[normed < 3] = 0
jy_all <- SetAssayData(jy_all, slot = 'data', normed)
```

```{r}
jy_all <- FindVariableFeatures(jy_all, selection.method = "vst")
all.genes <- rownames(jy_all)
jy_all <- ScaleData(jy_all, features = all.genes)
jy_all <- RunPCA(jy_all, approx = FALSE)
jy_all <- FindNeighbors(jy_all, dims = 1:30)
jy_all <- FindClusters(jy_all, resolution = 1.5)
jy_all <- RunUMAP(jy_all, dims = 1:30)

DimPlot(jy_all,  reduction = "umap", group.by = 'seurat_clusters') + NoAxes()
```

```{r fig.height=8, fig.width=14}
big_dimplot <- function(sobj, grep_pattern){
  dp = DimPlot(sobj, cells.highlight = list(imp = which(grepl(grep_pattern, sobj$area))))
  dp <- dp + scale_color_manual(values = c('grey90', '#1982c4'), labels=c('other', grep_pattern)) + NoAxes()
}
patterns = c('408_CC', '408_MS_CC', 'vMS_TC', 'dMS_TC', '408_TC', '164_CC', '164_MS_CC', '164_MS_TC',  '164_TC')
plots <- lapply(1:length(patterns), function(i){
    big_dimplot(jy_all, grep_pattern = patterns[i])
  })
areas = plot_grid(plotlist = plots, label_size = 10, nrow = 3)
areas
ggsave(plot = areas, filename = 'test_all_area_plots_size1_alpha1.png', path = file.path(output_dir_plot, '20220721_1'), width = 14, height = 8, dpi = 150)
```
```{r}

plot_clusters_umap(jy_all, clustering ='RNA_snn_res.1.5', pt.size = 2.0)
```

```{r}
jy_all.markers <- FindAllMarkers(jy_all, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
jy_all.markers %>%
   group_by(cluster) %>%
   slice_max(n = 32, order_by = avg_log2FC)
```


```{r}
clusters_164 = jy_all$RNA_snn_res.1.5[1:ncol(jy_164)]
jy_164$unified_clusters = clusters_164
clusters_408 = jy_all$RNA_snn_res.1.5[(ncol(jy_164)+1):ncol(jy_all)]
jy_408$unified_clusters = clusters_408
```

```{r fig.height=8, fig.width=4}
clusters = as.numeric(sort(unique(jy_408$unified_clusters)))
plots <- lapply(1:length(clusters), function(i){
    plot_clusters_vertical_spatial(jy_408, cluster = clusters[i], pt.size = 1, clustering = 'unified_clusters', anterior = FALSE)
  })
verts= plot_grid(plotlist = plots, label_size = 10, nrow = 1)
ggsave(plot = verts, filename = 'test_408_unified_vertical_cluster_plots_size1_alpha1.png', path = file.path(output_dir_plot, '20220721_1'), width = 5, height = 8, dpi = 150)
```
```{r fig.height=8, fig.width=5}
clusters = as.numeric(sort(unique(jy_164$unified_clusters)))
plots <- lapply(1:length(clusters), function(i){
    plot_clusters_vertical_spatial(jy_164, cluster = clusters[i], pt.size = 1, clustering = 'unified_clusters', anterior = TRUE)
  })
verts= plot_grid(plotlist = plots, label_size = 10, nrow = 1)
ggsave(plot = verts, filename = 'test_164_unified_vertical_cluster_plots_size1_alpha1.png', path = file.path(output_dir_plot, '20220721_1'), width = 5, height = 8, dpi = 150)
```

```{r fig.height=1, fig.width=8}
genes = rownames(markers2)
plots <- lapply(1:length(genes), function(i){
    plot_features_umap(jy_all, genes[i], pt.size = 0.5)
  })
umaps = plot_grid(plotlist = plots, label_size = 10, nrow = 1)
umaps
ggsave(plot = umaps, filename = 'cluster7_markers_all_umapl_expr_plots_size1_alpha1.png', path = file.path(output_dir_plot, '20220721_1'), width = 8, height = 1, dpi = 150)

```

```{r}
jy_all_7.markers <- FindMarkers(jy_all, ident.1 = 7, ident.2 = NULL, only.pos = FALSE)
markers2 = jy_all_7.markers %>%
   slice_max(n = 5, order_by = avg_log2FC)
markers2
```
```{r}
new.cluster.ids = c('TBR1+/LRP8+ MS to TC', 
              'PROX1 and NKX2.1 Immature INs',
'Immature CALB2+ CGE IN',
 'Excitatory CXCL12+ Neurons',
'GSX2- dLGE INs',
'Mature, SST+ MGE INs',
 'Mature, VIP+ CGE INs',
 'MAF1+/TSHZ1+ Immature INs',
 'Layer 2 Excitatory Neurons',
 'CXCR4+ Posterior, MS to TC INs',
'EMX1+/NKX2.1+ Anterior, MS to CC INs',
 'EMX1+/LHX6+ Posterior, MS to CC INs',
 'GSX2+/RELN+/PAX6+ dLGE INs')

```

```{r}
names(new.cluster.ids) <- levels(jy_all)
jy_all <- RenameIdents(jy_all, new.cluster.ids)
```

```{r}
library(ggrepel)
plot_clusters_umap <- function(sobj, clustering, pt.size = 3, space = "umap")
{
  coordinates <- Embeddings(sobj, reduction = space)
  #expmat <- sobj[[clustering]]
  expmat  = as.character(Idents(jy_all))
  gene_df <- as.data.frame(cbind(coordinates, expmat))
  colnames(gene_df) <- c('X', 'Y', 'expr')
  gene_df$X = as.numeric(gene_df$X)
  gene_df$Y = as.numeric(gene_df$Y)
  summary_gene_df = gene_df %>% dplyr::group_by(expr) %>% dplyr::summarise(xmean = mean(X), ymean = mean(Y))
  plot <- ggplot(gene_df, aes(x = X, y = Y, color = as.factor(expr))) + geom_point(size = pt.size, alpha = 0.8) + #+ geom_label_repel(data = summary_gene_df,
                                                                                                                # mapping = aes(x = xmean, 
                           #y = ymean), 
                           #label = summary_gene_df$expr) +
            theme_classic() + ggtitle(clustering) + NoAxes() + #NoLegend()  + 
    theme(title = element_text(face = 'bold', size = rel(1), hjust = 1)) 
  cluster_colors = scales::hue_pal()(length(unique(expmat)))
  plot = plot + scale_colour_manual(values = cluster_colors)
  return(plot)
}

plot_clusters_umap(jy_all, clustering = '', pt.size = 2.0)
```

```{r fig.height=3, fig.width=8}
immature_IN_names = c('PROX1 and NKX2.1 Immature INs',
'Immature CALB2+ CGE interneuron',
 'MAF1+/TSHZ1+ Immature INs',
 'CXCR4+ Posterior, MS to TC INs',
'EMX1+/NKX2.1+ Anterior, MS to CC INs',
 'EMX1+/LHX6+ Posterior, MS to CC INs',
 'GSX2+/RELN+/PAX6+ Clump')

jy_immature <- jy_all[, Idents(jy_all) %in% immature_IN_names]
```

```{r}
jy_immature <- FindVariableFeatures(jy_immature, selection.method = "vst")
all.genes <- rownames(jy_immature)
jy_immature <- ScaleData(jy_immature, features = all.genes)
jy_immature <- RunPCA(jy_immature, approx = FALSE)
jy_immature <- FindNeighbors(jy_immature, dims = 1:30)
jy_immature <- FindClusters(jy_immature, resolution = 1.5)
jy_immature <- RunUMAP(jy_immature, dims = 1:30)

DimPlot(jy_immature,  reduction = "umap", split.by = 'area') + NoAxes()
```
```{r}
breakpoints = 1:20/10+0.3
plots = list()
jy_immature <- FindNeighbors(jy_immature, dims = 1:30)
i = 1
for (breakpoint in breakpoints){
  jy_immature <- FindClusters(jy_immature, resolution = breakpoint)
  jy_immature <- RunUMAP(jy_immature, dims = 1:30)
  jy_immature.markers <- FindAllMarkers(jy_immature, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
  labels = jy_immature.markers %>%
   group_by(cluster) %>%
   slice_max(n = 1, order_by = avg_log2FC)
  new.cluster.ids <- labels$gene
  names(new.cluster.ids) <- levels(jy_immature)
  jy_immature <- RenameIdents(jy_immature, new.cluster.ids)
  plots[[i]] = DimPlot(jy_immature, reduction = "umap", pt.size = 1, label = TRUE) + NoAxes() + NoLegend() + ggtitle(breakpoint)
  i = i + 1
}

marrangeGrob(plots, nrow=2, ncol=2)
ml <- marrangeGrob(plots, nrow=2, ncol=2)
ggsave(filename = 'immature_sequential_clustering_umaps.pdf', path = file.path(output_dir_plot, '20220721_1'), ml)
```
# make an easy mapping
```{r}
get_broad_type <- function(celltype){
  Excitatory =  c('Layer 2 Excitatory Neurons',
                  'Excitatory CXCL12+ Neurons',
                  'Cajal Retzius Cells',
                  'Immature CALB2+ CGE interneuron')
  Mature_inhib = c('Mature, SST+ MGE INs',
                   "Mature, VIP+ CGE INs")
  other = c('TBR1+/LRP8+ MS to TC')
    
  immature_neurons = c(
  'PROX1 and NKX2.1 Immature INs',
 'MAF1+/TSHZ1+ Immature INs',
 'CXCR4+ Posterior, MS to TC INs',
'EMX1+/NKX2.1+ Anterior, MS to CC INs',
 'EMX1+/LHX6+ Posterior, MS to CC INs',
 'GSX2+/RELN+/PAX6+ Clump')
  if(celltype %in% Excitatory){
    return("EN")
  }else if(celltype %in% Mature_inhib){
    return('Mature IN')
  } else if(celltype %in% immature_neurons){
    return('Immature IN')
  } else{return('other')} 
}
```

## do heatmap real quick
```{r fig.height=14, fig.width=10}
# get the scaled data
scaled_values = as.matrix(GetAssayData(jy_all, slot = "data"))

genes_to_remove = c('DCX', 'DCDC2', 'KIA0319', 'NCAM1')

#cluster_ordering = sort(as.character(Idents(jy_all)), index.return = TRUE)
scaled_values = scaled_values[!rownames(scaled_values)%in% genes_to_remove,]

### Apply separate clustering, need to look into why 
hr <- hclust(as.dist(1-cor(t(scaled_values), method="pearson")), method = "complete")
#hc <- hclust(as.dist(1-cor(scaled_values, method="spearman")), method="complete")

broad_labels = unlist(lapply(1:ncol(scaled_values), function(i){
  get_broad_type(as.character(Idents(jy_all))[i])
}))
#broad_order = sort(broad_labels, index.return = TRUE)
#final_ox = order( cluster_ordering$x, broad_order$x)
#final_ox = broad_order$ix

#gaps = c()
#for(i in 2:length(broad_order$x)){
#  if(broad_order$x[i] != broad_order$x[i-1]){
#    gaps = c(gaps, i)
#    print(i)
#  }
#}

broad_area_sorted = sort(jy_all$area, index.return = TRUE)
final_ox = broad_area_sorted$ix

gaps = c()
for(i in 2:length(broad_area_sorted$x)){
  if(broad_area_sorted$x[i] != broad_area_sorted$x[i-1]){
    gaps = c(gaps, i)
    print(i)
  }
}

### Now arrange everything

annotation <- data.frame(cell_type = as.character(Idents(jy_all)),
                         #cell_class = broad_labels,
                         area = jy_all$area)
rownames(annotation) <- colnames(scaled_values) # check out the row names of annotation

scaled_values[, final_ox] %>%
  pheatmap(annotation_col = annotation, 
           color = colorRampPalette(brewer.pal(n = 9, name = "Purples"))(100),
  #breaks = seq(from= -5, to = 5, by = 11/100.), 
  cluster_rows = hr, #cluster_cols = hc, 
  #cluster_rows = TRUE,
  cluster_cols = FALSE,
  #clustering_distance_rows = "correlation", 
  #clustering_distance_cols = "correlation",
  fontsize_row = 8, fontsize_col = 4, show_colnames = FALSE, gaps_col = gaps,
           show_rownames = TRUE, cell_width = 10, cellheight = 8, width = 10, height = 14)#,
          #  filename = file.path(file.path(output_dir_plot, '20220721_1'), 'ncol_20_sort_by_broad_type_gaps.png'))
```

```{r}
plot_features_umap <- function(sobj, gene, pt.size = 3, alpha = 0.8, space = "umap", color = '#CB2A55', flipped = FALSE)
{
  coordinates <- Embeddings(sobj, reduction = space)
  expmat <- as.matrix(FetchData(sobj, gene))
  gene_df <- as.data.frame(cbind(coordinates, expmat))
  colnames(gene_df) <- c('X', 'Y', 'expr')
  gene_df <- gene_df %>% dplyr::arrange(!is.na(expr), expr)
  colors = c('grey90', 'grey90', color)
  gene_df$expr[gene_df$expr == 0] = NA
  plot <- ggplot(gene_df, aes(x = X, y = Y, color = expr)) + geom_point(size = pt.size, alpha = alpha)+  
            theme_classic() + ggtitle(gene) +  scale_color_gradient(na.value = colors[1], low = colors[2], high = colors[3], labels = NULL)  + theme(title = element_text(face = 'bold', size = rel(1), hjust = 1)) 
  if(flipped){
    plot <- plot + scale_x_reverse() + scale_y_reverse()
  }
  return(plot + NoAxes() + NoLegend())
}
```


```{r fig.height=4, fig.width=10}
genes = rownames(jy_immature)
plots <- lapply(1:length(genes), function(i){
    plot_features_umap(jy_immature, genes[i], pt.size = 0.5)
  })
umaps = plot_grid(plotlist = plots, label_size = 10, nrow = 4)
umaps
#ggsave(plot = umaps, filename = 'test_immature_umapl_expr_plots_size1_alpha1.png', path = file.path(output_dir_plot, '20220721_1'), width = 10, height = 4, dpi = 150)

```

```{r fig.height=8, fig.width=14}
big_dimplot <- function(sobj, grep_pattern){
  dp = DimPlot(sobj, cells.highlight = list(imp = which(grepl(grep_pattern, sobj$area))))
  dp <- dp + scale_color_manual(values = c('grey90', '#1982c4'), labels=c('other', grep_pattern)) + NoAxes()
}
patterns = c('408_CC', '408_MS_CC', 'vMS_TC', 'dMS_TC', '408_TC', '164_CC', '164_MS_CC', '164_MS_TC',  '164_TC')
plots <- lapply(1:length(patterns), function(i){
    big_dimplot(jy_immature, grep_pattern = patterns[i])
  })
areas = plot_grid(plotlist = plots, label_size = 10, nrow = 3)
areas
ggsave(plot = areas, filename = 'test_immature_area_plots_size1_alpha1.png', path = file.path(output_dir_plot, '20220721_1'), width = 14, height = 8, dpi = 150)
```
```{r}
jy_immature$seurat_clusters = jy_immature$RNA_snn_res.1.1
Idents(jy_immature) = jy_immature$seurat_clusters

DimPlot(jy_immature)
```
```{r fig.height=1, fig.width=4}
genes = rownames(markers2)
plots <- lapply(1:length(genes), function(i){
    plot_features_umap(jy_immature, genes[i], pt.size = 0.5)
  })
umaps = plot_grid(plotlist = plots, label_size = 10, nrow = 1)
umaps
ggsave(plot = umaps, filename = 'cluster4_markers_immature_umapl_expr_plots_size1_alpha1.png', path = file.path(output_dir_plot, '20220721_1'), width = 4, height = 1, dpi = 150)

```

```{r}
jy_immature.markers <- FindMarkers(jy_immature, ident.1 = 3, ident.2 = 4, only.pos = FALSE)
markers2 = jy_immature.markers %>%
   slice_max(n = 8, order_by = avg_log2FC)
markers2
```
```{r}

DimPlot(jy_immature, cells.highlight = list(clu3 = which(Idents(jy_immature) == 6))) + NoAxes() + NoLegend()
```
```{r}
clusters = as.numeric(sort(unique(jy_408$unified_clusters)))
plots <- lapply(1:length(clusters), function(i){
    plot_clusters_vertical_spatial(jy_408, cluster = clusters[i], pt.size = 1, clustering = 'unified_clusters', anterior = FALSE)
  })
verts= plot_grid(plotlist = plots, label_size = 10, nrow = 1)
```

```{r}
plot_clusters_vertical_spatial <- function(sobj, cluster, clustering = NULL, anterior = FALSE, cluster_color =  '#CB2A55', pt.size = 1, space = "H", arc = TRUE)
{
  cluster_identity = as.numeric(unlist(ifelse(is.null(clustering),
                                              Idents(sobj) == levels(Idents(sobj))[cluster],sobj[[clustering]]))) == (cluster)
  coordinates <- Embeddings(sobj, reduction = space)
  gene_df <- as.data.frame(cbind(coordinates, cluster_identity))
  colnames(gene_df) <- c('X', 'Y', 'clust')
  gene_df <- gene_df %>% dplyr::arrange(clust)
  plot <- ggplot(gene_df, aes(x = X, y = Y, color = factor(clust))) + geom_point(size = pt.size, alpha = 1) +  
            theme_classic() + ggtitle(cluster) + NoAxes() + NoLegend() + 
    coord_fixed(ratio = 0.5)  + theme(title = element_text(face = 'bold', size = rel(0.8), hjust = 1)) 
  cluster_color = scales::hue_pal()(nrow(unique(sobj[[clustering]])))[cluster]
  plot = plot + scale_colour_manual(values = c('grey90', cluster_color))
  intercept = ifelse(anterior, 660, 484)
  if(arc){plot = plot + geom_hline(yintercept=484, linetype = "dashed",color = cluster_color)}
  return(plot)
}
plot_clusters_vertical_spatial(jy_164, pt.size = 1, cluster = 3, clustering = 'RNA_snn_res.0.8')
```

```{r}
plot_features_vertical_spatial_smoothed <- function(sobj, gene, pt.size = 0.5, space = "H", arc = TRUE)
{
  coordinates <- Embeddings(sobj, reduction = space)
  expmat <- as.matrix(FetchData(sobj, gene))
  gene_df <- as.data.frame(cbind(coordinates, expmat))
  colnames(gene_df) <- c('X', 'Y', 'expr')
  gene_df <- gene_df %>% dplyr::arrange(!is.na(expr), expr)
  colors = c('grey90', 'grey90', '#0f4c5c')
  gene_df$expr[gene_df$expr == 0] = NA
  plot <- gene_df %>%
    filter(!is.na(expr)) %>%
    ggplot(aes(x = X, y = Y, color = expr)) +stat_density_2d(aes(fill = ..density..), geom = "raster", n = 400,contour = FALSE, interpolate = TRUE) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
#geom_bin2d(bins = 10) + #geom_point(size = pt.size, alpha = 1)+  
            theme_classic() + ggtitle(gene) + NoAxes() + NoLegend() + 
    coord_fixed(ratio = 0.5) + scale_fill_gradient(na.value = colors[1], low = colors[2], high = colors[3], labels = NULL)  + theme(title = element_text(face = 'bold', size = rel(0.5), hjust = 1)) 
  if(arc){plot = plot + geom_hline(yintercept=660, linetype = "dashed",color = colors[3])}
  return(plot)
}
plot_features_vertical_spatial_smoothed(jy_164, gene = 'PAX6')
```


```{r fig.height=8, fig.width=18}
genes = rownames(jy_408)
plots <- lapply(1:length(genes), function(i){
    plot_features_vertical_spatial_smoothed(jy_408, genes[i], pt.size = 1)
  })
verts= plot_grid(plotlist = plots, label_size = 10, nrow = 1)
verts
ggsave(plot = verts, filename = 'test_408_smoothed-vertical_expr_plots_size1_alpha1.png', path = file.path(output_dir_plot, '20220721_1'), width = 18, height = 8, dpi = 150)
```
```{r}

normed_data <- GetAssayData(jy_all, slot = 'data')
gad_1_true = normed_data['GAD1', ] != 0
jy_all$gad1 = gad_1_true
jy_gad = jy_all[, jy_all$gad1]


breakpoints = 1:20/10+0.3
plots = list()
jy_gad <- FindVariableFeatures(jy_gad, selection.method = "vst")
all.genes <- rownames(jy_gad)
jy_gad <- ScaleData(jy_gad, features = all.genes)
jy_gad <- FindNeighbors(jy_gad, dims = 1:30)
i = 1
for (breakpoint in breakpoints){
  jy_gad <- FindClusters(jy_gad, resolution = breakpoint)
  jy_gad <- RunUMAP(jy_gad, dims = 1:30)
  jy_gad.markers <- FindAllMarkers(jy_gad, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
  labels = jy_gad.markers %>%
   group_by(cluster) %>%
   slice_max(n = 1, order_by = avg_log2FC)
  new.cluster.ids <- labels$gene
  names(new.cluster.ids) <- levels(jy_gad)
  jy_gad <- RenameIdents(jy_gad, new.cluster.ids)
  plots[[i]] = DimPlot(jy_gad, reduction = "umap", pt.size = 1, label = TRUE) + NoAxes() + NoLegend() + ggtitle(breakpoint)
  i = i + 1
}

marrangeGrob(plots, nrow=2, ncol=2)
ml <- marrangeGrob(plots, nrow=2, ncol=2)
ggsave(filename = 'gad1_sequential_clustering_umaps.pdf', path = file.path(output_dir_plot, '20220721_1'), ml)
```

```{r fig.height=4, fig.width=10}
genes = rownames(jy_gad)
plots <- lapply(1:length(genes), function(i){
    plot_features_umap(jy_gad, genes[i], pt.size = 0.5)
  })
umaps = plot_grid(plotlist = plots, label_size = 10, nrow = 4)
umaps
ggsave(plot = umaps, filename = 'test_gad_umapl_expr_plots_size1_alpha1.png', path = file.path(output_dir_plot, '20220721_1'), width = 10, height = 4, dpi = 150)

```


```{r fig.height=8, fig.width=14}
big_dimplot <- function(sobj, grep_pattern){
  dp = DimPlot(sobj, cells.highlight = list(imp = which(grepl(grep_pattern, sobj$area))))
  dp <- dp + scale_color_manual(values = c('grey90', '#1982c4'), labels=c('other', grep_pattern)) + NoAxes()
}
patterns = c('408_CC', '408_MS_CC', 'vMS_TC', 'dMS_TC', '408_TC', '164_CC', '164_MS_CC', '164_MS_TC',  '164_TC')
plots <- lapply(1:length(patterns), function(i){
    big_dimplot(jy_gad, grep_pattern = patterns[i])
  })
areas = plot_grid(plotlist = plots, label_size = 10, nrow = 3)
areas
ggsave(plot = areas, filename = 'test_gad_area_plots_size1_alpha1.png', path = file.path(output_dir_plot, '20220721_1'), width = 14, height = 8, dpi = 150)
```

```{r}
VlnPlot(jy_all, features = c('COUPTF2'))
```
```{r}
VlnPlot(jy_all, features = 'GSX2') + NoLegend()
```

```{r}

plot_vertical_smoothed <- function(sobj, gene, images_ordered){
  expmat <- as.matrix(FetchData(sobj, gene))
  ## What's the logic. I need to build a rectangle, so just give it the x, y
  ## and fill is not density
  xpos = rep(0, length(images_ordered))
  ypos = 1:length(images_ordered)
  image_expr = c()
  for(i in 1:length(images_ordered)){
    image = images_ordered[i]
    gene_expr_in_subset = expmat[sobj$IMAGE.NAME == image]
    image_expr = c(image_expr, mean(gene_expr_in_subset))
  }
  tile_df = as.data.frame(cbind(xpos, ypos, image_expr)) 
  colnames(tile_df) <-  c('X', 'Y','mean_expr')
  p <- tile_df %>%
    ggplot(aes(x = X, y = Y, fill = mean_expr)) + geom_raster(interpolate = TRUE) +
    coord_fixed() + theme_classic() + NoAxes() + NoLegend() + ggtitle(gene) + theme(title = element_text(face = 'bold', size = rel(0.5), hjust = 1)) 
  return(p)
}

plot_vertical_smoothed(jy_164, 'PAX6', images_ordered)
```
```{r}
genes_to_show = c('DCX', 'GAD1', 'DLX2', 'NKX2.1', 'PROX1', 'MAF1', 'TSHZ1', 'CXCR4', 'CXCL12', 'CALB2', 'TBR1')
genes = genes_to_show
plots <- lapply(1:length(genes), function(i){
    plot_vertical_smoothed(jy_164, genes[i], images_ordered)
  })
verts= plot_grid(plotlist = plots, label_size = 10, nrow = 1)
verts
#ggsave(plot = verts, filename = 'test_408_smoothed-vertical_expr_plots_size1_alpha1.png', path = file.path(output_dir_plot, '20220721_1'), width = 18, height = 8, dpi = 150)
```

```{r fig.height=15, fig.width=6}
rplot <- RidgePlot(jy_all, features = genes_to_show, group.by = 'area', ncol = 2)
ggsave(rplot, filename = 'rplot_by_area.png', path = file.path(output_dir_plot, '20220727_1'), width = 6, height = 15, dpi = 150)
```

```{r fig.height=15, fig.width=10}
vplot <- VlnPlot(jy_all, features = genes_to_show, group.by = 'area', ncol = 3)
vplot
ggsave(vplot, filename = 'vplot_by_area.png', path = file.path(output_dir_plot, '20220727_1'), width = 10, height = 15, dpi = 150)
```

```{r fig.height=15, fig.width=10}
vplot <- VlnPlot(jy_all, features = genes_to_show, group.by = 'area', ncol = 3)
vplot
ggsave(vplot, filename = 'vplot_by_area.png', path = file.path(output_dir_plot, '20220727_1'), width = 10, height = 15, dpi = 150)
```


```{r fig.height=6, fig.width=4}
genes_to_show = c('DCX', 'GAD1', 'CXCR4', 'DLX2', 'NKX2.1', 'PROX1', 'MAF1', 'TSHZ1', 'CXCL12', 'CALB2', 'TBR1', 'COUPTF2', 'SP8', 'SCGN')
dplot <- DotPlot(jy_all, features = genes_to_show, group.by = 'broad_areas',) + RotatedAxis() + coord_flip()
dplot
#ggsave(dplot, filename = 'dplot_by_broadarea_allgenes.png', path = file.path(output_dir_plot, '20220727_1'), width = 9, height = 3, dpi = 150)
```

```{r}
broad_areas = c()
jy_all$broad_areas = 'wrong'
jy_all$broad_areas[grepl('408', jy_all$area) & grepl('TC', jy_all$area)] = 'pVentral'
jy_all$broad_areas[grepl('408', jy_all$area) & grepl('CC', jy_all$area)] = 'pDorsal'
jy_all$broad_areas[grepl('164', jy_all$area) & grepl('TC', jy_all$area)] = 'aVentral'
jy_all$broad_areas[grepl('164', jy_all$area) & grepl('CC', jy_all$area)] = 'aDorsal'
```


```{r fig.height=8, fig.width=10}
big_dimplot <- function(sobj, grep_pattern){
  dp = DimPlot(sobj, cells.highlight = list(imp = which(grepl(grep_pattern, sobj$broad_areas))))
  dp <- dp + scale_color_manual(values = c('grey90', '#1982c4'), labels=c('other', grep_pattern)) + NoAxes()
}
patterns = c('AntDrs', 'AntVnt', 'PosDrs', 'PosVnt')
plots <- lapply(1:length(patterns), function(i){
    big_dimplot(jy_all, grep_pattern = patterns[i])
  })
areas = plot_grid(plotlist = plots, label_size = 10, nrow = 3)
areas
ggsave(plot = areas, filename = 'umap_broad_areas.png', path = file.path(output_dir_plot, '20220727_1'), width = 10, height = 8, dpi = 150)
```
```{r fig.height=4, fig.width=4}
DimPlot(jy_all, split.by = 'broad_areas', ncol = 2) + NoAxes() +NoLegend()#+ theme(legend.position="bottom")
```

