---
title: "st_area"
output: html_notebook
---

Written by Aunoy Poddar
May 23rd, 2022

# Process the puncta quantified raw data
```{r eval=FALSE}
current_file <- rstudioapi::getActiveDocumentContext()$path
output_file <- stringr::str_replace(current_file, '.Rmd', '.R')
knitr::purl(current_file, output = output_file)
file.edit(output_file)
```

## Import packages and functions
```{r}
library(Seurat)
library(tictoc)
library(ggplot2)
library(patchwork)
library(pheatmap)
library(RColorBrewer)
library(tidyverse)
library(gridExtra)
```

## Load the data
```{r}
data_dir = '/home/aunoy/st/arc_profiling/st_analysis/hand_annotated_data/rethresholded'
output_dir_plot = '/home/aunoy/st/arc_profiling/st_analysis/results/plots'
output_dir_tbls = '/home/aunoy/st/arc_profiling/st_analysis/results/tables'
```

### Merge both datasets and generate a metadata column that corresponds
### to the cell #
```{r}
df = data.frame()
for (file_name in list.files(data_dir)){
  print(file_name)
  #if(grepl('408_TC', file_name) | grepl('408_vMS', file_name)){
  #  next
  #}
  df_to_append <- read.table(file.path(data_dir, file_name), sep = ',', header = TRUE)
  while(length(ind <- which(df_to_append$Image.Name == "")) > 0){
    df_to_append$Image.Name[ind] <- df_to_append$Image.Name[ind -1]
  }
  #df_to_append <- df_to_append %>%
  #  dplyr::select(-1)
  if(grepl('164', file_name)){
    df_to_append <- df_to_append %>%
      dplyr::select(-X)
  }
  colnames(df_to_append) <- toupper(colnames(df_to_append))
  df_to_append <- df_to_append %>%
    mutate(area = strsplit(file_name, '.csv')[[1]])
  if(!is_empty(df)){
    df_to_append <- df_to_append %>%
          dplyr::select(colnames(df))
  }
  df <- rbind(df, df_to_append)
}
```

## Let's just test by area first

What are our hypothesis?
Different streams may reflect different "LGE, MGE, and CGE" markers
```{r}
# Take all cells in cluster 2, and find markers that separate cells in the 'g1' group (metadata
# variable 'group')
#markers <- FindMarkers(pbmc_small, ident.1 = "g1", group.by = 'groups', subset.ident = "2")
#head(x = markers)


markers <- FindMarkers(jyobj, ident.1 = "408_CC", ident.2 = "408_TC", group.by = 'area')
markers %>%
   slice_max(n = 32, order_by = avg_log2FC)
```
## Posterior CC vs TC
### CC
ASCL1 - pro... neural?
MAF1 - MGE marker later
PAX6 - CGE/LGE
RELN - signaling molecule
SST - Somatostatin
SP8 - LGE/CGE

### TC
CALB2 - CGE/LGE neuronal marker (mature)
CXCL12 - chemokine
NKX2.1 - MGE early marker
TSHZ1 - LGE marker

```{r}
VlnPlot(jyobj, features = c('MAF1', 'PAX6', 'RELN', 'SST', 'SP8', 'CALB2', 'CXCL12', 'NKX2.1', 'TSHZ1'), stack = TRUE, group.by = 'area')
```

```{r}
VlnPlot(jyobj, features = 'CXCR7', group.by = 'area')
```

```{r}
VlnPlot(jyobj, features = 'COUPTF2', group.by = 'area')
```


```{r}
markers <- FindMarkers(jyobj, ident.1 = "408_CC", ident.2 = "164_CC", group.by = 'area')
markers %>%
   slice_max(n = 32, order_by = avg_log2FC)
```
## Posterior CC vs anterior CC
### Posterior
GSX2
NKX2.1
MAF1
VIP
NCAM1
RELN

### anterior
CALB2
DLX2

```{r}
markers <- FindMarkers(jyobj, ident.1 = "408_TC", ident.2 = "164_TC", group.by = 'area')
markers %>%
   slice_max(n = 32, order_by = avg_log2FC)
```
## Posterior TC vs Anterior TC
### Posterior TC
NKX2.1
PAX6
CXCL12
ASCL1

### Anterior TC
MAF1
CXCR4
SST
COUPTF2.... how really?

```{r}
markers <- FindMarkers(jyobj, ident.1 = "408_CC", ident.2 = "408_MS_CC", group.by = 'area')
markers %>%
   slice_max(n = 32, order_by = avg_log2FC)
```
## Posterior CC vs Posterior MS to CC
### Posterior CC
PAX6
SATB2
VIP

### Posterior MS to CC
TSHZ1
NKX2.1
MAF1
VLDLR
CXCR7
PROX1
EGFR
GSX2

```{r}
markers <- FindMarkers(jyobj, ident.1 = "164_TC", ident.2 = "164_CC", group.by = 'area')
markers %>%
   slice_max(n = 32, order_by = avg_log2FC)
```
## anterior TC vs anterior CC
### anterior TC
GSX2
MAF1
LRP8
CXCR7


### anterior CC
PAX6
ASCL1
DLX2
RELN

```{r}
markers <- FindMarkers(jyobj, ident.1 = "408_TC", ident.2 = "408_dMS_TC", group.by = 'area')
markers %>%
   slice_max(n = 32, order_by = avg_log2FC)
```
## Posterior TC vs Posterior dorsal migratory stream
### Posterior TC
CXCL12
CALB2
SATB2

### dorsal migratory stream
MAF1
ASCL1
EMX1
DLX2
PROX1
SP8
LHX6
COUPTF2

```{r}
markers <- FindMarkers(jyobj, ident.1 = "408_TC", ident.2 = "408_vMS_TC", group.by = 'area')
markers %>%
   slice_max(n = 32, order_by = avg_log2FC)
```
## Posterior TC vs Posterior ventral migratory stream
### Posterior TC
SATB2
CXCL12
NXK2.1
CALB2
VIP
RELN
KIA0319
PAX6
ASCL1
GAD1

### ventral migratory stream
TBR1
LRP8

```{r}
markers <- FindMarkers(jyobj, ident.1 = "408_vMS_TC", ident.2 = "408_dMS_TC", group.by = 'area')
markers %>%
   slice_max(n = 32, order_by = avg_log2FC)
```
## posterior VMS vs anterior VMS
### vMS
TBR1 - Excitatory immature? Deep brain marker 1, highly expressed in deep layers

### dMS
ASCL1 - MASH1, proneural
MAF1 - MGE
CXCR4 - Chemokine receptor
SATB2 - Excitatory mature?
NXK2.1 - MGE
RELN - Signaling molecule

Question... what is happening to the other markers? Are they moving up or down?
So we can ignore MAF1
NXK2.1 is going down... that makes sense
CXCR4: receptor is going down, and ligand signaling is going down? Is the ligand
pulling along other cells? That would be pretty interesting
TBR1: strangely going up. Maybe if we take GAD1 cells specifically this might be different


```{r}
VlnPlot(jyobj, features = c('ASCL1', 'MAF1', 'CXCR4', 'SATB2', 'NKX2.1', 'RELN', 'CXCL12', 'TBR1'), stack = TRUE, group.by = 'area')
```


```{r}
markers <- FindMarkers(jyobj, ident.1 = "164_TC", ident.2 = "164_MS_TC", group.by = 'area')
markers %>%
   slice_max(n = 32, order_by = avg_log2FC)
```
## anterior TC vs anterior TC stream
### anterior TC
CXCR4 - Receptor 4
SATB2 - Excitatory
KIA0319 - Disease Dyslexia
CALB2 - Excitatory mature
DCDC2 - Disease Dyslexia
VIP - Mature
SST - Mature
CXCL12 - Signaling ligand

### Anterior TC stream
NXK2.1 - MGE
PAX6 - CGE/LGE Marker
SP8 - CGE/LGE
DLX2 - Broad GABAergic
