---
title: "st_clump"
output: html_notebook
---

Written by Aunoy Poddar
July 21st, 2022

# Process the puncta quantified raw data
```{r eval=FALSE}
current_file <- rstudioapi::getActiveDocumentContext()$path
output_file <- stringr::str_replace(current_file, '.Rmd', '.R')
knitr::purl(current_file, output = output_file)
file.edit(output_file)
```

## Import packages and functions
```{r}
library(Seurat)
library(tictoc)
library(ggplot2)
library(patchwork)
library(pheatmap)
library(RColorBrewer)
library(tidyverse)
library(gridExtra)
library(png)
library(cowplot)
library(magick)
library(scales)
```

## Load the data
```{r}
data_dir = '/home/aunoy/st/arc_profiling/st_analysis/hand_annotated_data/rethresholded'
clump_dir = '/home/aunoy/st/arc_profiling/st_analysis/hand_annotated_data/clumps'
meta_dir = '/home/aunoy/st/arc_profiling/st_analysis/hand_annotated_data/overlay'
output_dir_plot = '/home/aunoy/st/arc_profiling/st_analysis/results/plots'
output_dir_tbls = '/home/aunoy/st/arc_profiling/st_analysis/results/tables'
```


### Merge both datasets and generate a metadata column that corresponds
### to the cell #
```{r}
df_408 = data.frame()
for (file_name in list.files(data_dir)){
  print(file_name)
  if(grepl('164', file_name)){
    next
  }
  #if(grepl('408_TC', file_name) | grepl('408_vMS', file_name)){
  #  next
  #}
  df_to_append <- read.table(file.path(data_dir, file_name), sep = ',', header = TRUE)
  while(length(ind <- which(df_to_append$Image.Name == "")) > 0){
    df_to_append$Image.Name[ind] <- df_to_append$Image.Name[ind -1]
  }
  
  colnames(df_to_append) <- toupper(colnames(df_to_append))
  df_to_append <- df_to_append %>%
    mutate(area = strsplit(file_name, '.csv')[[1]])
  
  ## Add relative_XY_position
  
  if(!is_empty(df_408)){
    df_to_append <- df_to_append %>%
          dplyr::select(colnames(df_408))
  }
  df_408 <- rbind(df_408, df_to_append)
}
```
```{r}
df_408$IMAGE.NAME = unlist(lapply(df_408$IMAGE.NAME, gsub, pattern='_Cluster', replacement=''))
df_408$IMAGE.NAME = unlist(lapply(df_408$IMAGE.NAME, gsub, pattern='[*]', replacement=''))
df_408$IMAGE.NAME = unlist(lapply(df_408$IMAGE.NAME, gsub, pattern='X', replacement=''))
df_408$IMAGE.NAME = unlist(lapply(df_408$IMAGE.NAME, gsub, pattern='L2_', replacement='L2-'))
df_408$IMAGE.NAME = unlist(lapply(df_408$IMAGE.NAME, gsub, pattern='-L2', replacement='_L2'))
df_408$IMAGE.NAME = unlist(lapply(df_408$IMAGE.NAME, gsub, pattern='Tc_12', replacement='TC_12'))
## Missing
df_408 = df_408[df_408$IMAGE.NAME != 'Layer1', ]
df_408 = df_408[df_408$IMAGE.NAME != 'TC_1', ]
df_408 = df_408[df_408$IMAGE.NAME != 'TC_18', ]
df_408 = df_408[df_408$IMAGE.NAME != 'TC_19', ]
#df_408$IMAGE.NAME = toupper(df_408$IMAGE.NAME)
unique(df_408$IMAGE.NAME)
```


## Order the images
```{r}
unique(df_408$IMAGE.NAME)
images_ordered = c('TC_20', 'TC_17', 'TC_16', 'TC_15', 'TC_14', 'TC_13', 'TC_12', 'TC_11', 'TC_10', 'TC_9', 'TC_8', 'TC_7', 'TC_6', 'TC_5',
                   'TC_4', 'TC_3', 'TC_2', 'CC_4', 'CC_5', 'CC_6', 'CC_7', 'CC_8', 'CC_9', 'CC_10', 'CC_11', 'CC_12', 'CC_L2-3', 'CC_L2-2', 'CC_L2-1', 'CC_Cortical1', 'CC_Cortical2')
```

```{r}
x_horz = 1:length(images_ordered) * 35
y_horz = rep(0, length(images_ordered))
horz_embedding = data.frame()
df_408$X_horz = -1
df_408$Y_horz = -1
IMAGE_SIZE = 1024
## This is the size of an image in the global coordinate space
IMAGE_LEN = 25

images = list.files(meta_dir)
for(i in 1:length(images_ordered)){
    image_name = images_ordered[i]
    print(image_name)
    split_names = strsplit(image_name, '_')
    cortex = toupper(split_names[[1]][1])
    number = split_names[[1]][2]
    number_csv = paste0('_', number, '.csv')
    filename = images[grepl(cortex, images) & grepl(number_csv, images) & grepl('408', images)]
    coordinates = read.table(file.path(meta_dir, filename), sep = ',', header = TRUE)
    ## checked already that lists are equal, missing 1, 18, 19 for now, layer 1 and others
 
    ## so this is a little tricky, so need to get it right
    ## Remember, it is the top right that the coordinate is coming from, but
    ## the bottom right is the new coordinate space.
    ## so first when we get the original coordinate space, to set to relative
    ## of bottom would be the same X, but 1024 - Y
    
    ## push out the coordinates for better visualization
    #x_repelled <- (512 - coordinates$X_Coordinate_In_pixels)
    
    
    df_408[df_408$IMAGE.NAME == image_name, 'X_horz'] = (coordinates$X_Coordinate_In_pixels / 
                                                      IMAGE_SIZE * IMAGE_LEN) + y_horz[i]
    df_408[df_408$IMAGE.NAME == image_name, 'Y_horz'] = ((1024-coordinates$Y_Coordinate_In_pixels) / 
                                                      IMAGE_SIZE * IMAGE_LEN) + x_horz[i]
}
```

## We have the coordinates for 408_TC and others
```{r}
rownames(df_408) = 1:nrow(df_408)
jy_408 = df_408 %>%
  dplyr::select(-c(area, IMAGE.NAME, X_horz, Y_horz)) %>%
  t() %>%
  CreateSeuratObject()
```

## just set everything from below 1 in ratio to zero
```{r}
jy_408 <- NormalizeData(jy_408, scale.factor = 1e5) ###
normed = GetAssayData(jy_408, slot = 'data')
normed[normed < 3] = 0
jy_408 <- SetAssayData(jy_408, slot = 'data', normed)
```

```{r}
jy_408 <- FindVariableFeatures(jy_408, selection.method = "vst")
all.genes <- rownames(jy_408)
jy_408 <- ScaleData(jy_408, features = all.genes)
jy_408 <- RunPCA(jy_408, approx = FALSE)
jy_408 <- FindNeighbors(jy_408, dims = 1:30)
jy_408 <- FindClusters(jy_408, resolution = 1.5)
jy_408 <- RunUMAP(jy_408, dims = 1:30)

DimPlot(jy_408,  reduction = "umap", group.by = 'seurat_clusters') + NoAxes()
```

```{r}
hcoords = df_408 %>% dplyr::select(c('X_horz', 'Y_horz')) %>% as.matrix()
colnames(hcoords) <- c('pixel_1', 'pixel_2')

jy_408[["H"]] <- CreateDimReducObject(embeddings = hcoords, key = "pixel_", assay = DefaultAssay(jy_408))
```

### Merge both datasets and generate a metadata column that corresponds
### to the cell #
```{r}
df_164 = data.frame()
for (file_name in list.files(data_dir)){
  print(file_name)
  if(grepl('408', file_name)){
    next
  }
  #if(grepl('408_TC', file_name) | grepl('408_vMS', file_name)){
  #  next
  #}
  df_to_append <- read.table(file.path(data_dir, file_name), sep = ',', header = TRUE)
  while(length(ind <- which(df_to_append$Image.Name == "")) > 0){
    df_to_append$Image.Name[ind] <- df_to_append$Image.Name[ind -1]
  }
  
  colnames(df_to_append) <- toupper(colnames(df_to_append))
  df_to_append <- df_to_append %>%
    mutate(area = strsplit(file_name, '.csv')[[1]])
  
  ## Add relative_XY_position
  
  if(!is_empty(df_164)){
    df_to_append <- df_to_append %>%
          dplyr::select(colnames(df_164))
  }
  df_164 <- rbind(df_164, df_to_append)
}
```
```{r}
df_164$IMAGE.NAME = unlist(lapply(df_164$IMAGE.NAME, gsub, pattern='CC-', replacement='CC_'))
df_164$IMAGE.NAME = unlist(lapply(df_164$IMAGE.NAME, gsub, pattern='[*]', replacement=''))
df_164$IMAGE.NAME = unlist(lapply(df_164$IMAGE.NAME, gsub, pattern='X', replacement=''))
df_164$IMAGE.NAME = unlist(lapply(df_164$IMAGE.NAME, gsub, pattern='L2', replacement='CC_L2'))
df_164$IMAGE.NAME = unlist(lapply(df_164$IMAGE.NAME, gsub, pattern='L2_', replacement='L2-'))
df_164$IMAGE.NAME = unlist(lapply(df_164$IMAGE.NAME, gsub, pattern='-L2', replacement='_L2'))
tc_cortical_names_bad = df_164[grepl('TC', df_164$area) & grepl('Cortical', df_164$IMAGE.NAME), 'IMAGE.NAME']
df_164[grepl('TC', df_164$area) & grepl('Cortical', df_164$IMAGE.NAME), 'IMAGE.NAME'] = unlist(lapply(tc_cortical_names_bad, gsub, pattern='Cort', replacement='TC_Cort'))
cc_cortical_names_bad = df_164[grepl('CC', df_164$area) & grepl('Cortical', df_164$IMAGE.NAME), 'IMAGE.NAME']
df_164[grepl('CC', df_164$area) & grepl('Cortical', df_164$IMAGE.NAME), 'IMAGE.NAME'] = unlist(lapply(cc_cortical_names_bad, gsub, pattern='Cort', replacement='CC_Cort'))
#df_164$IMAGE.NAME = unlist(lapply(df_164$IMAGE.NAME, gsub, pattern='Tc_12', replacement='TC_12'))
## Missing
#df_164 = df_164[df_164$IMAGE.NAME != 'Layer1', ]
#df_164 = df_164[df_164$IMAGE.NAME != 'TC_1', ]
#df_164 = df_164[df_164$IMAGE.NAME != 'TC_18', ]
#df_164 = df_164[df_164$IMAGE.NAME != 'TC_19', ]
#df_164$IMAGE.NAME = toupper(df_164$IMAGE.NAME)
unique(df_164$IMAGE.NAME)
```
## Now we know that everything is equal to one another, we should load the variable

```{r}
image_names = unique(df_164$IMAGE.NAME)
# Preset these variables to negative values so I can easily check if they were updated later
df_164$X = -1
df_164$Y = -1
# set some normalization variables
## This is the size of the image when the pixel values are taken from top left down
IMAGE_SIZE = 1024
## This is the size of an image in the global coordinate space
IMAGE_LEN = 32
TC_IMAGE_HEIGHT = 410
TC_IMAGE_WIDTH = 446
CC_IMAGE_HEIGHT= 422
CC_IMAGE_WIDTH = 214

# Load the dataframe with global and relative coordinates
img_cords = read.table(file.path(meta_dir, '164_pixel_coordinates.csv'), sep = ',', header = TRUE)

images = list.files(meta_dir)
for(image_name in image_names){
    if(grepl('408', image_name)){
      next
    }
    print(image_name)
    split_names = strsplit(image_name, '_')
    cortex = toupper(split_names[[1]][1])
    number = split_names[[1]][2]
    number_csv = paste0('_', number, '.csv')
    filename = images[grepl(cortex, images) & grepl(number_csv, images) & grepl('164', images)]
    coordinates = read.table(file.path(meta_dir, filename), sep = ',', header = TRUE)
    if(image_name == "CC_L2-1"){
      coordinates = coordinates[c(1:37, 39:nrow(coordinates)), ]
    }
    if(cortex == 'CC'){ 
      print(paste('cc', filename, image_name))
      ## So if CC, we add the coordinates for TC_1 to overall image coordinates
      x_adj = img_cords[img_cords$Name == 'TC_1', 'x'] + 
                img_cords[img_cords$Name == 'G_CC1_to_TC1', 'x']
      ## Start from bottom, add the height, subtract TC_1 height, and then global CC1 to TC1
      y_adj = TC_IMAGE_HEIGHT - img_cords[img_cords$Name == 'TC_1', 'y'] +
                img_cords[img_cords$Name == 'G_CC1_to_TC1', 'y'] + CC_IMAGE_HEIGHT
    }else{
      print(paste('tc', filename, image_name))
      x_adj = 0
      y_adj = TC_IMAGE_HEIGHT
    }
    
    ## So don't do repelled for now
    #x_repelled <- (512 - coordinates$X_Coordinate_In_pixels)
    
    ## so the resized x distance is from left, so just add to the box location and adj
    df_164[df_164$IMAGE.NAME == image_name, 'X'] = (coordinates$X_Coordinate_In_pixels / 
                                                      IMAGE_SIZE * IMAGE_LEN) + 
                                                    img_cords[img_cords$Name == image_name, 'x'] + x_adj
    ## resized y distance
    df_164[df_164$IMAGE.NAME == image_name, 'Y'] = y_adj - img_cords[img_cords$Name == image_name, 'y'] - 
                                                      (coordinates$Y_Coordinate_In_pixels / IMAGE_SIZE * 
                                                      IMAGE_LEN)  
}
```



## We have the coordinates for 408_TC and others
```{r}
rownames(df_164) = 1:nrow(df_164)
jy_164 = df_164 %>%
  dplyr::select(-c(area, IMAGE.NAME, X, Y)) %>%
  t() %>%
  CreateSeuratObject()
```

## just set everything from below 1 in ratio to zero
```{r}
jy_164 <- NormalizeData(jy_164, scale.factor = 1e5) ###
normed = GetAssayData(jy_164, slot = 'data')
normed[normed < 3] = 0
jy_164 <- SetAssayData(jy_164, slot = 'data', normed)
```

```{r}
jy_164 <- FindVariableFeatures(jy_164, selection.method = "vst")
all.genes <- rownames(jy_164)
jy_164 <- ScaleData(jy_164, features = all.genes)
jy_164 <- RunPCA(jy_164, approx = FALSE)
jy_164 <- FindNeighbors(jy_164, dims = 1:30)
jy_164 <- FindClusters(jy_164, resolution = 0.8)
jy_164 <- RunUMAP(jy_164, dims = 1:30)

DimPlot(jy_164,  reduction = "umap", group.by = 'seurat_clusters') + NoAxes()
```

```{r}
unique(df_164$IMAGE.NAME)
images_ordered = c('TC_Cortical3', 'TC_Cortical2', 'TC_Cortical1', 'TC_10', 'TC_9', 'TC_8', 'TC_7', 'TC_6', 'TC_5', 'TC_4', 'TC_3', 'TC_2','TC_1','CC_2','CC_3',
           'CC_4', 'CC_5', 'CC_6', 'CC_7', 'CC_8', 'CC_9', 'CC_10',
           'CC_L2-1', 'CC_L2-2', 'CC_L2-3', 'CC_Cortical1', 'CC_Cortical2')
```

```{r}
x_horz = 1:length(images_ordered) * 35
y_horz = rep(0, length(images_ordered))
horz_embedding = data.frame()
df_164$X_horz = -1
df_164$Y_horz = -1

images = list.files(meta_dir)
for(i in 1:length(images_ordered)){
    image_name = images_ordered[i]
    print(image_name)
    split_names = strsplit(image_name, '_')
    cortex = toupper(split_names[[1]][1])
    number = split_names[[1]][2]
    number_csv = paste0('_', number, '.csv')
    filename = images[grepl(cortex, images) & grepl(number_csv, images) & grepl('164', images)]
    coordinates = read.table(file.path(meta_dir, filename), sep = ',', header = TRUE)
    if(image_name == "CC_L2-1"){
      coordinates = coordinates[c(1:37, 39:nrow(coordinates)), ]
    }
    ## checked already that lists are equal, missing 1, 18, 19 for now, layer 1 and others
 
    ## so this is a little tricky, so need to get it right
    ## Remember, it is the top right that the coordinate is coming from, but
    ## the bottom right is the new coordinate space.
    ## so first when we get the original coordinate space, to set to relative
    ## of bottom would be the same X, but 1024 - Y
    
    ## push out the coordinates for better visualization
    #x_repelled <- (512 - coordinates$X_Coordinate_In_pixels)
    
    
    df_164[df_164$IMAGE.NAME == image_name, 'X_horz'] = (coordinates$X_Coordinate_In_pixels / 
                                                      IMAGE_SIZE * IMAGE_LEN) + y_horz[i]
    df_164[df_164$IMAGE.NAME == image_name, 'Y_horz'] = ((1024-coordinates$Y_Coordinate_In_pixels) / 
                                                      IMAGE_SIZE * IMAGE_LEN) + x_horz[i]
}
```

```{r}
hcoords = df_164 %>% dplyr::select(c('X_horz', 'Y_horz')) %>% as.matrix()
colnames(hcoords) <- c('pixel_1', 'pixel_2')

jy_164[["H"]] <- CreateDimReducObject(embeddings = hcoords, key = "pixel_", assay = DefaultAssay(jy_164))
```


```{r}
jy_164<- RenameCells(jy_164, c(outer('164_', 1:ncol(jy_164), FUN=paste0)))
jy_164$area = df_164$area
jy_408<- RenameCells(jy_408, c(outer('408_', 1:ncol(jy_408), FUN=paste0)))
jy_408$area = df_408$area
jy_all <- merge(jy_164, jy_408)
```
```{r}
jy_all <- NormalizeData(jy_all, scale.factor = 1e5) ###
normed = GetAssayData(jy_all, slot = 'data')
normed[normed < 3] = 0
jy_all <- SetAssayData(jy_all, slot = 'data', normed)
```

```{r}
jy_all <- FindVariableFeatures(jy_all, selection.method = "vst")
all.genes <- rownames(jy_all)
jy_all <- ScaleData(jy_all, features = all.genes)
jy_all <- RunPCA(jy_all, approx = FALSE)
jy_all <- FindNeighbors(jy_all, dims = 1:30)
jy_all <- FindClusters(jy_all, resolution = 1.5)
jy_all <- RunUMAP(jy_all, dims = 1:30)

DimPlot(jy_all,  reduction = "umap", group.by = 'seurat_clusters') + NoAxes()
```