---
title: "st_clumps"
output: html_notebook
---

Written by Aunoy Poddar
July 21st, 2022

# Process the puncta quantified raw data
```{r eval=FALSE}
current_file <- rstudioapi::getActiveDocumentContext()$path
output_file <- stringr::str_replace(current_file, '.Rmd', '.R')
knitr::purl(current_file, output = output_file)
file.edit(output_file)
```

## Import packages and functions
```{r}
library(Seurat)
library(tictoc)
library(ggplot2)
library(patchwork)
library(pheatmap)
library(RColorBrewer)
library(tidyverse)
library(gridExtra)
library(png)
library(cowplot)
library(magick)
library(scales)
library(packcircles)
library(ggalt)
```

## Load the data
```{r}
data_dir = '/home/aunoy/st/arc_profiling/st_analysis/hand_annotated_data/rethresholded'
clump_dir = '/home/aunoy/st/arc_profiling/st_analysis/hand_annotated_data/clumps'
meta_dir = '/home/aunoy/st/arc_profiling/st_analysis/hand_annotated_data/overlay'
output_dir_plot = '/home/aunoy/st/arc_profiling/st_analysis/results/plots'
output_dir_tbls = '/home/aunoy/st/arc_profiling/st_analysis/results/tables'
```

### plot the meta data real quick
```{r}
meta_ntrscts = read.csv(file.path(clump_dir, 'meta', 'META_ntrsct.csv'), header = FALSE) %>%
  as_tibble()
```


### Merge both datasets and generate a metadata column that corresponds
### to the cell #
```{r}
df_408 = data.frame()
for (file_name in list.files(data_dir)){
  if(grepl('164', file_name)){
    next
  }
  #if(grepl('408_TC', file_name) | grepl('408_vMS', file_name)){
  #  next
  #}
  print(file_name)

  df_to_append <- read.table(file.path(data_dir, file_name), sep = ',', header = TRUE)
  
  print(df_to_append)

  while(length(ind <- which(df_to_append$Image.Name == "")) > 0){
    df_to_append$Image.Name[ind] <- df_to_append$Image.Name[ind -1]
  }
  
  colnames(df_to_append) <- toupper(colnames(df_to_append))
  df_to_append <- df_to_append %>%
    mutate(area = strsplit(file_name, '.csv')[[1]])
  
  ## Add relative_XY_position
  
  if(!is_empty(df_408)){
    df_to_append <- df_to_append %>%
          dplyr::select(colnames(df_408))
  }
  df_408 <- rbind(df_408, df_to_append)
}
```
```{r}
df_408$IMAGE.NAME = unlist(lapply(df_408$IMAGE.NAME, gsub, pattern='_Cluster', replacement=''))
df_408$IMAGE.NAME = unlist(lapply(df_408$IMAGE.NAME, gsub, pattern='[*]', replacement=''))
df_408$IMAGE.NAME = unlist(lapply(df_408$IMAGE.NAME, gsub, pattern='X', replacement=''))
df_408$IMAGE.NAME = unlist(lapply(df_408$IMAGE.NAME, gsub, pattern='L2_', replacement='L2-'))
df_408$IMAGE.NAME = unlist(lapply(df_408$IMAGE.NAME, gsub, pattern='-L2', replacement='_L2'))
df_408$IMAGE.NAME = unlist(lapply(df_408$IMAGE.NAME, gsub, pattern='Tc_12', replacement='TC_12'))
## Missing
df_408 = df_408[df_408$IMAGE.NAME != 'Layer1', ]
df_408 = df_408[df_408$IMAGE.NAME != 'TC_1', ]
df_408 = df_408[df_408$IMAGE.NAME != 'TC_18', ]
df_408 = df_408[df_408$IMAGE.NAME != 'TC_19', ]
#df_408$IMAGE.NAME = toupper(df_408$IMAGE.NAME)
unique(df_408$IMAGE.NAME)
```


## Order the images
```{r}
unique(df_408$IMAGE.NAME)
images_ordered = c('TC_20', 'TC_17', 'TC_16', 'TC_15', 'TC_14', 'TC_13', 'TC_12', 'TC_11', 'TC_10', 'TC_9', 'TC_8', 'TC_7', 'TC_6', 'TC_5',
                   'TC_4', 'TC_3', 'TC_2', 'CC_4', 'CC_5', 'CC_6', 'CC_7', 'CC_8', 'CC_9', 'CC_10', 'CC_11', 'CC_12', 'CC_L2-3', 'CC_L2-2', 'CC_L2-1', 'CC_Cortical1', 'CC_Cortical2')
```

```{r}
x_horz = 1:length(images_ordered) * 35
y_horz = rep(0, length(images_ordered))
horz_embedding = data.frame()
df_408$X_horz = -1
df_408$Y_horz = -1
df_408$clump = NaN
clump_header = '408_'
clump_files = list.files(clump_dir)
IMAGE_SIZE = 1024
## This is the size of an image in the global coordinate space
IMAGE_LEN = 25

images = list.files(meta_dir)
for(i in 1:length(images_ordered)){
    image_name = images_ordered[i]
    print(image_name)
    split_names = strsplit(image_name, '_')
    cortex = toupper(split_names[[1]][1])
    number = split_names[[1]][2]
    number_csv = paste0('_', number, '.csv')
    filename = images[grepl(cortex, images) & grepl(number_csv, images) & grepl('408', images)]
    coordinates = read.table(file.path(meta_dir, filename), sep = ',', header = TRUE)
    ## checked already that lists are equal, missing 1, 18, 19 for now, layer 1 and others
    
    ## Get the clumps
    filename = clump_files[grepl(clump_header, clump_files) & grepl(paste0(image_name, '_'),clump_files)]
    clump_df = as.data.frame(t(read.csv(file.path(clump_dir, filename), header = FALSE)))
    colnames(clump_df) = c('roi', 'cluster')
    clump_df$roi = as.numeric(clump_df$roi)
    
    image_idxs = which(df_408$IMAGE.NAME == image_name)
    clump_df$roi_idxs = image_idxs[1] + clump_df$roi - 1
    df_408[clump_df$roi_idxs, "clump"] = paste0(clump_header, image_name, '_', clump_df$cluster)
    
    ## so this is a little tricky, so need to get it right
    ## Remember, it is the top right that the coordinate is coming from, but
    ## the bottom right is the new coordinate space.
    ## so first when we get the original coordinate space, to set to relative
    ## of bottom would be the same X, but 1024 - Y
    
    ## push out the coordinates for better visualization
    #x_repelled <- (512 - coordinates$X_Coordinate_In_pixels)
    
    
    df_408[df_408$IMAGE.NAME == image_name, 'X_horz'] = (coordinates$X_Coordinate_In_pixels / 
                                                      IMAGE_SIZE * IMAGE_LEN) + y_horz[i]
    df_408[df_408$IMAGE.NAME == image_name, 'Y_horz'] = ((1024-coordinates$Y_Coordinate_In_pixels) / 
                                                      IMAGE_SIZE * IMAGE_LEN) + x_horz[i]
}
```

## We have the coordinates for 408_TC and others
```{r}
rownames(df_408) = 1:nrow(df_408)
jy_408 = df_408 %>%
  dplyr::select(-c(area, IMAGE.NAME, X_horz, Y_horz, clump)) %>%
  t() %>%
  CreateSeuratObject()
```

## just set everything from below 1 in ratio to zero
```{r}
jy_408 <- NormalizeData(jy_408, scale.factor = 1e5) ###
normed = GetAssayData(jy_408, slot = 'data')
normed[normed < 3] = 0
for(gene_name in rownames(jy_408)) {
  mdn_gene_expr = median(normed[gene_name, normed[gene_name, ] > 0])
  #print(gene_name)
  #print(mdn_gene_expr)
  #normed[gene_name, normed[gene_name, ] < mdn_gene_expr] = 0
}
jy_408 <- SetAssayData(jy_408, slot = 'data', normed)
```

```{r}
jy_408 <- FindVariableFeatures(jy_408, selection.method = "vst")
all.genes <- rownames(jy_408)
jy_408 <- ScaleData(jy_408, features = all.genes)
jy_408 <- RunPCA(jy_408, approx = FALSE)
jy_408 <- FindNeighbors(jy_408, dims = 1:30)
jy_408 <- FindClusters(jy_408, resolution = 1.5)
jy_408 <- RunUMAP(jy_408, dims = 1:30)

DimPlot(jy_408,  reduction = "umap", group.by = 'seurat_clusters') + NoAxes()
```

```{r}
jy_408$clump = df_408$clump

DimPlot(jy_408,  reduction = "umap", group.by = 'clump') + NoAxes() + NoLegend()

```


```{r}
hcoords = df_408 %>% dplyr::select(c('X_horz', 'Y_horz')) %>% as.matrix()
colnames(hcoords) <- c('pixel_1', 'pixel_2')

jy_408[["H"]] <- CreateDimReducObject(embeddings = hcoords, key = "pixel_", assay = DefaultAssay(jy_408))
```

### Merge both datasets and generate a metadata column that corresponds
### to the cell #
```{r}
df_164 = data.frame()
for (file_name in list.files(data_dir)){
  print(file_name)
  if(grepl('408', file_name)){
    next
  }
  #if(grepl('408_TC', file_name) | grepl('408_vMS', file_name)){
  #  next
  #}
  df_to_append <- read.table(file.path(data_dir, file_name), sep = ',', header = TRUE)
  while(length(ind <- which(df_to_append$Image.Name == "")) > 0){
    df_to_append$Image.Name[ind] <- df_to_append$Image.Name[ind -1]
  }
  
  colnames(df_to_append) <- toupper(colnames(df_to_append))
  df_to_append <- df_to_append %>%
    mutate(area = strsplit(file_name, '.csv')[[1]])
  
  ## Add relative_XY_position
  
  if(!is_empty(df_164)){
    df_to_append <- df_to_append %>%
          dplyr::select(colnames(df_164))
  }
  df_164 <- rbind(df_164, df_to_append)
}
```
```{r}
df_164$IMAGE.NAME = unlist(lapply(df_164$IMAGE.NAME, gsub, pattern='CC-', replacement='CC_'))
df_164$IMAGE.NAME = unlist(lapply(df_164$IMAGE.NAME, gsub, pattern='[*]', replacement=''))
df_164$IMAGE.NAME = unlist(lapply(df_164$IMAGE.NAME, gsub, pattern='X', replacement=''))
df_164$IMAGE.NAME = unlist(lapply(df_164$IMAGE.NAME, gsub, pattern='L2', replacement='CC_L2'))
df_164$IMAGE.NAME = unlist(lapply(df_164$IMAGE.NAME, gsub, pattern='L2_', replacement='L2-'))
df_164$IMAGE.NAME = unlist(lapply(df_164$IMAGE.NAME, gsub, pattern='-L2', replacement='_L2'))
tc_cortical_names_bad = df_164[grepl('TC', df_164$area) & grepl('Cortical', df_164$IMAGE.NAME), 'IMAGE.NAME']
df_164[grepl('TC', df_164$area) & grepl('Cortical', df_164$IMAGE.NAME), 'IMAGE.NAME'] = unlist(lapply(tc_cortical_names_bad, gsub, pattern='Cort', replacement='TC_Cort'))
cc_cortical_names_bad = df_164[grepl('CC', df_164$area) & grepl('Cortical', df_164$IMAGE.NAME), 'IMAGE.NAME']
df_164[grepl('CC', df_164$area) & grepl('Cortical', df_164$IMAGE.NAME), 'IMAGE.NAME'] = unlist(lapply(cc_cortical_names_bad, gsub, pattern='Cort', replacement='CC_Cort'))
#df_164$IMAGE.NAME = unlist(lapply(df_164$IMAGE.NAME, gsub, pattern='Tc_12', replacement='TC_12'))
## Missing
#df_164 = df_164[df_164$IMAGE.NAME != 'Layer1', ]
#df_164 = df_164[df_164$IMAGE.NAME != 'TC_1', ]
#df_164 = df_164[df_164$IMAGE.NAME != 'TC_18', ]
#df_164 = df_164[df_164$IMAGE.NAME != 'TC_19', ]
#df_164$IMAGE.NAME = toupper(df_164$IMAGE.NAME)
unique(df_164$IMAGE.NAME)
```
## Now we know that everything is equal to one another, we should load the variable

```{r}
image_names = unique(df_164$IMAGE.NAME)
# Preset these variables to negative values so I can easily check if they were updated later
df_164$X = -1
df_164$Y = -1
df_164$clump = NaN
clump_header = '164_'
clump_files = list.files(clump_dir)
# set some normalization variables
## This is the size of the image when the pixel values are taken from top left down
IMAGE_SIZE = 1024
## This is the size of an image in the global coordinate space
IMAGE_LEN = 32
TC_IMAGE_HEIGHT = 410
TC_IMAGE_WIDTH = 446
CC_IMAGE_HEIGHT= 422
CC_IMAGE_WIDTH = 214

# Load the dataframe with global and relative coordinates
img_cords = read.table(file.path(meta_dir, '164_pixel_coordinates.csv'), sep = ',', header = TRUE)

images = list.files(meta_dir)
for(image_name in image_names){
    if(grepl('408', image_name)){
      next
    }
    print(image_name)
    split_names = strsplit(image_name, '_')
    cortex = toupper(split_names[[1]][1])
    number = split_names[[1]][2]
    number_csv = paste0('_', number, '.csv')
    filename = images[grepl(cortex, images) & grepl(number_csv, images) & grepl('164', images)]
    coordinates = read.table(file.path(meta_dir, filename), sep = ',', header = TRUE)
    
    ## Get the clumps
    filename = clump_files[grepl(clump_header, clump_files) & grepl(paste0(image_name, '_'),clump_files)]
    if(length(filename != 0)){
      clump_df = as.data.frame(t(read.csv(file.path(clump_dir, filename), header = FALSE)))
      colnames(clump_df) = c('roi', 'cluster')
      clump_df$roi = as.numeric(clump_df$roi)
      
      if(image_name == "CC_L2-1"){
        coordinates = coordinates[c(1:37, 39:nrow(coordinates)), ]
        if(38 %in% clump_df$roi){clump_df = clump_df[clump_df$roi != 38, ]}
        clump_df$roi[clump_df$roi > 37] = clump_df$roi[clump_df$roi > 37] - 1
      }
      
      image_idxs = which(df_164$IMAGE.NAME == image_name)
      clump_df$roi_idxs = image_idxs[1] + clump_df$roi - 1
      df_164[clump_df$roi_idxs, "clump"] = paste0(clump_header, image_name, '_', clump_df$cluster)
    } else{
      print('No clumps!')
      print(image_name)
    }
    
    if(cortex == 'CC'){ 
      print(paste('cc', filename, image_name))
      ## So if CC, we add the coordinates for TC_1 to overall image coordinates
      x_adj = img_cords[img_cords$Name == 'TC_1', 'x'] + 
                img_cords[img_cords$Name == 'G_CC1_to_TC1', 'x']
      ## Start from bottom, add the height, subtract TC_1 height, and then global CC1 to TC1
      y_adj = TC_IMAGE_HEIGHT - img_cords[img_cords$Name == 'TC_1', 'y'] +
                img_cords[img_cords$Name == 'G_CC1_to_TC1', 'y'] + CC_IMAGE_HEIGHT
    }else{
      print(paste('tc', filename, image_name))
      x_adj = 0
      y_adj = TC_IMAGE_HEIGHT
    }
    
    ## So don't do repelled for now
    #x_repelled <- (512 - coordinates$X_Coordinate_In_pixels)
    
    ## so the resized x distance is from left, so just add to the box location and adj
    df_164[df_164$IMAGE.NAME == image_name, 'X'] = (coordinates$X_Coordinate_In_pixels / 
                                                      IMAGE_SIZE * IMAGE_LEN) + 
                                                    img_cords[img_cords$Name == image_name, 'x'] + x_adj
    ## resized y distance
    df_164[df_164$IMAGE.NAME == image_name, 'Y'] = y_adj - img_cords[img_cords$Name == image_name, 'y'] - 
                                                      (coordinates$Y_Coordinate_In_pixels / IMAGE_SIZE * 
                                                      IMAGE_LEN)  
}
```



## We have the coordinates for 408_TC and others
```{r}
rownames(df_164) = 1:nrow(df_164)
jy_164 = df_164 %>%
  dplyr::select(-c(area, IMAGE.NAME, X, Y, clump)) %>%
  t() %>%
  CreateSeuratObject()
```

## just set everything from below 1 in ratio to zero
```{r}
jy_164 <- NormalizeData(jy_164, scale.factor = 1e5) ###
normed = GetAssayData(jy_164, slot = 'data')
normed[normed < 3] = 0
for(gene_name in rownames(jy_164)) {
  mdn_gene_expr = median(normed[gene_name, normed[gene_name, ] > 0])
  #print(gene_name)
  #print(mdn_gene_expr)
  #normed[gene_name, normed[gene_name, ] < mdn_gene_expr] = 0
}
jy_164 <- SetAssayData(jy_164, slot = 'data', normed)
```

```{r}
jy_164 <- FindVariableFeatures(jy_164, selection.method = "vst")
all.genes <- rownames(jy_164)
jy_164 <- ScaleData(jy_164, features = all.genes)
jy_164 <- RunPCA(jy_164, approx = FALSE)
jy_164 <- FindNeighbors(jy_164, dims = 1:30)
jy_164 <- FindClusters(jy_164, resolution = 0.8)
jy_164 <- RunUMAP(jy_164, dims = 1:30)
jy_164$clump <- df_164$clump

DimPlot(jy_164,  reduction = "umap", group.by = 'seurat_clusters') + NoAxes()
```
```{r}
DimPlot(jy_164,  reduction = "umap", group.by = 'clump') + NoAxes() + NoLegend()
```

```{r}
unique(df_164$IMAGE.NAME)
images_ordered = c('TC_Cortical3', 'TC_Cortical2', 'TC_Cortical1', 'TC_10', 'TC_9', 'TC_8', 'TC_7', 'TC_6', 'TC_5', 'TC_4', 'TC_3', 'TC_2','TC_1','CC_2','CC_3',
           'CC_4', 'CC_5', 'CC_6', 'CC_7', 'CC_8', 'CC_9', 'CC_10',
           'CC_L2-1', 'CC_L2-2', 'CC_L2-3', 'CC_Cortical1', 'CC_Cortical2')
```

```{r}
x_horz = 1:length(images_ordered) * 35
y_horz = rep(0, length(images_ordered))
horz_embedding = data.frame()
df_164$X_horz = -1
df_164$Y_horz = -1

images = list.files(meta_dir)
for(i in 1:length(images_ordered)){
    image_name = images_ordered[i]
    print(image_name)
    split_names = strsplit(image_name, '_')
    cortex = toupper(split_names[[1]][1])
    number = split_names[[1]][2]
    number_csv = paste0('_', number, '.csv')
    filename = images[grepl(cortex, images) & grepl(number_csv, images) & grepl('164', images)]
    coordinates = read.table(file.path(meta_dir, filename), sep = ',', header = TRUE)
    if(image_name == "CC_L2-1"){
      coordinates = coordinates[c(1:37, 39:nrow(coordinates)), ]
    }
    ## checked already that lists are equal, missing 1, 18, 19 for now, layer 1 and others
 
    ## so this is a little tricky, so need to get it right
    ## Remember, it is the top right that the coordinate is coming from, but
    ## the bottom right is the new coordinate space.
    ## so first when we get the original coordinate space, to set to relative
    ## of bottom would be the same X, but 1024 - Y
    
    ## push out the coordinates for better visualization
    #x_repelled <- (512 - coordinates$X_Coordinate_In_pixels)
    
    
    df_164[df_164$IMAGE.NAME == image_name, 'X_horz'] = (coordinates$X_Coordinate_In_pixels / 
                                                      IMAGE_SIZE * IMAGE_LEN) + y_horz[i]
    df_164[df_164$IMAGE.NAME == image_name, 'Y_horz'] = ((1024-coordinates$Y_Coordinate_In_pixels) / 
                                                      IMAGE_SIZE * IMAGE_LEN) + x_horz[i]
}
```

```{r}
hcoords = df_164 %>% dplyr::select(c('X_horz', 'Y_horz')) %>% as.matrix()
colnames(hcoords) <- c('pixel_1', 'pixel_2')

jy_164[["H"]] <- CreateDimReducObject(embeddings = hcoords, key = "pixel_", assay = DefaultAssay(jy_164))
```


```{r}
jy_164<- RenameCells(jy_164, c(outer('164_', 1:ncol(jy_164), FUN=paste0)))
jy_164$area = df_164$area
jy_408<- RenameCells(jy_408, c(outer('408_', 1:ncol(jy_408), FUN=paste0)))
jy_408$area = df_408$area
jy_all <- merge(jy_164, jy_408)
```
```{r}
jy_all <- NormalizeData(jy_all, scale.factor = 1e5) ###
normed = GetAssayData(jy_all, slot = 'data')
normed[normed < 3] = 0
for(gene_name in rownames(jy_all)) {
  if (gene_name == 'DCX'){
    mdn_gene_expr = 0.5
    print('skip dcx')
  } else if (!gene_name %in% c('COUPTF2', 'SP8')){
    mdn_gene_expr = median(normed[gene_name, normed[gene_name, ] > 0])
  }else{
    mdn_gene_expr = quantile(normed[gene_name, normed[gene_name, ] > 0], .40)
  }

  normed[gene_name, normed[gene_name, ] < mdn_gene_expr] = 0
}
jy_all <- SetAssayData(jy_all, slot = 'data', normed)
```

```{r, fig.width=3, fig.height = 3}
jy_all <- FindVariableFeatures(jy_all, selection.method = "vst")
all.genes <- rownames(jy_all)
jy_all <- ScaleData(jy_all, features = all.genes)
jy_all <- RunPCA(jy_all, approx = FALSE)
jy_all <- FindNeighbors(jy_all, dims = 1:30)
jy_all <- FindClusters(jy_all, resolution = 0.5)
jy_all <- RunUMAP(jy_all, dims = 1:30)

DimPlot(jy_all,  reduction = "umap", group.by = 'seurat_clusters') + NoAxes()
```

```{r}
DimPlot(jy_all,  reduction = "umap", group.by = 'area') + NoAxes() # NoLegend()
```
```{r fig.width = 10, fig.height = 3}
FeaturePlot(jy_all, c('CXCL12', 'CXCR4'), cells = which(FetchData(jy_all, 'GAD1') > 0), cols = c( '#F18F01', '#048BA8'), blend= TRUE) 
```


```{r}
new.cluster.ids = c('CGE/LGE',
                    'Ex',
                    'TBR1+ CGE',
                    'CALB2+DLX2+',
                    'VIP+GAD1+',
                    'SST+LHX6+',
                    'MGE')

```

```{r}
names(new.cluster.ids) <- levels(jy_all)
jy_all <- RenameIdents(jy_all, new.cluster.ids)
```
## What are my nearest neighbors?

## Let's just look at it simply. What do clusters look like?
## What cell types are in those clusters?
## Definitely a clump graph
## Stacked barplots is a way to go
```{r}
plot_cluster_fraction <- function(sobj, clump_id){
  all_idents = levels(Idents(sobj))
  def_colors = hue_pal()(length(all_idents))
  
  clump_obj <- sobj[,sobj$clump == clump_id]
  clstrs <- as.character(Idents(clump_obj))
  clmp_ids <- clump_obj$clump
  clmp_df <- as.data.frame(cbind(clstrs, clmp_ids))
  cell_count = nrow(clmp_df)
  colnames(clmp_df) <- c('cluster', 'clump')
  
  which_colors = def_colors[which(all_idents %in% clstrs)]

  clmp_df %>% dplyr::count(clump, cluster) %>%
    ggplot(aes(x="", y=n, fill=cluster))+ 
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
    ggtitle(paste0(clump_id, ', n=', cell_count)) +
    scale_fill_manual(values = which_colors) +
  theme_void()+ NoLegend() + theme(title = element_text(face = 'bold', size = rel(0.8), hjust = 1)) # remove background, grid, numeric labels
}
plot_cluster_fraction(jy_all, '164_CC_8_0')
```
```{r, fig.height=15, fig.width = 15}
clmps = unique(jy_all$clump)
plots <- lapply(1:length(clmps), function(i){
    plot_cluster_fraction(jy_all, clmps[i])
  })
umaps = plot_grid(plotlist = plots, label_size = 3, nrow = 23)
umaps
```


## try a stacked barplot
```{r}
aClumpDF <- as.data.frame(cbind(as.character(Idents(jy_all)), jy_all$clump, jy_all$area))
colnames(aClumpDF) <- c('ctype', 'clump', 'area')

g1 <- aClumpDF %>% filter(clump != NaN) %>%
  dplyr::count(clump, ctype) %>% 
ggplot(aes(clump, n, fill=ctype)) +
  geom_bar(stat="identity")
g2 <- aClumpDF %>% filter(clump == NaN) %>%
  dplyr::count(clump, ctype) %>% 
ggplot(aes(ctype, y = n, fill = ctype)) +
  geom_bar(stat="identity") + RotatedAxis() + NoLegend()
g2
```
```{r}
aClumpDF %>% filter(clump != NaN) %>%
  dplyr::count(clump, ctype) %>% 
ggplot(aes(ctype, y = n, fill = ctype)) +
  geom_bar(stat="identity") + RotatedAxis() + NoLegend()
```
```{r}
## I want to summarize the ratio of nan to non-nan
```

```{r}
aClumpDF %>% filter(clump != NaN) %>%
  dplyr::count(ctype, area, clump) %>% 
ggplot(aes(area, n, fill=ctype)) + RotatedAxis() +
  geom_bar(stat="identity")
```

```{r}
aClumpDF %>% filter(clump != NaN) %>%
  dplyr::count(area, clump) %>%
   ggplot(aes(area, n)) + 
  geom_boxplot() + RotatedAxis()
```


```{r}
Mode <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}

aClumpDF %>% group_by(clump) %>% mutate(top_ctype=Mode(ctype))
aClumpDF$top_ctype <-  with(aClumpDF, ave(ctype, clump, FUN=Mode))
aClumpDF$top_ctype
```
```{r, fig.height = 8, fig.width = 8}

 
# Create data
#clusters <- aClumpDF %>% filter(grepl('MS', area)) %>% dplyr::count(area, clump) %>% filter(clump != NaN)
clusters <- aClumpDF %>% dplyr::count(ctype, clump) %>% filter(clump != NaN)
 
# Generate the layout. This function return a dataframe with one line per bubble. 
# It gives its center (x and y) and its radius, proportional of the value
packing <- circleProgressiveLayout(clusters$n, sizetype='area')
 
# We can add these packing information to the initial data frame
clusters <- cbind(clusters, packing)
 
# Check that radius is proportional to value. We don't want a linear relationship, since it is the AREA that must be proportionnal to the value
# plot(data$radius, data$value)
 
# The next step is to go from one center + a radius to the coordinates of a circle that
# is drawn by a multitude of straight lines.
clusters.gg <- circleLayoutVertices(packing, npoints=50)
clusters.gg$idents <- rep(clusters$ctype, each=51)
 
# Make the plot
ggplot() + 
  
  # Make the bubbles
  geom_polygon(data = clusters.gg, aes(x, y, group = id, fill=as.factor(idents)), colour = "black", alpha = 0.9) +
  
  # Add text in the center of each bubble + control its size
  geom_text(data = clusters, aes(x, y, size=n, label = clump)) +
  scale_size_continuous(range = c(1,3)) +
  
  # General theme:
  theme_void() + 
  theme(legend.position="none") +
  coord_equal()
```
```{r}
clump_meta <- data.frame()

jy_clump = jy_all[, jy_all$clump!= NaN]
tic()
for(i in 1:ncol(jy_clump)){
  # Iterate through the cells, get the neighbors for that particular cell
  cell <- colnames(jy_clump[,i])
  clump <- jy_clump[, jy_clump$clump == jy_clump$clump[i]]
  neighbors <- clump@meta.data %>% filter(clump != cell)
  probs = rep(0, length(levels(jy_all)))
  neighbor_ids <- as.numeric(neighbors$seurat_clusters)
  # Calculate the probability of each cluster type
  for(j in 1:length(unique(neighbor_ids))){
    j_class = unique(neighbor_ids)[j]
    probs[j_class] = sum(neighbor_ids == j_class) / nrow(neighbors)
  }

  clump_meta <- rbind(clump_meta, probs)
  colnames(clump_meta) <- c(outer('p', 1:length(levels(jy_all)), FUN=paste0))
}
toc()
clump_meta
```
```{r}
clumps <- as.data.frame(cbind(jy_clump@meta.data, clump_meta))
```

```{r, fig.height = 10, fig.width = 14}
ref_cluster = 1
plots = list()

for(i in 1:length(levels(unique(clumps$seurat_clusters)))){
  ref_cluster = i
  plots[[i]] <- clumps %>%
  filter(as.numeric(seurat_clusters) == ref_cluster) %>%
  dplyr::select(c(seurat_clusters, p1, p2, p3, p4, p5, p6,p7,p8,p9,p10,p11,p12,p13)) %>%
  pivot_longer(!seurat_clusters, names_to = "classes", values_to = "prob") %>%
  ggplot(aes(x = prob, fill = factor(classes, levels = c(outer('p', 1:length(levels(jy_all)), FUN=paste0))))) + geom_boxplot(notch = FALSE) + 
  ggtitle(paste(levels(jy_all)[ref_cluster], "vs other")) + scale_fill_discrete(name = 'subtypes', labels=levels(Idents(jy_all)))
 }

plot_grouped <- marrangeGrob(plots, nrow=2, ncol=2)
ggsave(filename = 'cell_specific_clustering.pdf', path = file.path(output_dir_plot, '20220808_1'), plot_grouped, height = 10, width = 14, dpi = 150)
```
```{r}
ref_cluster = 2

clumps %>%
  filter(cluster == ref_cluster) %>%
  select(c(image, p0, p1, p2, p3, p4, p5, p6)) %>%
  pivot_longer(!cluster, names_to = "classes", values_to = "prob") %>%
  ggplot(aes(x = prob, color = classes)) + geom_boxplot() + 
  ggtitle(paste("Cluster",as.character(ref_cluster-1), "vs other"))
```

```{r}
pmat <- clumps %>%
    group_by(seurat_clusters) %>%
    dplyr::select(c(p1, p2, p3, p4, p5, p6,p7,p8,p9,p10,p11,p12,p13)) %>%
    dplyr::summarise(across(everything(), list(mean))) %>%
    dplyr::select(-seurat_clusters) %>%
    as.matrix()

rownames(pmat) <- levels(Idents(jy_all))
colnames(pmat) <- rownames(pmat)
```

```{r fig.height = 8, fig.width = 8}
pheatmap(pmat, color = turbo(n = 50))
```

```{r fig.height = 5, fig.width = 6}
library("viridis")           # Load
pheatmap(pmat,color = rocket(n = 50), cluster_rows = FALSE, cluster_cols = FALSE)
```
```{r}
## I want to know the expression of different genes by the different areas
## and clumps in those respective areas

## So basically 4 plots, anterior dorsal, ventral, and posterior
## Then need the clump name per thing-a-ma-bob
## Clump versus no clump
## differences between clumps (top_ctype per clump)
```

```{r}
## Start with the barcharts

plot_functional_genes <- function(sobj, group_key, group = 'area', fxn_gene_list = NULL) {
  ## So I need to make a barchart with the average expression of the particular
  ## gene list the I care about. This can be hardcoded... here?
  if(is.null(fxn_gene_list)){
    fxn_gene_list = c('VLDLR', 'LRP8', 'CXCR4', 'CXCR7', 'CXCL12', 'CXCL14', 'NCAM1')
  }
  sbset_obj = sobj[, sobj[[group]] == group_key]
  ## I want to plot their "clumpedness," so really it's either clump or no clump as a group
  gene_expr = as.data.frame(FetchData(sbset_obj, fxn_gene_list))
  gene_expr$clump = sbset_obj$clump != "NaN"
  gene_expr %>%
    pivot_longer(!clump, names_to = 'gene', values_to = 'expr') %>%
    ggplot(aes(x = gene, y = expr, fill = clump)) +
    geom_boxplot() + theme_classic() + ggtitle(group_key) + RotatedAxis()
}
plot_functional_genes(jy_all, '164_TC')
```
```{r fig.height = 9, fig.width = 12}
## For areas
area_list = unique(jy_all$area)
plots = list()
plots <- lapply(1:length(area_list), function(i){
    plot_functional_genes(jy_all, area_list[i])
  })
vlnplots = plot_grid(plotlist = plots, label_size = 3, nrow = 9)
vlnplots
#ggsave(filename = 'img_fxnal_gene_clumps.pdf', path = file.path(output_dir_plot, '20220817_1'), vlnplots, height = 9, width = 12, dpi = 150)
```

```{r fig.height = 18, fig.width = 12}
## for images
jy_all$image = c(df_164$IMAGE.NAME, df_408$IMAGE.NAME)
image_list = unique(jy_all$image)
plots = list()
plots <- lapply(1:length(image_list), function(i){
    plot_functional_genes(jy_all, image_list[i], group = 'image')
  })
bxplots = plot_grid(plotlist = plots, label_size = 3, nrow = 12)
bxplots
ggsave(filename = 'img_fxnal_gene_clumps.pdf', path = file.path(output_dir_plot, '20220817_1'), bxplots, height = 18, width = 12, dpi = 150)
```

```{r fig.height=6, fig.width = 8}
plot_clump_expr <- function(sobj, clump_name, gene, pt_size = 8, IMAGE_SPECIFIC = FALSE) {

  sbset_obj = sobj[, df_408$IMAGE.NAME == clump_name]
  xy = Embeddings(sbset_obj, reduction = 'H')
  #expmat  = as.character(Idents(sbset_obj))
  expmat = FetchData(sbset_obj, gene)
  df <- as.data.frame(cbind(xy, expmat))
  colnames(df) <- c('x', 'y', 'ident')
  ligands = c('CXCL12', 'CXCL14', 'RELN')
  receptors = c('CXCR4', 'CXCR7', 'LRP8', 'VLDLR', 'EGFR')
  maturity = c('VIP', 'SST')
  adhesion = c('NCAM1')
  immaturity = c('DCX')
  disease = c('DCDC2', 'KIA0319')
  
  color_df = as.data.frame(rownames(sobj))
  colnames(color_df) = 'gene'
  color_df$color = '#0768FA'
  color_df$color[color_df$gene %in% ligands] = '#FFFB46'
  color_df$color[color_df$gene %in% receptors] = '#F26419'
  color_df$color[color_df$gene %in% maturity] = '#450920'
  color_df$color[color_df$gene %in% adhesion] = '#F42C04'
  color_df$color[color_df$gene %in% immaturity] = '#0CF700'
  color_df$color[color_df$gene %in% disease] = '#8FB356'
  
  
  if (IMAGE_SPECIFIC){
    title_name = clump_name
  } else{
    title_name = gene
  }
  
  #colors = hue_pal()(length(levels(Idents(jy_all))))
  #colors = colors[which(levels(Idents(jy_all)) %in% df$ident)]
  colors = c('grey90', 'grey90', color_df$color[color_df$gene == gene])
  df$x = as.numeric(df$x)
  df$y = as.numeric(df$y)
  df$clump = sbset_obj$clump
  df$ident_label = as.character(round(df$ident, digits = 2))
  df %>%
    #ggplot(aes(x = x, y = y, color = clump)) +
    #geom_point(size = 8) + theme_classic() + ggtitle(clump_name) + coord_fixed(ratio = 1) + NoAxes()  ## without cell type
    #ggplot(aes(x = x, y = y, color = factor(ident, levels = levels(Idents(sobj))))) +
    ggplot(aes(x = x, y = y, color = ident)) +
    geom_point(size = pt_size) + theme_classic() + ggtitle(title_name) + coord_fixed(ratio = 1) + NoAxes() + #scale_color_manual(values = colors) +
    geom_encircle(data = filter(df, clump != "NaN"), expand = 0.03,aes(group = clump) ) + scale_color_gradient(na.value = colors[1], low = colors[2], high = colors[3]) #+ geom_label_repel(data = filter(df, ident > 0), label = filter(df, ident > 0)[['ident_label']]) 
  #+ scale_color_gradient(limits = c(0,11))

}

plot_clump_expr(jy_408, 'TC_9', 'GAD1')
```


```{r}
plot_clump_clust <- function(sobj, clump_name, pt_size = 8) {

  sbset_obj = sobj[, df_408$IMAGE.NAME == clump_name]
  xy = Embeddings(sbset_obj, reduction = 'H')
  #expmat  = as.character(Idents(sbset_obj))
  expmat = FetchData(sbset_obj, gene)
  df <- as.data.frame(cbind(xy, expmat))
  colnames(df) <- c('x', 'y', 'ident')
  
  #colors = hue_pal()(length(levels(Idents(jy_all))))
  #colors = colors[which(levels(Idents(jy_all)) %in% df$ident)]
  colors = c('grey90', 'grey90', color_df$color[color_df$gene == gene])
  df$x = as.numeric(df$x)
  df$y = as.numeric(df$y)
  df$clump = sbset_obj$clump
  df %>%
    ggplot(aes(x = x, y = y, color = clump)) +
    geom_point(size = pt_size) + theme_classic() + ggtitle(clump_name) + coord_fixed(ratio = 1) + NoAxes() +  ## without cell type
    #ggplot(aes(x = x, y = y, color = factor(ident, levels = levels(Idents(sobj))))) +
    #ggplot(aes(x = x, y = y, color = ident)) +
    #geom_point(size = 8) + theme_classic() + ggtitle(clump_name) + coord_fixed(ratio = 1) + NoAxes() + #scale_color_manual(values = colors) +
    geom_encircle(data = filter(df, clump != "NaN"), expand = 0.03,aes(group = clump) )

}

plot_clump_clust(jy_408, 'TC_11')

```

```{r}
plot_clump_celltype <- function(sobj, clump_name,  pt_size = 8) {

  sbset_obj = sobj[, which(sobj$image == clump_name)]
  xy = Embeddings(sbset_obj, reduction = 'H')
  expmat  = as.character(Idents(sbset_obj))
  #expmat = FetchData(sbset_obj, gene)
  df <- as.data.frame(cbind(xy, expmat))
  colnames(df) <- c('x', 'y', 'ident')
  colors = hue_pal()(length(levels(Idents(jy_all))))
  colors = colors[which(levels(Idents(jy_all)) %in% df$ident)]
  #colors = c('grey90', 'grey90', color_df$color[color_df$gene == gene])
  df$x = as.numeric(df$x)
  df$y = as.numeric(df$y)
  df$clump = sbset_obj$clump
 # myplot <- 
    df %>%
    ggplot(aes(x = x, y = y, color = factor(ident, levels = levels(Idents(sobj))))) +
    geom_point(size = pt_size) + theme_classic() +# ggtitle(clump_name) + 
    coord_fixed(ratio = 1) + NoAxes() + scale_color_manual(values = colors, name = 'cluster') + 
    geom_encircle(data = filter(df, clump != "NaN"), expand = 0.03,aes(group = clump) ) + xlim(0, 32) + ylim(525, 558) +   theme_cowplot() + NoAxes() + NoLegend()#+ 
    #theme(legend.key.size=unit(0.1,'mm'),
    #    legend.text=element_text(size=4),
    #    legend.title=element_text(size=6))#+ scale_color_manual(values = colors, name = 'cluster', guide = guide_legend(override.aes = list(size=4))) +
#+ scale_color_gradient(na.value = colors[1], low = colors[2], high = colors[3])
  #+ scale_color_gradient(limits = c(0,11))
  #return(myplot)
}
jy_408$clump = jy_all$clump_plot[(ncol(jy_164)+1):ncol(jy_all)]
#jy_408$image = jy_all$image[(ncol(jy_164)+1):ncol(jy_all)]
jy_164$clump = jy_all$clump_plot[1:ncol(jy_164)]
#jy_164$image = jy_all$image[1:ncol(jy_164)]
plot_clump_celltype(jy_408, 'TC_3', pt_size = 3)
```

```{r}
dapi_img = image_read('/home/aunoy/st/arc_profiling/st_analysis/hand_annotated_data/test/408_tc3.tif')

fig <- image_graph(width = 1024, height = 1024, res = 96)
myplot <- plot_clump_celltype(jy_408, 'TC_3', pt_size = 3)
dev.off()
```
```{r}
dapi_img = image_read('/home/aunoy/st/arc_profiling/st_analysis/hand_annotated_data/test/408_tc3.tif')
myplot <- plot_clump_celltype(jy_408, 'TC_3', pt_size = 5)
ggdraw() +
  draw_image(dapi_img) +
  draw_plot(myplot, scale = 1.14)
```

```{r}
normed = GetAssayData(jy_408, slot = "data")

```


```{r, fig.height = 18, fig.width = 12}
## So the layout that I am going to want is...
## there are 32 genes that I am interested in, so on one page ideally that will be 4 by 8
## And then we can show the cell type
jy_408$image = df_408$IMAGE.NAME
jy_164$image = df_164$IMAGE.NAME
plot_cluster_profile <- function(sobj, image, pt_size = 8){
  genes = rownames(sobj)
  plots = list()
  plots <- lapply(1:length(genes), function(i){
    plot_clump_expr(sobj, image, genes[i], pt_size = pt_size)
  })
  #plots = append(list(plot_clump_clust(sobj, image, pt_size = pt_size), plot_functional_genes(sobj, image, group = 'image'), plot_clump_celltype(sobj, image, pt_size = pt_size)), plots)
  plots = append(list(plot_clump_clust(sobj, image, pt_size = pt_size), plot_functional_genes(sobj, image, group = 'image')), plots)
  all_plots = plot_grid(plotlist = plots, label_size = 1, nrow = 9)
  all_plots
}


#pdf("/home/aunoy/st/arc_profiling/st_analysis/results/plots/20220817_1/TC_clump_profiles.pdf", onefile = TRUE)
for(image in unique(df_408$IMAGE.NAME)){
  arranged = plot_cluster_profile(jy_408, image, pt_size = 5)
  ggsave(filename = paste0(image, '_408_clump_profiles.pdf'), path = file.path(output_dir_plot, '20220822_1'), arranged, 
         height = 18, width = 12)
}
#dev.off()

## Final lines
#marrangeGrob(plots, nrow=8, ncol=4)
#ml <- marrangeGrob(plots, nrow=2, ncol=2)
```


```{r, fig.height = 18, fig.width = 18}
plots = list()
plots <- lapply(1:length(unique(df_408$IMAGE.NAME)), function(i){
  plot_clump_expr(jy_408, unique(df_408$IMAGE.NAME)[i], 'COUPTF2', pt_size = 8, IMAGE_SPECIFIC = TRUE)
})
all_plots = plot_grid(plotlist = plots, label_size = 1, nrow = 6)
all_plots
ggsave(filename = paste0('408_COUPTF2_clump_profiles.pdf'), path = file.path(output_dir_plot, '20220823_1'), all_plots, 
         height = 18, width = 18)
```
```{r}
sum(FetchData(jy_all, 'GAD1') != 0) / sum(FetchData(jy_all, 'GAD1') == 0)
```

```{r fig.height = 3, fig.width = 4.5}
DimPlot(jy_all) + NoAxes()
```


```{r}
FeaturePlot(jy_all, cells = which(Idents(jy_all) == 'VIP+GAD1+'), c('COUPTF2', 'SP8', 'PROX1', 'DLX2'), cols = c('lightgrey', hue_pal()(9)[5]))
```
```{r}
FeaturePlot(jy_all, cells = which(Idents(jy_all) == 'VIP+GAD1+'), c('VIP', 'LHX6', 'NKX2.1', 'GAD1'), cols = c('lightgrey', hue_pal()(9)[5]))
```


```{r}
FeaturePlot(jy_all,  c('COUPTF2', 'SP8', 'PROX1', 'DLX2'), cols = c('lightgrey', hue_pal()(9)[5]))
```

```{r}
FeaturePlot(jy_all, c('NKX2.1', 'LHX6', 'MAF1', 'GAD1'), cols = c('lightgrey', hue_pal()(9)[9]))
```

```{r}
FeaturePlot(jy_all, c('TSHZ1', 'GSX2', 'GAD1'), cols = c('lightgrey', hue_pal()(9)[1]))
```

```{r fig.height = 3, fig.width = 4}
FeaturePlot(jy_all, 'DCX', cols = c('lightgrey', 'green')) + NoAxes() + NoLegend()
```
```{r fig.height = 6, fig.width = 15}
FeaturePlot(jy_all,  c('LHX6', 'SST'), cols = c('lightgrey', hue_pal()(7)[6]), split.by = 'area', by.col = TRUE)
```
```{r fig.height = 2, fig.widgth = 3}
genes = c('LHX6', 'SST')
plots <- lapply(1:length(genes), function(i){
    plot_features_umap(jy_all, genes[i], pt.size = 0.8, alpha = 1, color = hue_pal()(7)[6])
  })
umaps = plot_grid(plotlist = plots, label_size = 10, nrow = 1)
umaps
```
```{r fig.height = 6, fig.width = 12}
DimPlot(jy_all, split.by = 'area', ncol = 3)
```

```{r fig.width = 10, fig.height = 2}
FeaturePlot(jy_all, c('TBR1', 'COUPTF2'), cols = c('#F18F01', '#048BA8'), blend= TRUE) 
```
```{r fig.width = 10, fig.height = 3}
FeaturePlot(jy_all, c('VIP', 'SST'), cols = c( '#F18F01', '#048BA8'), blend= TRUE) 
```

```{r fig.width = 10, fig.height = 3}
FeaturePlot(jy_all, c('TBR1', 'COUPTF2'), cols = c( '#F18F01', '#048BA8'), blend= TRUE) 
```

```{r fig.width = 10, fig.height = 6}
DimPlot(jy_all, split.by = 'area', ncol = 3) 
```
```{r fig.width = 18, fig.height = 5}
FeaturePlot(jy_all, features = c('GAD1', 'DLX2'), split.by = 'area', by.col = TRUE) 
```

```{r}
jy_all
```

## Tree
```{r}
breakpoints = 1:40/20
i = 1
res_str = 'clust_tree_res.'
norm_str = 'RNA_snn_res.'
for (breakpoint in breakpoints){
  jy_all <- FindClusters(jy_all, resolution = breakpoint, verbose = FALSE)
  jy_all[[paste0(res_str, breakpoint)]] = jy_all[[paste0(norm_str, breakpoint)]]
}
```

```{r fig.height = 15, fig.width = 10}
library(clustree)
clustree(jy_all, prefix = res_str)
```

```{r fig.width = 15, fig.height = 4}
DotPlot(jy_all, features = all.genes) + RotatedAxis()
```
```{r fig.width = 8, fig.height = 2}
DotPlot(jy_all, features = all.genes, group.by = 'broad_areas') + RotatedAxis()
```

```{r}
DimPlot(jy_all, split.by = 'broad_areas', ncol = 2)
```

```{r fig.width = 1.5, fig.height =1}
DimPlot(jy_all, group.by = 'broad_areas') + NoAxes()
```

```{r}
XY_164 %>%
  ggplot(aes(x = pixel_1, y = pixel_2)) + geom_point() + x
```

