---
title: "st_nn"
output: html_notebook
---

Written by Aunoy Poddar
July 21st, 2022

# Process the puncta quantified raw data
```{r eval=FALSE}
current_file <- rstudioapi::getActiveDocumentContext()$path
output_file <- stringr::str_replace(current_file, '.Rmd', '.R')
knitr::purl(current_file, output = output_file)
file.edit(output_file)
```

## Import packages and functions
```{r}
library(Seurat)
library(tictoc)
library(ggplot2)
library(patchwork)
library(pheatmap)
library(RColorBrewer)
library(tidyverse)
library(gridExtra)
library(png)
library(cowplot)
library(magick)
library(scales)
library(packcircles)
library(ggalt)
library(cccd)
library(stringr)
library(ggfortify)
library(circlize)
library(reshape2)
library(igraph)
#library("leiden")
```

## Load the data
```{r}
data_dir = '/home/aunoy/st/arc_profiling/st_analysis/hand_annotated_data/rethresholded'
clump_dir = '/home/aunoy/st/arc_profiling/st_analysis/hand_annotated_data/clumps'
meta_dir = '/home/aunoy/st/arc_profiling/st_analysis/hand_annotated_data/overlay'
output_dir_plot = '/home/aunoy/st/arc_profiling/st_analysis/results/plots'
output_dir_tbls = '/home/aunoy/st/arc_profiling/st_analysis/results/tables'
```

### plot the meta data real quick
```{r}
meta_ntrscts = read.csv(file.path(clump_dir, 'meta', 'META_ntrsct.csv'), header = FALSE) %>%
  as_tibble()
```

### Load the data
```{r}
df_408 <- load_slice(slice = "408")
df_408 <- clean_408(df_408)
df_408 <- embed_horizontal_408(df_408)
```

## We have the coordinates for 408_TC and others
```{r}
rownames(df_408) = 1:nrow(df_408)
jy_408 = df_408 %>%
  dplyr::select(-c(area, IMAGE.NAME, X_horz, Y_horz, clump)) %>%
  t() %>%
  CreateSeuratObject()
jy_408$image <- df_408$IMAGE.NAME
```

## just set everything from below 1 in ratio to zero
```{r}
jy_408 <- NormalizeData(jy_408, scale.factor = 1e5) ###
normed = GetAssayData(jy_408, slot = 'data')
normed[normed < 3] = 0
for(gene_name in rownames(jy_408)) {
  mdn_gene_expr = median(normed[gene_name, normed[gene_name, ] > 0])
}
jy_408 <- SetAssayData(jy_408, slot = 'data', normed)
```

```{r}
jy_408 <- FindVariableFeatures(jy_408, selection.method = "vst")
all.genes <- rownames(jy_408)
jy_408 <- ScaleData(jy_408, features = all.genes)
jy_408 <- RunPCA(jy_408, approx = FALSE)
jy_408 <- FindNeighbors(jy_408, dims = 1:30)
jy_408 <- FindClusters(jy_408, resolution = 0.8)
jy_408 <- RunUMAP(jy_408, dims = 1:30)

DimPlot(jy_408,  reduction = "umap", group.by = 'seurat_clusters') + NoAxes()
```
```{r}
jy_408.markers <- FindAllMarkers(jy_408, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
jy_408.markers %>%
   group_by(cluster) %>%
   slice_max(n = 32, order_by = avg_log2FC)

```

```{r}
jy_408$clump = df_408$clump

DimPlot(jy_408,  reduction = "umap", group.by = 'clump') + NoAxes() + NoLegend()

```


```{r}
hcoords = df_408 %>% dplyr::select(c('X_horz', 'Y_horz')) %>% as.matrix()
colnames(hcoords) <- c('pixel_1', 'pixel_2')

jy_408[["H"]] <- CreateDimReducObject(embeddings = hcoords, key = "pixel_", assay = DefaultAssay(jy_408))
```

### Merge both datasets and generate a metadata column that corresponds
### to the cell #
```{r}
df_164 <- load_slice(slice = "164")
df_164 <- clean_164(df_164)
df_164 <- embed_horizontal_164(df_164)
```

## We have the coordinates for 408_TC and others
```{r}
rownames(df_164) = 1:nrow(df_164)
jy_164 = df_164 %>%
  dplyr::select(-c(area, IMAGE.NAME, X, Y, clump)) %>%
  t() %>%
  CreateSeuratObject()
jy_164$image = df_164$IMAGE.NAME
```

## just set everything from below 1 in ratio to zero
```{r}
jy_164 <- NormalizeData(jy_164, scale.factor = 1e5) ###
normed = GetAssayData(jy_164, slot = 'data')
normed[normed < 3] = 0
for(gene_name in rownames(jy_164)) {
  mdn_gene_expr = median(normed[gene_name, normed[gene_name, ] > 0])
}
jy_164 <- SetAssayData(jy_164, slot = 'data', normed)
```

```{r}
jy_164 <- FindVariableFeatures(jy_164, selection.method = "vst")
all.genes <- rownames(jy_164)
jy_164 <- ScaleData(jy_164, features = all.genes)
jy_164 <- RunPCA(jy_164, approx = FALSE)
jy_164 <- FindNeighbors(jy_164, dims = 1:30)
jy_164 <- FindClusters(jy_164, resolution = 0.8)
jy_164 <- RunUMAP(jy_164, dims = 1:30)
jy_164$clump <- df_164$clump

DimPlot(jy_164,  reduction = "umap", group.by = 'seurat_clusters') + NoAxes()
```
```{r}
DimPlot(jy_164,  reduction = "umap", group.by = 'clump') + NoAxes() + NoLegend()
```

```{r}
unique(df_164$IMAGE.NAME)
images_ordered = c('TC_Cortical3', 'TC_Cortical2', 'TC_Cortical1', 'TC_10', 'TC_9', 'TC_8', 'TC_7', 'TC_6', 'TC_5', 'TC_4', 'TC_3', 'TC_2','TC_1','CC_2','CC_3',
           'CC_4', 'CC_5', 'CC_6', 'CC_7', 'CC_9', 'CC_8', 'CC_10',
           'CC_L2-1', 'CC_L2-2', 'CC_L2-3', 'CC_Cortical1', 'CC_Cortical2')
```

```{r}
x_horz = 1:length(images_ordered) * 35
y_horz = rep(0, length(images_ordered))
horz_embedding = data.frame()
df_164$X_horz = -1
df_164$Y_horz = -1

images = list.files(meta_dir)
for(i in 1:length(images_ordered)){
    image_name = images_ordered[i]
    print(image_name)
    split_names = strsplit(image_name, '_')
    cortex = toupper(split_names[[1]][1])
    number = split_names[[1]][2]
    number_csv = paste0('_', number, '.csv')
    filename = images[grepl(cortex, images) & grepl(number_csv, images) & grepl('164', images)]
    coordinates = read.table(file.path(meta_dir, filename), sep = ',', header = TRUE)
    if(image_name == "CC_L2-1"){
      coordinates = coordinates[c(1:37, 39:nrow(coordinates)), ]
    }
    ## checked already that lists are equal, missing 1, 18, 19 for now, layer 1 and others
 
    ## so this is a little tricky, so need to get it right
    ## Remember, it is the top right that the coordinate is coming from, but
    ## the bottom right is the new coordinate space.
    ## so first when we get the original coordinate space, to set to relative
    ## of bottom would be the same X, but 1024 - Y
    
    ## push out the coordinates for better visualization
    #x_repelled <- (512 - coordinates$X_Coordinate_In_pixels)
    
    
    df_164[df_164$IMAGE.NAME == image_name, 'X_horz'] = (coordinates$X_Coordinate_In_pixels / 
                                                      IMAGE_SIZE * IMAGE_LEN) + y_horz[i]
    df_164[df_164$IMAGE.NAME == image_name, 'Y_horz'] = ((1024-coordinates$Y_Coordinate_In_pixels) / 
                                                      IMAGE_SIZE * IMAGE_LEN) + x_horz[i]
}
```

```{r}
hcoords = df_164 %>% dplyr::select(c('X_horz', 'Y_horz')) %>% as.matrix()
colnames(hcoords) <- c('pixel_1', 'pixel_2')

jy_164[["H"]] <- CreateDimReducObject(embeddings = hcoords, key = "pixel_", assay = DefaultAssay(jy_164))
```


```{r}
jy_164<- RenameCells(jy_164, c(outer('164_', 1:ncol(jy_164), FUN=paste0)))
jy_164$area = df_164$area
jy_408<- RenameCells(jy_408, c(outer('408_', 1:ncol(jy_408), FUN=paste0)))
jy_408$area = df_408$area
jy_all <- merge(jy_164, jy_408)
```
```{r}
jy_all <- NormalizeData(jy_all, scale.factor = 1e5) ###
normed = GetAssayData(jy_all, slot = 'data')
normed[normed < 3] = 0
for(gene_name in rownames(jy_all)) {
  if (gene_name == 'DCX'){
    mdn_gene_expr = 0.5
    print('skip dcx')
  } else if (!gene_name %in% c('COUPTF2', 'SP8')){
    mdn_gene_expr = median(normed[gene_name, normed[gene_name, ] > 0])
  }else{
    mdn_gene_expr = quantile(normed[gene_name, normed[gene_name, ] > 0], .40)
  }

  normed[gene_name, normed[gene_name, ] < mdn_gene_expr] = 0
}
jy_all <- SetAssayData(jy_all, slot = 'data', normed)
```

```{r, fig.width=3, fig.height = 3}
jy_all <- FindVariableFeatures(jy_all, selection.method = "vst")
all.genes <- rownames(jy_all)
jy_all <- ScaleData(jy_all, features = all.genes)
jy_all <- RunPCA(jy_all, approx = FALSE)
jy_all <- FindNeighbors(jy_all, dims = 1:30)
jy_all <- FindClusters(jy_all, resolution = 0.5)
jy_all <- RunUMAP(jy_all, dims = 1:30)

DimPlot(jy_all,  reduction = "umap", group.by = 'seurat_clusters') + NoAxes()
```

```{r}
DimPlot(jy_all,  reduction = "umap", group.by = 'area') + NoAxes() # NoLegend()
```
```{r fig.width = 10, fig.height = 3}
FeaturePlot(jy_all, c('CXCL12', 'CXCR4'), cells = which(FetchData(jy_all, 'GAD1') > 0), cols = c( '#F18F01', '#048BA8'), blend= TRUE) 
```


```{r}
new.cluster.ids = c('CGE/LGE',
                    'Ex',
                    'TBR1+ CGE',
                    'CALB2+DLX2+',
                    'VIP+GAD1+',
                    'SST+LHX6+',
                    'MGE')

```

```{r}
names(new.cluster.ids) <- levels(jy_all)
jy_all <- RenameIdents(jy_all, new.cluster.ids)
```

```{r}
## Need to extract as cell x position matrix (X, Y)
## Let's start with 5 neighbors
XY_164 = Embeddings(jy_164, 'H')
neighbors = 5

nn_graph = nng(XY_164, k = neighbors)
#XY_408 = Embeddings(jy_408, 'H')
```


```{r}
avg_same = c()
avg_othr = c()
for(i in 1:ncol(jy_164)){
  ## so I am going to iterate through each cell
  ## Get the class identity of the cell
  class_cell = Idents(jy_164)[i]
  ## Get the cells that are the same
  nearest_neighbors = as.matrix(nn_graph[[i]])
  neighbor_idents = Idents(jy_164)[nearest_neighbors[[1]]]
  same_ixs = which(neighbor_idents == class_cell)
  ## Get the cells that are not the same
  othr_ixs = which(neighbor_idents != class_cell)
  ## Get the avreage distance of same
  same_obj = dist(XY_164[c(i, nearest_neighbors[[1]][same_ixs]), ])
  avg_same = c(avg_same, mean(same_obj[1:length(same_ixs)]))
  ## Get the avreage distance of not same
  othr_obj = dist(XY_164[c(i, nearest_neighbors[[1]][othr_ixs]), ])
  avg_othr = c(avg_othr, mean(same_obj[1:length(othr_ixs)]))
}
```

```{r}
tc_csv = read_csv('/home/aunoy/st/arc_profiling/st_analysis/hand_annotated_data/clump/164_TC_3_1_assignments.csv', col_names = FALSE)
colnames(tc_csv) <- c('clump', 'asgnm')
```

```{r}
example_list <- tc_csv[1, 2]
```

```{r}
pre_str = example_list$asgnm
pre_str
```

```{r}
str1 <- gsub('\\]', '', gsub('\\[', '', pre_str))
str2 <- gsub('u', '', gsub("'", '', str1))
```

```{r message = FALSE}
## Load from 
clumps_dir = '/home/aunoy/st/arc_profiling/st_analysis/hand_annotated_data/clump/clump_data/'

clump_num_df = data.frame(img= character(0), y= integer(0), z = integer(0))
colnames(clump_num_df) <- c('img', 'pixel_ext', 'clust_num')
prev_clump = 'temp'
tic()

for(file_name in list.files(clumps_dir)){
  ### If the file is an assignment file, skip
  if(grepl('assignment', file_name)){
    next
  }
  ### We need to isolate the name, pixel_ext, # of clusters
  split_name = strsplit(file_name, '_')
  clump_name = paste(split_name[[1]][1:3], collapse = "_")
  pixel_ext = as.integer(strsplit(split_name[[1]][4], '[.]')[[1]][1])
  ### Load the file
  clump_csv <- read_csv(file.path(clumps_dir, file_name))
  if(prev_clump != clump_name){
    prev_clump = clump_name
    print(clump_name)
  }
  num_clusters = nrow(clump_csv)
  clump_num_df <- clump_num_df %>%
  add_row(img = clump_name, pixel_ext = pixel_ext, clust_num = num_clusters)
}
toc()
## 1644 seconds it taeks, so about half an hour. This is worth saving lol
```

```{r}
## Save this difficultly made file
saveRDS(clump_num_df, file.path('/home/aunoy/st/arc_profiling/st_analysis/hand_annotated_data/clump', 'clump_num_df.rds'))
```

```{r}
## Get the order
samp <- clump_num_df %>%
  filter(pixel_ext == 1) %>%
  arrange(clust_num)

order = samp$img
```


```{r fig.width = 6, fig.height = 3}
clump_num_df %>%
  #filter(pixel_ext <= 10) %>%
  arrange(clust_num) %>%
  ggplot(aes(x = img, y = clust_num, group = factor(pixel_ext))) + 
  geom_line(aes(color=factor(pixel_ext))) + 
  geom_point(aes(color=factor(pixel_ext))) + 
  scale_x_discrete(limits = order) + theme_classic() + RotatedAxis()
```

```{r}

get_numeric_assignments <- function(assignment_str){
  str1 <- gsub('\\]', '', gsub('\\[', '', assignment_str))
  str2 <- gsub('u', '', gsub("'", '', str1))
  return(as.numeric(unlist(strsplit(str2, ','))))
}

get_assignments <- function(assignment_str, image_name){
  ### breakdown
  assignment_list <- get_numeric_assignments(assignment_str)
  if(length(assignment_list) == 0){
    return(-1)
  }
  if(grepl('164', image_name)){
    sdf <- df_164
    sobj <- jy_164
  }
  else{
    sdf <- df_408
    sobj <- jy_408
  }
  img_name_abbr = gsub('..._', '', image_name)
  cell_ixs <- which(sdf$IMAGE.NAME == img_name_abbr)
  image_sobj <- sobj[, cell_ixs] 
  cell_names <- colnames(image_sobj[, assignment_list])
  ## just return the names
  cells <- jy_all[, which(colnames(jy_all) %in% cell_names)]
  ## Will we get the same response each time?
  return(cells)
}
```



```{r message = FALSE}
### So I am going to make a clump DF and also going to update jy_all
## Load from 
clumps_dir = '/home/aunoy/st/arc_profiling/st_analysis/hand_annotated_data/clump/clump_data/'
pixel_ext = '1'


features = c("...1","Area", "Perim.", "Major", "Minor", "Angle",
          "Circ.", "Feret", "%Area","MinFeret", "AR",
          "Round", "Solidity"  )

#jy_all$clump = "NaN"

clump_df = data.frame()
tic()
#[501:length(list.files(clumps_dir))]
for(file_name in list.files(clumps_dir)){
  ### If the file is an assignment file, skip
  if(!grepl(paste0('_', pixel_ext, '.csv'), file_name) || grepl('assignments', file_name)){ #|| grepl('164', file_name)){
    next
  }
  print(file_name)
  ### We need to isolate the name, pixel_ext, # of clusters
  split_name = strsplit(file_name, '_')
  clump_name = paste(split_name[[1]][1:3], collapse = "_")
  assignment_name = paste0(clump_name, '_', pixel_ext, '_assignments.csv')
  #pixel_ext = as.integer(strsplit(split_name[[1]][4], '[.]')[[1]][1])
  ### Load the file
  clump_name = gsub('Cortical_', 'Cortical', clump_name)
  clump_name = gsub('L2_', 'L2-', clump_name)
  clump_csv <- read_csv(file.path(clumps_dir, file_name))
  clump_csv$...1 <- as.character(clump_csv$...1)
  assignments_csv <- read_csv(file.path(clumps_dir, assignment_name), col_names = FALSE)
  
  temp <- data.frame()
  gtemp <- data.frame()
  ctype_names <- levels(Idents(jy_all))
  for(i in 1:nrow(clump_csv)){
    itr_name = paste0(clump_name, '_Clump_', i)
    clump_csv[i, 1] = itr_name
    assignment_str = assignments_csv[which(assignments_csv$X1 == itr_name), 2][[1]]
    cells = get_assignments(assignment_str, clump_name)
    ctypes <- matrix(0, 1, length(unique(Idents(jy_all))))
    clump_expr <- matrix(NaN, 1, length(rownames(jy_all)))
    if(class(cells) != "numeric"){
      for(j in 1:ncol(cells)) {
        ctype = which(ctype_names == Idents(cells)[[j]])
        ctypes[ctype] = ctypes[ctype] + 1
      }
      clump_expr <- rowMeans(as.matrix(GetAssayData(cells, 'data')))
      jy_all$clump[which(colnames(jy_all) %in% colnames(cells))] = clump_name
    } 
  else{
      colnames(clump_expr) <- colnames(gtemp)
    }
    temp <- rbind(temp, ctypes)
    ### This is to get average expression in clump
    gtemp <- rbind(gtemp, clump_expr)
  }
  colnames(temp) <- ctype_names
  colnames(gtemp) <- rownames(jy_all)
  clump_csv_to_add <- clump_csv %>% dplyr::select(features)
  clump_df <- rbind(clump_df, cbind(clump_csv_to_add, temp, gtemp))
  #print(assignment_name)
  #df_408 <- rbind(df_408, df_to_append)
  ### Gotta make sure that the image names are the same, there are some discrepancies
}
## Save this difficultly made file
saveRDS(clump_df, file.path('/home/aunoy/st/arc_profiling/st_analysis/hand_annotated_data/clump', 'clump_df.rds'))
toc()
```

```{r}
clump_df_408 <- readRDS(file.path('/home/aunoy/st/arc_profiling/st_analysis/hand_annotated_data/clump', 'clump_df_408.rds'))
```

```{r}
temporary
```
```{r}
clump_df <- rbind(clump_df, clump_df_408)
```

```{r}
saveRDS(clump_df, file.path('/home/aunoy/st/arc_profiling/st_analysis/hand_annotated_data/clump', 'clump_df.rds'))
```

```{r}
clump_df_164 <- readRDS(file.path('/home/aunoy/st/arc_profiling/st_analysis/hand_annotated_data/clump', 'clump_df_164.rds'))
```
```{r}
clump_df <- rbind(clump_df_164, clump_df)
```


# START HERE
```{r}
clump_df <- readRDS(file.path('/home/aunoy/st/arc_profiling/st_analysis/hand_annotated_data/clump', 'clump_df.rds'))
```



```{r}
clump_df %>%
  ggplot(aes(x = Area, y = Perim.)) + geom_point()
```
```{r}
clump_pca <- prcomp(clump_df[, 14:20], center = TRUE,scale. = TRUE)

summary(clump_pca)

```

```{r}
library(ggfortify)
autoplot(clump_pca)
```
```{r}
autoplot(clump_pca, data = clump_df, colour = 'stream')
```
```{r}
clump_df$stream = "wrong"
clump_df$stream[which(grepl('408_TC', clump_df$...1))] = "408_TC"
clump_df$stream[which(grepl('164_TC', clump_df$...1))] = "164_TC"
clump_df$stream[which(grepl('408_CC', clump_df$...1))] = "408_CC"
clump_df$stream[which(grepl('164_CC', clump_df$...1))] = "164_CC"
clump_df$stream[which(grepl('408_Cortical', clump_df$...1))] = "PCort"
clump_df$stream[which(grepl('164_TC_Cortical', clump_df$...1))] = "ATCort"
clump_df$stream[which(grepl('164_CC_Cortical', clump_df$...1))] = "ACCort"
clump_df$stream[which(grepl('408_L2', clump_df$...1))] = "PL2"
clump_df$stream[which(grepl('164_CC_L2', clump_df$...1))] = "AL2"
```

```{r}
clump_df %>%
  ggplot(aes(x = stream, y = Area)) + geom_violin()
```

## How many clumps are there?
## How big are these clumps?
## What percent of DCX positive cells are in clumps?

```{r}
asummary()
```

```{r}
clump_df %>% group_by(stream) %>%
summarize()
```

```{r}
clump_df %>%
  ggplot(aes(x = stream, y = Area)) + geom_violin()
```

```{r}
clump_df$img <- str_split_fixed(clump_df$...1, "_Clump", 2)[, 1]
```


```{r fig.width = 10, fig.height = 10}
clump_df %>%
  ggplot(aes(x = stream, y = Area, color = 'TBR1+ CGE')) + geom_point(size = clump_df$Area / 10e4, ) + RotatedAxis()
```

```{r}

subset_df <- clump_df %>%
  filter(grepl('_', stream))

clump_df %>%
  filter(grepl('_', stream)) %>%
  ggplot(aes(x = stream, y = ncell)) + geom_boxplot() + geom_point(size = subset_df$Area / 10e4, ) + RotatedAxis() + ylab('# DCX cells in clump')
```
```{r}
clump_df %>%
  filter(grepl('_', stream)) %>%
  ggplot(aes(x = stream, y = Area)) + geom_boxplot() +  RotatedAxis()
```

```{r}
library(umap)
clump_umap <- umap(clump_pca$x)
```
```{r}
umap_cds <- as.data.frame(clump_umap$layout)
colnames(umap_cds) <- c('umap1', 'umap2')

clump_df$umap1 <- umap_cds$umap1
clump_df$umap2 <- umap_cds$umap2
```

```{r}
clump_df %>%
  filter(umap2 < 10) %>%
  arrange(CALB2_pct) %>%
  ggplot(aes(x = umap1, y = umap2, color = CALB2_pct)) + geom_point(size = 0.8, alpha = 0.8)
```
```{r}
clump_df %>%
  #filter(grepl('_', stream)) %>%
  ggplot(aes(x = umap1, y = umap2, color = stream)) + geom_point(size = 0.8, alpha = 0.5)
```

```{r}
clump_df$ncell <- rowSums(clump_df[, 14:20])
```

```{r}
clump_df$MGE_pct <- clump_df$MGE / clump_df$ncell
clump_df$TBR1_pct <- clump_df$`TBR1+ CGE` / clump_df$ncell
clump_df$Ex_pct <- clump_df$Ex / clump_df$ncell
clump_df$SST_pct <- clump_df$`SST+LHX6+` / clump_df$ncell
clump_df$CALB2_pct <- clump_df$`CALB2+DLX2+` / clump_df$ncell
clump_df$VIP_pct <- clump_df$`VIP+GAD1+` / clump_df$ncell
clump_df$CGE_pct <- clump_df$`CGE/LGE` / clump_df$ncell
```

```{r}
weird_cluster <- clump_df %>%
  filter(umap2 > 10)
```
```{r}
weird_cluster
```
```{r}
clump_df$MGE_pct <- clump_df$MGE / clump_df$ncell
clump_df$TBR1_pct <- clump_df$`TBR1+ CGE` / clump_df$ncell
clump_df$Ex_pct <- clump_df$Ex / clump_df$ncell
clump_df$SST_pct <- clump_df$`SST+LHX6+` / clump_df$ncell
clump_df$CALB2_pct <- clump_df$`CALB2+DLX2+` / clump_df$ncell
clump_df$VIP_pct <- clump_df$`VIP+GAD1+` / clump_df$ncell
clump_df$CGE_pct <- clump_df$`CGE/LGE` / clump_df$ncell
```

```{r}
#clump_df$order = hclust_avg$order
bplot_df <- clump_df[hclust_avg$order, c(1, 21,25, 26:32)] %>%
  filter(MGE_pct != 'NaN') %>%
  pivot_longer(!c(...1, stream, ncell), names_to = "pct_type", values_to = "pct")
```

```{r fig.width = 18, fig.height = 3}
bplot_df  %>%
  filter(ncell > 5) %>%
  #filter(grepl('164', stream)) %>%
  ggplot(aes(x = ...1, y = pct, fill = pct_type)) +
  geom_bar(position="stack", stat="identity")  +
  theme(axis.text.x=element_blank()) + xlab('clump') #remove x axis labels) + xl
```

```{r}
dist_mat <- dist(clump_pca$x, method = 'euclidean')
hclust_avg <- hclust(dist_mat, method = 'average')
plot(hclust_avg)
```
```{r}
avg_same = c()
avg_othr = c()
for(i in 1:ncol(clump_df)){
  ## so I am going to iterate through each cell
  ## Get the class identity of the cell
  class_cell = Idents(jy_164)[i]
  ## Get the cells that are the same
  nearest_neighbors = as.matrix(nn_graph[[i]])
  neighbor_idents = Idents(jy_164)[nearest_neighbors[[1]]]
  same_ixs = which(neighbor_idents == class_cell)
  ## Get the cells that are not the same
  othr_ixs = which(neighbor_idents != class_cell)
  ## Get the avreage distance of same
  same_obj = dist(XY_164[c(i, nearest_neighbors[[1]][same_ixs]), ])
  avg_same = c(avg_same, mean(same_obj[1:length(same_ixs)]))
  ## Get the avreage distance of not same
  othr_obj = dist(XY_164[c(i, nearest_neighbors[[1]][othr_ixs]), ])
  avg_othr = c(avg_othr, mean(same_obj[1:length(othr_ixs)]))
}
```

```{r}
clump_df$max_pct <- clump_df[, 26:32] %>%
  apply(1, max)
```

```{r}
clump_df$hmg_ix <- (clump_df$max_pct - (1/7)) / (1-1/7)
```

```{r}
clump_df %>%
  filter(!is.na(hmg_ix)) %>%
  filter(ncell > 3) %>%
ggplot(aes(x=hmg_ix)) + 
  geom_histogram(color="black", fill="white")
```

```{r}
clump_3 <- clump_df %>% filter(ncell>3)
nctyp = 7
btstrp = 1000

null_dist = matrix(0, nrow = btstrp, ncol = nrow(clump_3))
tic()
for(k in 1:btstrp){
  if(k %% 250 == 0){
    print(k)
  }
  for(i in 1:nrow(clump_3)){
     cells = clump_3$ncell[i]
     samp <- rdunif(cells, 1 , 7)
     mx_pct <- max(table(samp)) / cells
     null_dist[k, i] = (mx_pct - (1/7)) / (1-1/7)
  }
}
toc()
```
```{r}
null_dist
```

```{r}
hist(null_dist)
```
```{r}
null_df <- as.data.frame(as.vector(colMeans(null_dist)))
colnames(null_df) <- 'ixs'
null_df$dist = 'null'
null_df
```

```{r}
true_df <- as.data.frame(cbind(clump_3$hmg_ix, 'true'))
colnames(true_df) <- c('ixs', 'dist')
mg_df <- rbind(null_df, true_df)
mg_df$ixs <- as.numeric(mg_df$ixs)
```

```{r}
mg_df %>%
  ggplot(aes(x=ixs, color=dist)) +
  geom_histogram(fill="white",  alpha=0.4, position="identity")
```

```{r}
jy_all$clump
```

```{r}
jy_all$in_clump <- 'Not in Clump'
jy_all$in_clump[which(jy_all$clump != "NaN")] <- 'In Clump'
```

```{r}
DotPlot(jy_all, features = c('CXCR4', 'CXCR7', 'EGFR', 'VLDLR', 'RELN', 'LRP8'), group.by = 'in_clump') + RotatedAxis()
```

```{r}
jy_all$clump_stream <- paste(jy_all$area, jy_all$in_clump)
```

```{r}
DotPlot(jy_all, features = c('CXCR4', 'CXCR7', 'EGFR', 'VLDLR', 'RELN', 'LRP8'), 
        group.by = 'clump_stream') + RotatedAxis()
```
```{r fig.height = 5, fig.width = 14}
DotPlot(jy_all, features = rownames(jy_all), group.by = 'clump_stream') + RotatedAxis()
```
```{r fig.width = 6, fig.height = 4}
DimPlot(jy_all, group.by = 'in_clump', split.by = 'area', ncol = 5)
```

```{r}
jy_all$avp = 'wrong'
jy_all$avp[which(grepl('164', jy_all$area))] = '164'
jy_all$avp[which(grepl('408', jy_all$area))] = '408'
```
```{r}
jy_all$clump_stream2 <- paste(jy_all$avp, jy_all$in_clump)
```

```{r}
jy_all$clump_plot = jy_all$clump
jy_all$clump_plot[which(jy_all$clump_type != "True Clump")] = "NaN"
```

```{r}
DotPlot(jy_all, features = c('CXCR4', 'LRP8', 'CXCR7', 'VLDLR', 'EGFR', 'CXCL12', 'CXCL14', 'RELN'), group.by = "avp") + RotatedAxis(
)
```
## Define the specific clump types
```{r}

linear = c("164_TC_10_12",
"164_TC_10_5",
"164_TC_1_1",
"164_TC_5_4",
"164_TC_7_5",
"164_TC_8_7",
"164_TC_9_1",
"164_TC_9_2",
"408_CC_12_5",
"408_TC_10_5",
"408_TC_9_5")

psuedolinear = c("408_Cortical_1_0",
"408_TC_10_3",
"164_TC_1_3",
"164_TC_Cortical1_11",
"164_CC_8_2",
"164_CC_9_3",
"164_CC_L2-1_5",
"164_CC_L2-2_4",
"164_TC_8_2",
"164_TC_8_3",
"164_TC_2_1",
"164_TC_4_9",
"164_TC_5_2",
"164_TC_5_9",
"164_TC_6_0",
"164_TC_7_5",
"164_TC_7_1",
"164_TC_7_4",
"164_TC_8_4",
"408_TC_14_4",
"408_TC_2_0",
"408_TC_2_12",
"408_TC_3_3",
"408_TC_4_11",
"408_TC_4_16",
"408_tc_4_1",
"408_TC_6_5",
"164_TC_Cortical_2_1")

big_clump = c("408_TC_7_4",
"164_TC_1_0",
"164_TC_3_1",
"408_TC_11_1",
"408_TC_12_0",
"408_TC_13_0",
"408_TC_14_0",
"408_TC_5_3",
"408_TC_15_2",
"408_TC_3_1",
"408_TC_3_0",
"164_TC_6_6",
"408_TC_11_1",
"164_TC_Cortical1_5")

```

```{r}
jy_all$clump_type = "NaN"
jy_all$clump_type[which(jy_all$clump != "NaN")] = "Small Clump"
jy_all$clump_type[which(jy_all$clump %in% linear)] = "Linear"
jy_all$clump_type[which(jy_all$clump %in% psuedolinear)] = "Psuedo-Linear"
jy_all$clump_type[which(jy_all$clump %in% big_clump)] = "True Clump"
```
```{r}
DotPlot(jy_all, features = c('CXCR4', 'LRP8', 'CXCR7', 'VLDLR', 'EGFR', 'CXCL12', 'CXCL14', 'RELN'), group.by = "clump_type") + RotatedAxis(
)
```
```{r}
jy_all$clump_reduced = 'error'
jy_all$clump_reduced[which(jy_all$clump_type %in% c('True Clump'))] = 'Clump'
jy_all$clump_reduced[which(jy_all$clump_type %in% c('NaN', 'Small Clump', 'Linear', 'Psuedo-Linear'))] = 'Individual'
```

```{r}
dp <- DotPlot(jy_all, features = c('CXCR4', 'CXCR7', 'EGFR', 'LRP8', 'VLDLR'), group.by = "clump_reduced") + RotatedAxis() + ylab("")

ggsave(plot = dp, filename = 'clump_dot_plot.pdf', path = file.path(output_dir_plot, '20221212_1'), width = 12, height = 5, units = 'cm', dpi = 300)
```
```{r}
jy_all$clump_stream <- paste(jy_all$area, jy_all$clump_type)
```

```{r}
jy_all$clump_ctype <- paste(Idents(jy_all), jy_all$clump_reduced)
```


```{r}
#DotPlot(jy_all[, which(grepl("TC", jy_all$area) & grepl("164", jy_all$area))], features = c('CXCR4', 'LRP8', 'CXCR7', 'VLDLR', 'EGFR', 'CXCL12', 'CXCL14', 'RELN'), group.by = "clump_ctype") + RotatedAxis() + coord_flip()
DotPlot(jy_all, features = c('CXCR4', 'LRP8', 'CXCR7', 'VLDLR', 'EGFR', 'CXCL12', 'CXCL14', 'RELN'), group.by = "clump_ctype") + RotatedAxis() + coord_flip()
```
```{r}
dp <- DotPlot(jy_all[, which(grepl('MS', jy_all$area))], features = c('CXCR4', 'LRP8', 'CXCR7', 'VLDLR', 'EGFR'), group.by = "clump_stream") + RotatedAxis() + ylab("")
ggsave(plot = dp, filename = 'clump_dot_plot_typestream.pdf', path = file.path(output_dir_plot, '20221212_1'), width = 15, height = 15, units = 'cm', dpi = 300)
```

## Do a chord diagram that you like

##   from to value
## 1    a  A     1
## 2    b  B     2
## 3    c  C     3

So for me, I need from cell type 1 to cell type 2

Basically

from   to.  value
CT1.   CT1
CT1 CT2
CT1 CT3

```{r}
dp <- DotPlot(jy_all[, which(grepl('MS', jy_all$area))], features = c('CXCR4', 'LRP8', 'CXCR7', 'VLDLR', 'EGFR'), group.by = "clump_type") + RotatedAxis() + ylab("")
ggsave(plot = dp, filename = 'clump_dot_plot_type.pdf', path = file.path(output_dir_plot, '20221212_1'), width = 12, height = 10, units = 'cm', dpi = 300)
```


```{r}
classes <- levels(Idents(jy_all))
n = length(classes)
c1 = rep(classes, n)
c2 = rep(classes, each=n)
c_df <- as.data.frame(cbind(c1, c2))
```

```{r}
XY_164 = Embeddings(jy_164, 'H')
neighbors = 5

nn_graph = nng(XY_164, k = neighbors)

XY_408 = Embeddings(jy_408, 'H')
nn_graph2 = nng(XY_408, k = neighbors)

clusters_164 = Idents(jy_all)[1:ncol(jy_164)]
Idents(jy_164) = clusters_164
clusters_408 = Idents(jy_all)[(ncol(jy_164)+1):ncol(jy_all)]
Idents(jy_408) = clusters_408
```


```{r}

fill_adj_matrix <- function(nn_graph, jy_obj, adj_mat, undirected = TRUE){
  adj_mat$val = 0
  added = as.data.frame(matrix(-1, 1, 2))
  colnames(added) = c('c1', 'c2')
  for(i in 1:ncol(jy_obj)){
    class_cell = Idents(jy_obj)[i]
    ## Get the cells that are the same
    nearest_neighbors = as.matrix(nn_graph[[i]])
    neighbor_idents = Idents(jy_obj)[nearest_neighbors[[1]]]
    for(n in 1:length(neighbor_idents)){
      #print(c(i, n))
      n_id = as.numeric(nearest_neighbors[[1]][n])
      neighbor = neighbor_idents[n]
      if(length(added$c2[which(added$c1 == i)] == n_id) > 0 &&
         added$c2[which(added$c1 == i)] == n_id && undirected
         ){
          #print('dup')
       } else{
         #print('yup')
        value = adj_mat$val[which(adj_mat$c1 == class_cell & adj_mat$c2 == neighbor)]
        adj_mat$val[which(adj_mat$c1 == class_cell & adj_mat$c2 == neighbor)] = value + 1
        added <- added %>% add_row(c1 = n_id, c2 = i)
      }
    }
  }
  return(adj_mat)
}

norm_adj_mat <- function(jy_obj, adj_mat){
  idents <- levels(Idents(jy_obj))
  for(ident in idents){
     id_ct <- sum(Idents(jy_obj) == ident) * neighbors
     adj_mat[which(adj_mat$c1 == ident), 3] = as.numeric(adj_mat[which(adj_mat$c1 == ident), 
                                                          3]) / id_ct
  }
  return(adj_mat)
}


adj_mat1 <- fill_adj_matrix(nn_graph, jy_164, c_df)
adj_mat2 <- fill_adj_matrix(nn_graph2, jy_408, c_df)

#adj_mat1p <-norm_adj_mat(jy_164, adj_mat1)
#adj_mat2p <-norm_adj_mat(jy_408, adj_mat2)
```

```{r}
adj_mat_final <- as.data.frame(cbind(c1, c2, adj_mat1$val + adj_mat2$val))
#adj_mat_final <- norm_adj_mat(jy_all, adj_mat_final)
colnames(adj_mat_final) <- c('from', 'to', 'value')
adj_mat_final$value <- as.numeric(adj_mat_final$value)
```

```{r}
circos.clear()
chordDiagram(adj_mat_final, self.link = 2)
```
```{r}
df2 = data.frame(start = c("a", "b", "c", "a"), end = c("a", "a", "b", "c"))
chordDiagram(df2, grid.col = 1:3, self.link = 1)
title("self.link = 1")
chordDiagram(df2, grid.col = 1:3, self.link = 2)
title("self.link = 2")

```
```{r}
mat <- dcast(adj_mat_final, from ~ to, value.var = "value") %>%
  column_to_rownames("from") %>%
  #mutate_all(.funs = readr::parse_number) %>%
  as.matrix() 
```
```{r}
circos.clear()
chordDiagram(mat, self.link = 1, grid.col = get_cluster_colors(rownames(mat)), col = col_mat)
```
```{r}
col_mat = matrix("#e5e5e5", nrow = nrow(mat), ncol = ncol(mat))
diag(col_mat) <- get_cluster_colors(rownames(mat))
#dim(col_mat) = dim(mat)  # to make sure it is a matrix
```

```{r}
XYd_164 = Embeddings(jy_164[, which(grepl('CC', jy_164$area) & grepl('MS', jy_164$area))], 'H')
XYv_164 = Embeddings(jy_164[, which(grepl('TC', jy_164$area) & grepl('MS', jy_164$area))], 'H')

nnd_graph = nng(XYd_164, k = neighbors)
nnv_graph = nng(XYv_164, k = neighbors)

XYd_408 = Embeddings(jy_408[, which(grepl('CC', jy_408$area) & grepl('MS', jy_408$area))], 'H')
XYv_408 = Embeddings(jy_408[, which(grepl('TC', jy_408$area) & grepl('MS', jy_408$area))], 'H')

nnd_graph2 = nng(XYd_408, k = neighbors)
nnv_graph2 = nng(XYv_408, k = neighbors)
```

```{r}
stream = 'CC'

adj_mat1 <- fill_adj_matrix(nn_graph, 
                            jy_164[, which(grepl(stream, jy_164$area) & grepl('MS', jy_164$area))], 
                            c_df, undirected = FALSE)
adj_mat2 <- fill_adj_matrix(nn_graph2, 
                            jy_408[, which(grepl(stream, jy_408$area) & grepl('MS', jy_408$area))], 
                            c_df, undirected = FALSE)
```
```{r}
adj_mat_final <- as.data.frame(cbind(c1, c2, adj_mat1$val + adj_mat2$val))
#adj_mat_final <- norm_adj_mat(jy_all[, which(grepl(stream, jy_all$area) & grepl('MS', jy_all$area))], adj_mat_final)
colnames(adj_mat_final) <- c('from', 'to', 'value')
adj_mat_final$value = as.numeric(adj_mat_final$value)
```

```{r}
check_adj_prob <- function(adj_mat){
  types = unique(adj_mat$from)
  for(ct in types){
    sm <- sum(adj_mat[which(adj_mat$from == ct), 3])
    print(sm)
  }
}
check_adj_prob(adj_mat_final)
```


```{r}
mat <- dcast(adj_mat_final, from ~ to, value.var = "value") %>%
  column_to_rownames("from") %>%
  #mutate_all(.funs = readr::parse_number) %>%
  as.matrix() 

circos.clear()
chordDiagram(mat, self.link = 1, grid.col = get_cluster_colors(rownames(mat)), col = col_mat)
```
Okay, so I need a nodeID for each "unique type", so just the cell types

```{r}
### Need to set up the d: edges
### and set the vertices: which are the node IDs
#adj_mat_final
net <- graph_from_adjacency_matrix(mat, mode = "directed", weighted = TRUE)
```
```{r}
net <- simplify(net, remove.multiple = F, remove.loops = T)
```

```{r}
plot(net, edge.arrow.size=.4, edge.curved=.5)
```
```{r}
V(net)$color <- get_cluster_colors(V(net)$name)

V(net)$size <- log(round(rowSums(mat) / neighbors)) * 7

# The labels are currently node IDs.
# Setting them to NA will render no labels:
V(net)$label <- NA

# Set edge width based on weight:
E(net)$width <- log(E(net)$weight)

#change arrow size and edge color:
E(net)$arrow.size <- .2
E(net)$edge.color <- "gray80"

# We can even set the network layout:
graph_attr(net, "layout") <- layout_with_fr(net)#net, center = 'CGE/LGE')
plot(net, edge.arrow.size=.4, edge.curved=.5)
```
### First maek a heatmap from images and cell types
```{r}
jy_all$slice <- NA
jy_all$slice[1:ncol(jy_164)] <- '164'
jy_all$slice[(ncol(jy_164)+1):ncol(jy_all)] <- '408'
jy_all$imgslice <- paste0(jy_all$slice, "_", jy_all$image)

ids <- levels(Idents(jy_all))
imgs <- unique(jy_all$imgslice)
jy_matrix <- matrix(-1, length(imgs), length(ids))
for(i in 1:length(imgs)){
  img <- imgs[i]
  obj <- jy_all[, which(jy_all$imgslice == img)]
  tb <- table(factor(Idents(obj), levels = ids))
  jy_matrix[i, ] <- tb / sum(tb)
}
```
```{r fig.height = 2, fig.width = 6}
rownames(jy_matrix) <- imgs
colnames(jy_matrix) <- ids
pheatmap(t(jy_matrix), cellwidth = 10, cellheight = 10, fontsize = 10,
         cluster_cols = FALSE, cluster_rows = FALSE)
```
```{r}
barplot(table(Idents(jy_all)), col = get_cluster_colors(levels(Idents(jy_all))), cex.names=0.7)
```
### Before permutation, lets just confirm that all neighbors are in same image
We have found that 69 cells have neighbors in other images. This should not be
the case and should be fixed in following analyses.
```{r}

same_img_check <- function(nn_graph, jy_obj){
  counter = 0
  for(i in 1:ncol(jy_obj)){
    cell_img = jy_obj$image[i]
    ## Get the cells that are the same
    nearest_neighbors = as.matrix(nn_graph[[i]])
    neighbor_imgs = jy_obj$image[nearest_neighbors[[1]]]
    if(any(neighbor_imgs != cell_img)){
      counter = counter + 1
    }
  }
  return(counter)
}
print(same_img_check(nn_graph, jy_164))
```


### Need to run a permutation test
```{r}

get_interactions <- function(knn_graph, obj, classes, c_df){
    c_df$val = 0
    for(i in 1:ncol(obj)){
      class_cell = Idents(obj)[i]
      ## Get the cells that are the same
      nearest_neighbors = as.matrix(nn_graph[[i]])
      neighbor_idents = Idents(obj)[nearest_neighbors[[1]]]
      for(neighbor in neighbor_idents){
        value = c_df$val[which(c_df$c1 == class_cell & c_df$c2 == neighbor)]
        c_df$val[which(c_df$c1 == class_cell & c_df$c2 == neighbor)] = value + 1
      }
    }
    return(c_df)
}
### Iterate through all images
### run 100 permutations, and get the p value from the real data
permutations = 99
neighbors = 5

### Need to set up the dataframe
classes <- levels(Idents(jy_all))
n = length(classes)
c1 = rep(classes, n)
c2 = rep(classes, each=n)
c_df <- as.data.frame(cbind(c1, c2))

## will save all into 2 different matrices
interaction_mat <- matrix(-1, nrow(c_df), length(imgs)) 
avoidance_mat <- matrix(-1, nrow(c_df), length(imgs)) 

## Need to create a jy_all embedding
embed_164 <- Embeddings(jy_164, "H")
embed_408 <- Embeddings(jy_408, "H")
jy_all[["H"]] <- CreateDimReducObject(embeddings = rbind(embed_164, embed_408), key = "pixel_", assay = DefaultAssay(jy_all))

for(i in 1:length(imgs)){
  print(paste("Permuting image", i, "of", length(imgs)))
  img <- imgs[i]
  obj <- jy_all[, which(jy_all$imgslice == img)]
  ### Create nn graph for real
  XY_obj = Embeddings(obj, 'H')
  nn_graph = nng(XY_obj, k = neighbors)
  ### Iterate through each cell type
  ### Compute the mean for this one
  data_cts <- get_interactions(nn_graph, obj, classes, c_df)
  obj_idents <- Idents(obj)
  perm_matrix = matrix(NA, nrow(c_df), permutations)
  for(permutation in 1:permutations){
    Idents(obj) <- sample(Idents(obj))
    perm_cts <- get_interactions(nn_graph, obj, classes, c_df)
    perm_matrix[, permutation] <- perm_cts$val
  }
  interaction_mat[, i] <- rowSums(perm_matrix <= data_cts$val) / (permutations + 1)
  avoidance_mat[, i] <- rowSums(perm_matrix >= data_cts$val) / (permutations + 1)
  ## count the identities
  tbl <- table(Idents(obj))
  ## If the cell type does not exist in the image, do not count the P value for the
  ## interaction... obviously
  nonexist_ixs <- which(!(c_df$c1 %in% names(tbl)) | !(c_df$c2 %in% names(tbl)))
  interaction_mat[nonexist_ixs, i] <- NA
  avoidance_mat[nonexist_ixs, i] <- NA
}
```
```{r}
## Save this difficultly made files
saveRDS(interaction_mat, file.path('/home/aunoy/st/arc_profiling/st_analysis/hand_annotated_data/', 'interaction_mat.rds'))
saveRDS(avoidance_mat, file.path('/home/aunoy/st/arc_profiling/st_analysis/hand_annotated_data/', 'avoidance_mat.rds'))
```

```{r}
plot_map <- interaction_mat
plot_map[which(plot_map >= 0.05)] = NA
pheatmap(plot_map, cluster_cols = FALSE, cluster_rows = FALSE, cex = 0.8)
```

```{r}
sum(interaction_mat < 0.05, na.rm = TRUE)
```

```{r}
min(rowMeans(interaction_mat, na.rm = TRUE))
```

```{r}
rownames(avoidance_mat) <- paste0(c_df$c1, "->", c_df$c2)
colnames(avoidance_mat) <- imgs
rownames(interaction_mat) <- paste0(c_df$c1, "->", c_df$c2)
colnames(interaction_mat) <- imgs
```

```{r}
vms_labels <- c(paste0("164_", antr_TC_MS), paste0("408_", post_TC_MS))
dms_labels <- c(paste0("164_", antr_CC_MS), paste0("408_", post_CC_MS))

sub_mat <- interaction_mat[, dms_labels]
avgs <- rowMeans(sub_mat < 0.05, na.rm = TRUE)
#avgs
```
```{r}
interaction_df <- c_df %>% add_column(value = avgs)
colnames(interaction_df) <- c('from', 'to', 'value')
mat <- dcast(interaction_df, from ~ to, value.var = "value") %>%
  column_to_rownames("from") %>%
  #mutate_all(.funs = readr::parse_number) %>%
  as.matrix() 
```
```{r}
net <- graph_from_adjacency_matrix(mat, mode = "directed", weighted = TRUE)
```

```{r}
plot(net)
```
```{r}
V(net)$color <- get_cluster_colors(V(net)$name)

V(net)$size <- table(Idents(jy_all[, which(jy_all$imgslice %in% dms_labels)]))[V(net)$name] / 5

# The labels are currently node IDs.
# Setting them to NA will render no labels:
V(net)$label <- NA

# Set edge width based on weight:
E(net)$width <- E(net)$weight * 15

#change arrow size and edge color:
E(net)$arrow.size <- .2
E(net)$edge.color <- "blue1"

# We can even set the network layout:
graph_attr(net, "layout") <- layout_as_star(net, center = 'CGE/LGE')
plot(net, edge.curved=.1)
```

```{r}
pheatmap(avoidance_mat, cluster_cols = FALSE, cluster_rows = FALSE, cex = 0.8)
```

```{r}
plot_clusters_vertical_spatial_no_grid(jy_408)
```

```{r fig.height=8, fig.width=3}
clusters = levels(Idents(jy_408))
plots <- lapply(1:length(clusters), function(i){
    plot_clusters_vertical_spatial(jy_408, cluster = clusters[i], pt.size = 0.1)
  })
verts= plot_grid(plotlist = plots, label_size = 1, nrow = 1)
#verts
#ggsave(plot = verts, filename = 'jy_408_spatial_arc_sep.pdf', path = file.path(output_dir_plot, '20221212_1'), width = 7, height = 7, units = 'cm', dpi = 300)
```

```{r}
od_idnts = c("MGE", "CGE/LGE", "TBR1+ CGE", "CALB2+DLX2+", "VIP+GAD1+", "SST+LHX6+", "Ex")
pap = plot_clusters_vertical_spatial_no_grid(jy_408, pt.size = 0.1, x_width = 40, force_idents = od_idnts)
#ggsave(plot = pap, filename = 'jy_408_spatial_arc_sep_od.pdf', path = file.path(output_dir_plot, '20221212_1'), width = 7, height = 7, units = 'cm', dpi = 300)
pap
```


