---
title: "st_profiling"
output: html_notebook
---

Written by Aunoy Poddar
May 23rd, 2022

# Process the puncta quantified raw data
```{r eval=FALSE}
current_file <- rstudioapi::getActiveDocumentContext()$path
output_file <- stringr::str_replace(current_file, '.Rmd', '.R')
knitr::purl(current_file, output = output_file)
file.edit(output_file)
```

## Import packages and functions
```{r}
library(Seurat)
library(tictoc)
library(ggplot2)
library(patchwork)
library(pheatmap)
library(RColorBrewer)
library(tidyverse)
library(gridExtra)
```

## Load the data
```{r}
data_dir = '/home/aunoy/st/arc_profiling/st_analysis/hand_annotated_data/rethresholded'
output_dir_plot = '/home/aunoy/st/arc_profiling/st_analysis/results/plots'
output_dir_tbls = '/home/aunoy/st/arc_profiling/st_analysis/results/tables'
```

### Merge both datasets and generate a metadata column that corresponds
### to the cell #
```{r}
df = data.frame()
for (file_name in list.files(data_dir)){
  print(file_name)
  #if(grepl('408_TC', file_name) | grepl('408_vMS', file_name)){
  #  next
  #}
  df_to_append <- read.table(file.path(data_dir, file_name), sep = ',', header = TRUE)
  while(length(ind <- which(df_to_append$Image.Name == "")) > 0){
    df_to_append$Image.Name[ind] <- df_to_append$Image.Name[ind -1]
  }
  #df_to_append <- df_to_append %>%
  #  dplyr::select(-1)
  if(grepl('164', file_name)){
    df_to_append <- df_to_append %>%
      dplyr::select(-X)
  }
  colnames(df_to_append) <- toupper(colnames(df_to_append))
  df_to_append <- df_to_append %>%
    mutate(area = strsplit(file_name, '.csv')[[1]])
  if(!is_empty(df)){
    df_to_append <- df_to_append %>%
          dplyr::select(colnames(df))
  }
  df <- rbind(df, df_to_append)
}
```

```{r}
### right now i want experiment # for the day and overwrite to be false
# 
# ## Write to file
# date <- gsub('-', '', Sys.Date())
# exp_num <- '1'
# folder <- paste0(date, '_', exp_num)
# 
# ## check if folder exists, if not, then proceed
# expltdir <- file.path(output_dir_plot, folder)
# extbldir <- file.path(output_dir_plot, folder)
# 
# 
# if(dir.exists(expltdir) || dir.exists(extbldir)){
#   quit('Folder exists. Set --overwrite to TRUE to replace folder')
# }
# 
# ## Create the directories
# dir.create(expltdir)
# dir.create(extbldir)
```


### Add the cellnames as rownames
```{r}
rownames(df) <- c(outer(c('C'), 1:dim(df)[1], FUN=paste0))
```

## Define the different gene sets based on conversation with JY
```{r}
migra = toupper(c('Dcx', 'Lrp8', 'Reln', 'Dcdc2', 'Ncam1', 'Kia0319', 'Vldlr'))
#CGE = toupper(c('Egfr', 'Vip', 'Prox1'))
#LGE = toupper(c('Tshz1', 'Gsx2', 'Emx1'))
#MGE = toupper(c('Lhx6', 'Maf1', 'Sst'))
CGE = toupper(c('Egfr', 'Prox1'))
LGE = toupper(c('Tshz1', 'Gsx2', 'Emx1'))
MGE = toupper(c('Lhx6', 'Maf1', 'Nkx2.1'))
CGE_LGE = toupper(c('Scgn', 'Couptf2', 'Sp8', 'Calb2', 'Pax6'))
GABA = toupper(c('Dlx2', 'Gad1'))
mature_IN = toupper(c('Gad1', 'Vip', 'Sst'))
progen_IN = toupper(c('Dlx2'))
Excit = toupper(c('Eomes', 'Tbr1', 'Satb2'))
ligand = toupper(c('Reln', 'Cxcl12', 'Cxcl14'))
recept = toupper(c('Lrp8', 'Cxcr7', 'Cxcr4', 'Vldlr'))
```

## Heatmaps

### Rearrange the data to wide for heatmap
```{r}
df_longer <- df %>%
  rownames_to_column('Cell') %>%
  dplyr::select(-area) %>%
  pivot_longer(!Cell, names_to = 'Gene', values_to = "Puncta2Nuc_IR")

df_wide <- df %>%
  rownames_to_column('Cell')%>%
  dplyr::select(-area) %>%
  pivot_longer(!Cell, names_to = 'Gene', values_to = "Puncta2Nuc_IR") %>%
  pivot_wider(names_from = Gene, values_from = Puncta2Nuc_IR)
```


## some quick heatmap business

```{r}
### log(x+1) function
log1 <- function(x) {
   return(log(x+1))
}

### Scale and then log+1
log1_and_mult <- function(x) {
   return(log1(x*1e4))
}

### Get the numeric values only
df_num <- df_wide %>%
  column_to_rownames('Cell')

### Normalize to cell total
### Log + Multiply
### Center and scale
scaled_mat <- df_num %>%
  sweep(1, rowSums(df_num), '/') %>%
  log1_and_mult() #%>%
  #apply(1, scale)

### Apply separate clustering, need to look into why 
hr <- hclust(as.dist(1-cor(t(scaled_mat), method="pearson")), method = "complete")
hc <- hclust(as.dist(1-cor(scaled_mat, method="spearman")), method="complete")

annotation <- data.frame(area = factor(df$area))
rownames(annotation) <- rownames(df) # check out the row names of annotation

rownames(scaled_mat) <- colnames(df_num)
scaled_mat %>%
  pheatmap(annotation_col = annotation, 
           color = colorRampPalette(rev(brewer.pal(n = 7, name = "RdYlBu")))(100),
  #breaks = seq(from= -5, to = 5, by = 11/100.), 
  cluster_rows = hr, cluster_cols = hc, 
  #cluster_rows = TRUE, cluster_cols = TRUE, 
  #clustering_distance_rows = "correlation", 
  #clustering_distance_cols = "correlation",
  fontsize_row = 8, fontsize_col = 4, show_colnames = FALSE,
           show_rownames = TRUE, cell_width = 6, cellheight = 8)#,
          #filename = file.path(output_dir, 'log.png'))
```
### By area, not dendogram
```{r}
rownames(scaled_mat) <- colnames(df_num)
scaled_mat %>%
  pheatmap(annotation_col = annotation, 
           color = colorRampPalette(rev(brewer.pal(n = 7, name = "RdYlBu")))(100),
  #breaks = seq(from= -5, to = 5, by = 11/100.), 
  cluster_rows = hr, cluster_cols = FALSE, 
  #cluster_rows = TRUE, cluster_cols = TRUE, 
  #clustering_distance_rows = "correlation", 
  #clustering_distance_cols = "correlation",
  fontsize_row = 8, fontsize_col = 4, show_colnames = FALSE,
           show_rownames = TRUE, cell_width = 6, cellheight = 8)#,
          # filename = '/home/aunoy/pheatmap_logz_norm.png')
```


```{r}
dist_mat <- as.dist(1-cor(scaled_mat, method="spearman"))
dist_mat %>%
pheatmap(annotation_col = annotation,
         color = colorRampPalette(rev(brewer.pal(n = 7, name = "RdYlBu")))(100),
        cluster_rows = TRUE, cluster_cols = TRUE,
fontsize_row = 8, fontsize_col = 4, show_colnames = FALSE,
         show_rownames = FALSE, cell_width = 0.1, cellheight = 0.3)#,
    #filename = file.path(output_dir, 'spearmann_log.png'))
```


```{r}
df_longer %>%
  filter(Gene == 'Gsx2') %>%
  ggplot(aes(x=Puncta2Nuc_IR)) + 
  geom_histogram(color="black", fill="white")
```
```{r}
plots = list()
save = FALSE
all_genes <- df %>% 
  dplyr::select(-area) %>%
  colnames()

for (i in 1:length(all_genes)){
  plots[[i]] <- df_longer %>%
  filter(Gene == all_genes[i]) %>%
  mutate(log_norm = log1_and_mult(Puncta2Nuc_IR)) %>%
  ggplot(aes(x=log_norm, label = Gene)) + 
  geom_histogram(color="black", fill="white") + 
  labs(title=all_genes[i])+
  theme_classic()
}

#gridExtra::grid.arrange(grobs = plots, ncol = 4, nrow = 8, lengths=2:6)
if (save){
  ml <- marrangeGrob(plots, nrow=2, ncol=2)
  ggsave("/home/aunoy/raw_histograms.pdf", ml)
} else{
  marrangeGrob(plots, nrow=2, ncol=2)
}
```

### process data in Seurat object

```{r}
jyobj <- df %>%
  dplyr::select(-c(area, IMAGE.NAME)) %>%
  t() %>%
  CreateSeuratObject()
```


```{r}
jyobj <- NormalizeData(jyobj, scale.factor = 1e5) ###
sum(jyobj@assays$RNA[,] < 1)

```
### plot highly variable genes
```{r}
jyobj <- FindVariableFeatures(jyobj, selection.method = "vst")

# Identify the 10 most highly variable genes
top10 <- head(VariableFeatures(jyobj), 10)

# plot variable features with and without labels
plot1 <- VariableFeaturePlot(jyobj) + theme(axis.title.x = element_text(size = 10), axis.text.x = element_text(size = 6))
plot2 <- LabelPoints(plot = plot1, points = top10, repel = TRUE) + theme(axis.title.x = element_text(size = 10), axis.text.x = element_text(size = 6))
plot1 + plot2 + theme(axis.title.y = element_text(size = 10))
#ggsave(file.path(output_dir, 'vst_plot.png'))
```

```{r}
all.genes <- rownames(jyobj)
jyobj <- ScaleData(jyobj, features = all.genes)
```

```{r}
jyobj <- RunPCA(jyobj, features = VariableFeatures(object = jyobj), approx = FALSE)
print(jyobj[["pca"]], dims = 1:5, nfeatures = 5)
```
```{r}
VizDimLoadings(jyobj, dims = 1:2, reduction = "pca")
```

```{r}
jyobj$area <- df$area
DimPlot(jyobj, reduction = "pca", group.by = 'area')

```
```{r}
DimHeatmap(jyobj, dims = 1,  balanced = TRUE)
```

```{r}
DimHeatmap(jyobj, dims = 1:15, balanced = TRUE)
```

```{r}
# jyobj <- JackStraw(jyobj, num.replicate = 100)
# jyobj <- ScoreJackStraw(jyobj, dims = 1:20)
# 
# JackStrawPlot(jyobj, dims = 1:15)
```
```{r}
ElbowPlot(jyobj)
```

## PC30,resolution 0.5

```{r}
## dont' do 
gs <- list(dims = c(30),
           res = c(0.8)) %>% 
  cross_df() # Convert to data frame grid

getclusters <- function(dims, res, jyobj){
  y <- FindNeighbors(jyobj, dims = 1:dims)
  x <- FindClusters(y, resolution = res)
  return (length(unique(x$seurat_clusters)))
}

gs <- gs %>% mutate(clusters = pmap(gs, getclusters, jyobj))

#jyobj <- FindNeighbors(jyobj, dims = 1:30)
#jyobj <- FindClusters(jyobj, resolution = 0.5)
```

```{r}
gs$clusters <- do.call(rbind, gs$clusters)
```

```{r}
gs %>%
  filter(clusters < 40) %>%
  ggplot(aes(x = dims, y = clusters, group = res, color = factor(res))) + geom_line() +
  theme_classic() + ggtitle('UMAP Clustering Parameters') + labs(color = 'resolution')
```

```{r}
head(Idents(jyobj), 3)

```

```{r}
## dont' do 
gs <- list(res = seq(0.1, 1, 0.05))

getclusters <- function(res, jyobj){
  y <- FindNeighbors(jyobj, dims = 1:30)
  x <- FindClusters(y, resolution = res)
  return (length(unique(x$seurat_clusters)))
}

gs <- gs %>% mutate(clusters = pmap(gs, getclusters, jyobj))

#jyobj <- FindNeighbors(jyobj, dims = 1:30)
#jyobj <- FindClusters(jyobj, resolution = 0.5)
```

```{r}
clustering = pmap(gs, getclusters, jyobj)
clustering <- unlist(clustering, recursive = FALSE)

clust_plot = cbind(gs$res, clustering)
```

```{r}
colnames(clust_plot) = c('res', 'clustering')
clust_plot %>%
  as_data_frame() %>%
ggplot(aes(x = res, y = clustering)) + geom_line() + theme_classic()
```
```{r}

```


```{r}
gs %>%
  filter(clusters < 40) %>%
  ggplot(aes(x = dims, y = clusters, group = res, color = factor(res))) + geom_line() +
  theme_classic() + ggtitle('UMAP Clustering Parameters') + labs(color = 'resolution')
```


```{r}
jyobj <- RunUMAP(jyobj, dims = 1:30)

new.cluster.ids <- c("Excitatory Neuron", "Ganglionic Eminences?", "GABAergic Projection Neuron","Mature CGE VIP+ INs", "Immature
CALB2+ CGE INs", "Ganglionic Eminences 1?", "Mature MGE SST+ INs", "Dorsal LGE", "Cortical Layer 2 Neurons")
names(new.cluster.ids) <- levels(jyobj)
jyobj <- RenameIdents(jyobj, new.cluster.ids)
DimPlot(jyobj, reduction = "umap", pt.size = 1) + NoAxes() #+ NoLegend() + NoAxes()


DimPlot(jyobj, reduction = "umap")
```
```{r}
getarea <- function(abbr){
  print(length(abbr))
  ant <- grepl('164', abbr)
  ap <- ifelse(ant, 'Anterior', 'Posterior')
  cc <- grepl('CC', abbr)
  tc <- ifelse(cc, 'Cingulate', 'Temporal')
  ms <- grepl('MS', abbr)
  if(length(ms) > 1){
    print(ms)
  }
  msnms <- ifelse(ms, 'Migratory', '')
  
  if(ms && !cc){
    dms <- grepl('d', abbr)
    dv <- ifelse(dms, 'Dorsal ', 'Ventral ')
  }
  else{dv = ''}
  
  if(ms){
    return(paste0(dv, msnms, ' to ', ap, ' ', tc, ' Cortex'))
  }
  else{return(paste(ap, tc, 'Cortex'))}
}

getAbbr <- function(abbr){
  print(length(abbr))
  ant <- grepl('164', abbr)
  ap <- ifelse(ant, 'A', 'P')
  cc <- grepl('CC', abbr)
  tc <- ifelse(cc, 'CC', 'TC')
  ms <- grepl('MS', abbr)

  msnms <- ifelse(ms, 'MS', '')
  
  if(ms && !cc){
    dms <- grepl('d', abbr)
    dv <- ifelse(dms, '', ' 2')
  }
  else{dv = ''}
  #"MS into "
  if(ms){
    #return(paste0(dv, msnms, ' into ', ap, ' ', tc, ' Cortex'))
    if(paste0(msnms, ' into ', ap, tc, dv) == 'MS into ATC 2'){
      return('MS into PC')
    }
    return(paste0(msnms, ' into ', ap, tc, dv))
  }
  else{return(paste0(ap, tc))}
}
simp <- jyobj$area %>% as_tibble() %>% rename(abbr = value)
jyobj$areaAbbr <- do.call(rbind, pmap(simp, getAbbr))
#jyobj$ant_post <- factor(grepl('164', df$area), labels = c('posterior', 'anterior'))

DimPlot(jyobj, reduction = "umap", split.by = 'areaAbbr') + ggtitle('spatial location') +
  NoAxes()  + facet_wrap(~areaAbbr)
```

## Compute scores for groups of genes

```{r}
jyobj.markers <- FindAllMarkers(jyobj, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
jyobj.markers %>%
   group_by(cluster) %>%
   slice_max(n = 32, order_by = avg_log2FC)
```

# PC30,resolution 0.8

```{r}
jyobj <- FindNeighbors(jyobj, dims = 1:30)
jyobj <- FindClusters(jyobj, resolution = 0.8)
```

```{r}
head(Idents(jyobj), 3)

```

```{r}
jyobj <- RunUMAP(jyobj, dims = 1:30)

DimPlot(jyobj, reduction = "umap", group.by = 'seurat_clusters')
```
```{r}
jyobj$ant_post <- factor(grepl('164', jyobj$area), labels = c('posterior', 'anterior'))
jyobj$MS <- factor(grepl('MS', jyobj$area), labels = c('non-migratory (cortex)', 'migratory'))
jyobj$CCvTC <- factor(grepl('CC', jyobj$area), labels = c('temporal cortex', 'cingulate cortex'))
#jyobj@meta.data$DV <- factor(grepl('v', jyobj$area) | grepl('164_MS_TC', jyobj$area), labels = c('Dorsal stream', 'Ventral stream'))
jyobj$DV <- factor(grepl('v', jyobj$area) | grepl('164_MS_TC', jyobj$area), labels = c('Dorsal stream', 'Ventral stream'))

#post <- grepl('dMS', jyobj$area) | grepl('vMS', jyobj$area)
#post <- Idents(jyobj) == 'Ganglionic Eminences 3???'
post <- df$IMAGE.NAME == 'TC_1'

subset <- jyobj[,ix_408_CC]
#print(unique(jyobj$image_name[!(jyobj$image_name %in% subset$image_name)]))

#sum(subset$DV == 'Dorsal migratory stream')

#DimPlot(subset, reduction = "umap", feature) + NoAxes() + NoLegend()
subset$x = df_408_CC$x
subset$y = df_408_CC$y
subset$d = sqrt(subset$x ** 2 + subset$y ** 2)
FeaturePlot(subset, features = c('x', 'y', 'd'))
```
```{r}
post <- jyobj$seurat_clusters == 1 | jyobj$seurat_clusters == 5 | jyobj$seurat_clusters == 8

subset <- jyobj[,post]

sum(subset$DV == 'Dorsal migratory stream')

#DimPlot(subset, reduction = "umap")
FeaturePlot(subset, features = c('NKX2.1',  'LHX6', 'MAF1'), coord.fixed = TRUE)
```
```{r}
### define groups
#FeaturePlot(subset, features = c('SP8', 'COUPTF2'), split.by = 'DV')

#VlnPlot(subset, features = c('NKX2.1', 'PROX1', 'LHX6'), split.by = 'MS')
```

## Compute scores for groups of genes

```{r}
jyobj.markers <- FindAllMarkers(jyobj, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
jyobj.markers %>%
   group_by(cluster) %>%
   slice_max(n = 32, order_by = avg_log2FC)
```

## Look at co-expression


```{r}
# pairs <- data.frame(rbind(c("EGFR", "COUPTF2"),
#                c("PROX1", "SCGN"),
#                c("SP8", "COUPTF2"),
#                c("DCX", "GAD1"),
#                c("TBR1", "SATB2"),
#                c("TBR1", "DCX"),
#                c("RELN", "VLDLR"),
#                c("SCGN", "VLDLR"),
#                c("VLDLR", "COUPTF2"),
#                c("VLDLR", "DCX"),
#                c("TBR1", "GAD1")))
# 
# plots = list()
# save = FALSE
# 
# for (i in 1:3){
#   plotobj <- FeaturePlot(jyobj, features = as.character(pairs[i, ]), blend = TRUE)
#   idx <- i*4-3
#   plots[[idx]] <- plotobj[[1]]
#   plots[[idx+1]] <- plotobj[[2]]
#   plots[[idx+2]] <- plotobj[[3]]
#   plots[[idx+3]] <- plotobj[[4]]
# }
# 
# #gridExtra::grid.arrange(grobs = plots, ncol = 4, nrow = 8, lengths=2:6)
# if (save){
#   ml <- marrangeGrob(plots, nrow=2, ncol=2)
#   ggsave("/home/aunoy/raw_histograms.pdf", ml)
# } else{
#   marrangeGrob(plots, nrow=2, ncol=2)
# }
```

#```{r, fig.width=18,fig.height=6}
```{r}
###FeaturePlot(jyobj, features = c("EGFR", "COUPTF2"), blend = TRUE)
```

```{r}
###FeaturePlot(jyobj, features = c("PROX1", "SCGN"), blend = TRUE)
```

```{r}
###FeaturePlot(jyobj, features = c("SP8", "COUPTF2"), blend = TRUE)
```

```{r}
###FeaturePlot(jyobj, features = c("DCX", "GAD1"), blend = TRUE)
```

```{r}
###FeaturePlot(jyobj, features = c("TBR1", "SATB2"), blend = TRUE)
```

```{r}
###FeaturePlot(jyobj, features = c("TBR1", "DCX"), blend = TRUE)
```

```{r}
###FeaturePlot(jyobj, features = c("RELN", "VLDLR"), blend = TRUE)
```

```{r}
###FeaturePlot(jyobj, features = c("SCGN", "VLDLR"), blend = TRUE)
```

```{r}
###FeaturePlot(jyobj, features = c("VLDLR", "COUPTF2"), blend = TRUE)
```

```{r}
###FeaturePlot(jyobj, features = c("VLDLR", "DCX"), blend = TRUE)
```

```{r}
###FeaturePlot(jyobj, features = c("TBR1", "GAD1"), blend = TRUE)
```


```{r}
newdf <- df %>% mutate(cellnum = 1:nrow(df))
cc_408_df = newdf[ix_408_CC, ]
for(image_name in unique(cc_408_df$IMAGE.NAME)) {
  image_df <- cc_408_df %>% filter(IMAGE.NAME == image_name)
  clust_df <- as.data.frame(jyobj$seurat_clusters[image_df$cellnum])
  clust_df <- clust_df %>% rownames_to_column('arb')
  clust_df$roinum <- 1:nrow(clust_df)
  colnames(clust_df) <- c('cellnum', 'cluster', 'roinum')
  output_path <- '/home/aunoy/st/arc_profiling/st_analysis/results/tables/20220627_1'
  write.csv(clust_df, file.path(output_path, paste0(image_name, '.csv')))
}


```

