---
title: "st_physical"
output: html_notebook
---

Written by Aunoy Poddar
July 9th, 2022

# Process the puncta quantified raw data
```{r eval=FALSE}
current_file <- rstudioapi::getActiveDocumentContext()$path
output_file <- stringr::str_replace(current_file, '.Rmd', '.R')
knitr::purl(current_file, output = output_file)
file.edit(output_file)
```

## Import packages and functions
```{r}
library(Seurat)
library(tictoc)
library(ggplot2)
library(patchwork)
library(pheatmap)
library(RColorBrewer)
library(tidyverse)
library(gridExtra)
library(png)
library(cowplot)
library(magick)

```

## Load the data
```{r}
data_dir = '/home/aunoy/st/arc_profiling/st_analysis/hand_annotated_data/rethresholded'
meta_dir = '/home/aunoy/st/arc_profiling/st_analysis/hand_annotated_data/overlay'
output_dir_plot = '/home/aunoy/st/arc_profiling/st_analysis/results/plots'
output_dir_tbls = '/home/aunoy/st/arc_profiling/st_analysis/results/tables'
```

### Merge both datasets and generate a metadata column that corresponds
### to the cell #
```{r}
df_408 = data.frame()
for (file_name in list.files(data_dir)){
  print(file_name)
  if(grepl('164', file_name)){
    next
  }
  #if(grepl('408_TC', file_name) | grepl('408_vMS', file_name)){
  #  next
  #}
  df_to_append <- read.table(file.path(data_dir, file_name), sep = ',', header = TRUE)
  while(length(ind <- which(df_to_append$Image.Name == "")) > 0){
    df_to_append$Image.Name[ind] <- df_to_append$Image.Name[ind -1]
  }
  
  colnames(df_to_append) <- toupper(colnames(df_to_append))
  df_to_append <- df_to_append %>%
    mutate(area = strsplit(file_name, '.csv')[[1]])
  
  ## Add relative_XY_position
  
  if(!is_empty(df_408)){
    df_to_append <- df_to_append %>%
          dplyr::select(colnames(df_408))
  }
  df_408 <- rbind(df_408, df_to_append)
}
```
```{r}
df_408$IMAGE.NAME = unlist(lapply(df_408$IMAGE.NAME, gsub, pattern='_Cluster', replacement=''))
df_408$IMAGE.NAME = unlist(lapply(df_408$IMAGE.NAME, gsub, pattern='[*]', replacement=''))
df_408$IMAGE.NAME = unlist(lapply(df_408$IMAGE.NAME, gsub, pattern='X', replacement=''))
df_408$IMAGE.NAME = unlist(lapply(df_408$IMAGE.NAME, gsub, pattern='L2_', replacement='L2-'))
df_408$IMAGE.NAME = unlist(lapply(df_408$IMAGE.NAME, gsub, pattern='-L2', replacement='_L2'))
df_408$IMAGE.NAME = unlist(lapply(df_408$IMAGE.NAME, gsub, pattern='Tc_12', replacement='TC_12'))
## Missing
df_408 = df_408[df_408$IMAGE.NAME != 'Layer1', ]
df_408 = df_408[df_408$IMAGE.NAME != 'TC_1', ]
df_408 = df_408[df_408$IMAGE.NAME != 'TC_18', ]
df_408 = df_408[df_408$IMAGE.NAME != 'TC_19', ]
#df_408$IMAGE.NAME = toupper(df_408$IMAGE.NAME)
unique(df_408$IMAGE.NAME)
```
## Now we know that everything is equal to one another, we should load the variable

```{r}
image_names = unique(df_408$IMAGE.NAME)
# Preset these variables to negative values so I can easily check if they were updated later
df_408$X = -1
df_408$Y = -1
# set some normalization variables
## This is the size of the image when the pixel values are taken from top left down
IMAGE_SIZE = 1024
## This is the size of an image in the global coordinate space
IMAGE_LEN = 20

# Load the dataframe with global and relative coordinates
img_cords = read.table(file.path(meta_dir, '408_pixel_coordinates.csv'), sep = ',', header = TRUE)

images = list.files(meta_dir)
for(image_name in image_names){
      if(grepl('164', image_name)){
      next
    }
    split_names = strsplit(image_name, '_')
    cortex = toupper(split_names[[1]][1])
    number = split_names[[1]][2]
    number_csv = paste0('_', number, '.csv')
    filename = images[grepl(cortex, images) & grepl(number_csv, images) & grepl('408', images)]
    coordinates = read.table(file.path(meta_dir, filename), sep = ',', header = TRUE)
    ## checked already that lists are equal, missing 1, 18, 19 for now, layer 1 and others
    if(cortex == 'CC'){ 
      #print(paste('cc', filename, image_name))
      x_adj = 0
      y_adj = 0
    } else if(as.numeric(number) <= 10){
      #print(paste('tc<11', filename, image_name))
      x_adj = 180#img_cords[img_cords$Name == 'G_TC_1', 'x']
      y_adj = 210 #img_cords[img_cords$Name == 'G_TC_1', 'y']
    }else{
      #print(paste('tc>=11', filename, image_name))
      x_adj = 380#img_cords[img_cords$Name == 'G_TC_11', 'x']
      y_adj = 410 #img_cords[img_cords$Name == 'G_TC_11', 'y']
    }
    
    ## so this is a little tricky, so need to get it right
    ## Remember, it is the top right that the coordinate is coming from, but
    ## the bottom right is the new coordinate space.
    ## so first when we get the original coordinate space, to set to relative
    ## of bottom would be the same X, but 1024 - Y
    
    ## push out the coordinates for better visualization
    x_repelled <- (512 - coordinates$X_Coordinate_In_pixels)
    
    
    df_408[df_408$IMAGE.NAME == image_name, 'X'] = (x_repelled / 
                                                      IMAGE_SIZE * IMAGE_LEN) + 
                                                    img_cords[img_cords$Name == image_name, 'x'] + x_adj
    df_408[df_408$IMAGE.NAME == image_name, 'Y'] = ((1024-coordinates$Y_Coordinate_In_pixels) / 
                                                      IMAGE_SIZE * IMAGE_LEN) + 
                                                    img_cords[img_cords$Name == image_name, 'y'] + y_adj    
}
```

## We have the coordinates for 408_TC and others
```{r}
jy_408 = df_408 %>%
  dplyr::select(-c(area, IMAGE.NAME, X, Y)) %>%
  t() %>%
  CreateSeuratObject()
```

## just set everything from below 1 in ratio to zero
```{r}
jy_408 <- NormalizeData(jy_408, scale.factor = 1e5) ###
normed = GetAssayData(jy_408, slot = 'data')
normed[normed < 3] = 0
jy_408 <- SetAssayData(jy_408, slot = 'data', normed)
```

```{r}
xycords = df_408 %>% select(c('X', 'Y')) %>% as.matrix()
colnames(xycords) <- c('pixel_1', 'pixel_2')

jy_408[["XY"]] <- CreateDimReducObject(embeddings = xycords, key = "pixel_", assay = DefaultAssay(jy_408))
```

```{r}
jy_408$gad1_true = normed['GAD1',] != 0 & normed['SATB2',] == 0
```

```{r}
nkx21 <- normed['NKX2.1',] != 0 & normed['LHX6',] == 0 & jy_408$gad1_true 
lhx6 <- normed['NKX2.1',] == 0 & normed['LHX6',] != 0 & jy_408$gad1_true 
mge_both <- normed['NKX2.1',] != 0 & normed['LHX6',] != 0 & jy_408$gad1_true 
mge_neither <- normed['NKX2.1',] == 0 & normed['LHX6',] == 0 & jy_408$gad1_true 
non_interneuron <- !jy_408$gad1_true 

jy_408$mge_lineage = 'error'
jy_408$mge_lineage[nkx21] = 'NKX2.1'
jy_408$mge_lineage[lhx6] = 'LHX6'
jy_408$mge_lineage[mge_both] = 'NKX2.1 & LHX6'
jy_408$mge_lineage[mge_neither] = 'Non-MGE'
jy_408$mge_lineage[non_interneuron] = 'Non-IN'
```


```{r}
DimPlot(jy_408, #cells = grepl('CC', df_408$area), 
        cols = c('grey', 'purple'), reduction = "XY", pt.size = 0.2, group.by = 'gad1_true', order = which(jy_408$gad1_true))
```
```{r}
DimPlot(jy_408, #cells = grepl('CC', df_408$area), 
        #cols = c('grey', 'purple', 'blue', 'red', 'hotpink1'), 
        reduction = "XY", pt.size = 0.1, split.by = 'mge_lineage', 
        cells.highlight = list(nkx2.1 = which(nkx21), lhx6 = which(lhx6), both = which(mge_both)),
        cols.highlight = c('orange1','hotpink1', 'black'), 
        order = which(jy_408$gad1_true)) + scale_y_reverse() + scale_x_reverse() + NoAxes()
```


```{r}
sp8 <- normed['SP8',] != 0 & normed['COUPTF2',] == 0 & jy_408$gad1_true 
couptf2 <- normed['SP8',] == 0 & normed['COUPTF2',] != 0 & jy_408$gad1_true 
cge_lge <- normed['SP8',] != 0 & normed['COUPTF2',] != 0 & jy_408$gad1_true 
neither_cge_lge <- normed['SP8',] == 0 & normed['COUPTF2',] == 0 & jy_408$gad1_true 
non_interneuron <- !jy_408$gad1_true 

jy_408$cge_lineage = 'error'
jy_408$cge_lineage[sp8] = 'SP8'
jy_408$cge_lineage[couptf2] = 'COUPTF2'
jy_408$cge_lineage[cge_lge] = 'SP8 & COUPTF2'
jy_408$cge_lineage[neither_cge_lge] = 'Non-CGE/LGE'
jy_408$cge_lineage[non_interneuron] = 'Non-IN'
```

```{r}
DimPlot(jy_408, #cells = grepl('CC', df_408$area), 
        #cols = c('grey', 'purple', 'blue', 'red', 'hotpink1'), 
        reduction = "XY", pt.size = 1, split.by = 'cge_lineage', 
        cells.highlight = list(sp8 = which(sp8), couptf2 = which(couptf2), both = which(cge_lge)),
        cols.highlight = c('red','blue', 'purple'), 
        order = which(jy_408$gad1_true)) + scale_y_reverse() + scale_x_reverse() + NoAxes()
```

```{r}
jy_408 <- FindVariableFeatures(jy_408, selection.method = "vst")
all.genes <- rownames(jy_408)
jy_408 <- ScaleData(jy_408, features = all.genes)
jy_408 <- RunPCA(jy_408, approx = FALSE)
jy_408 <- FindNeighbors(jy_408, dims = 1:30)
jy_408 <- FindClusters(jy_408, resolution = 0.8)
jy_408 <- RunUMAP(jy_408, dims = 1:30)

DimPlot(jy_408, cols = c('greenyellow', 'lightgoldenrodyellow', 'orange1', 'aquamarine4', 'tomato', 'dodgerblue3', 'violetred3'), reduction = "umap", group.by = 'seurat_clusters') + NoAxes()
```


```{r}
DimPlot(jy_408, #cells = grepl('CC', df_408$area), 
        #cols = c('greenyellow', 'lightgoldenrodyellow', 'orange1', 'aquamarine4', 'tomato', 'dodgerblue3', 'violetred3'), 
        cols = c('greenyellow', 'lightgoldenrodyellow', 'aquamarine4', 'orange1', 'dodgerblue3', 'tomato', 'violetred3'), 
        reduction = "XY", order = c(6, 4, 3, 2, 0, 1, 5), pt.size = 1) + scale_y_reverse() + scale_x_reverse() #group.by = 'mge_lineage', 
        #cells.highlight = list(sp8 = which(sp8), couptf2 = which(couptf2), both = which(cge_lge)),
        #cols.highlight = c('red','blue', 'purple'), 
        #order = which(jy_408$gad1_true)) + scale_y_reverse() + scale_x_reverse()
```

```{r}
cluster_by_loc = as.data.frame(as.matrix(cbind(rownames(df_408), jy_408$seurat_clusters, df_408$X, df_408$Y)))
colnames(cluster_by_loc) = c('cellnum', 'cluster', 'X', 'Y')
```

```{r}
cluster_by_loc %>%
  #filter(cluster == 3) %>%
  ggplot(aes(x = X, color = cluster)) + geom_histogram(position = 'identity', bins = 50, binwidth = 1000, stat = 'count')
```
```{r}
DimPlot(jy_408, #cells = grepl('CC', df_408$area), 
        #cols = c('grey', 'purple', 'blue', 'red', 'hotpink1'), 
        reduction = "XY", pt.size = 1, #group.by = 'mge_lineage', 
        cells.highlight = list(cluster0 = which(jy_408$seurat_clusters == 0))) + scale_y_reverse() + scale_x_reverse()#,
        #cols.highlight = c('red','blue', 'purple'), 
        #order = which(jy_408$gad1_true)) + scale_y_reverse() + scale_x_reverse()
```

```{r}
DimPlot(jy_408, #cells = grepl('CC', df_408$area), 
        #cols = c('grey', 'purple', 'blue', 'red', 'hotpink1'), 
        reduction = "XY", pt.size = 1, #group.by = 'mge_lineage', 
        cells.highlight = list(cluster1 = which(jy_408$seurat_clusters == 1))) + scale_y_reverse() + scale_x_reverse()#,
```

```{r}
DimPlot(jy_408, #cells = grepl('CC', df_408$area), 
        #cols = c('grey', 'purple', 'blue', 'red', 'hotpink1'), 
        reduction = "XY", pt.size = 1, #group.by = 'mge_lineage', 
        cells.highlight = list(cluster2 = which(jy_408$seurat_clusters == 2))) + scale_y_reverse() + scale_x_reverse()#,
```

```{r}
DimPlot(jy_408, #cells = grepl('CC', df_408$area), 
        #cols = c('grey', 'purple', 'blue', 'red', 'hotpink1'), 
        reduction = "XY", pt.size = 1, #group.by = 'mge_lineage', 
        cells.highlight = list(cluster3 = which(jy_408$seurat_clusters == 3))) + scale_y_reverse() + scale_x_reverse()#,
```

```{r}
DimPlot(jy_408, #cells = grepl('CC', df_408$area), 
        #cols = c('grey', 'purple', 'blue', 'red', 'hotpink1'), 
        reduction = "XY", pt.size = 1, #group.by = 'mge_lineage', 
        cells.highlight = list(cluster4 = which(jy_408$seurat_clusters == 4))) + scale_y_reverse() + scale_x_reverse()#,
```

```{r}
DimPlot(jy_408, #cells = grepl('CC', df_408$area), 
        #cols = c('grey', 'purple', 'blue', 'red', 'hotpink1'), 
        reduction = "XY", pt.size = 1, #group.by = 'mge_lineage', 
        cells.highlight = list(cluster5 = which(jy_408$seurat_clusters == 5))) + scale_y_reverse() + scale_x_reverse()#,
```

```{r}
DimPlot(jy_408, #cells = grepl('CC', df_408$area), 
        #cols = c('grey', 'purple', 'blue', 'red', 'hotpink1'), 
        reduction = "XY", pt.size = 1, #group.by = 'mge_lineage', 
        cells.highlight = list(cluster6 = which(jy_408$seurat_clusters == 6))) + scale_y_reverse() + scale_x_reverse()#,
```

```{r}
bruh <- FeaturePlot(jy_408, features = c('NKX2.1', 'LHX6'),
        reduction = "XY", pt.size = 1, order = TRUE, split.by = 'area', by.col = TRUE) #+ scale_y_reverse() + scale_x_reverse() + NoAxes() + NoLegend()
```
```{r}
DimPlot(jy_408, #cells = grepl('CC', df_408$area), 
        cols = c('greenyellow', 'lightgoldenrodyellow', 'orange1', 'aquamarine4', 'tomato', 'dodgerblue3', 'violetred3'),
        reduction = "XY", pt.size = 1, split.by = 'seurat_clusters') + scale_y_reverse() + scale_x_reverse() + NoAxes() + NoLegend()
```
```{r}
jy_408.markers <- FindAllMarkers(jy_408, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
jy_408.markers %>%
   group_by(cluster) %>%
   slice_max(n = 32, order_by = avg_log2FC)
```
## SATB2 neurons removed

```{r}
jy_408_IN <- jy_408[, jy_408$gad1_true]
jy_408_IN <- FindVariableFeatures(jy_408_IN, selection.method = "vst")
all.genes <- rownames(jy_408_IN)
jy_408_IN <- ScaleData(jy_408_IN, features = all.genes)
jy_408_IN <- RunPCA(jy_408_IN, approx = FALSE)
jy_408_IN <- FindNeighbors(jy_408_IN, dims = 1:30)
jy_408_IN <- FindClusters(jy_408_IN, resolution = 0.8)
jy_408_IN <- RunUMAP(jy_408_IN, dims = 1:30)

DimPlot(jy_408_IN, reduction = "umap", group.by = 'seurat_clusters')
```
```{r}
jy_408_IN[["XY"]] <- CreateDimReducObject(embeddings = xycords[jy_408$gad1_true, ], key = "pixel_", assay = DefaultAssay(jy_408_IN))
```

```{r}
DimPlot(jy_408_IN, #cells = grepl('CC', df_408$area), 
        #cols = c('grey', 'purple', 'blue', 'red', 'hotpink1'), 
        reduction = "XY", pt.size = 1) + scale_y_reverse() + scale_x_reverse() 
```
```{r}
jy_408_IN.markers <- FindAllMarkers(jy_408_IN, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
jy_408_IN.markers %>%
   group_by(cluster) %>%
   slice_max(n = 32, order_by = avg_log2FC)
```
## No SATB2 neurons removed

```{r}
jy_408_IN <- jy_408[, jy_408$gad1_true]
jy_408_IN <- FindVariableFeatures(jy_408_IN, selection.method = "vst")
all.genes <- rownames(jy_408_IN)
jy_408_IN <- ScaleData(jy_408_IN, features = all.genes)
jy_408_IN <- RunPCA(jy_408_IN, approx = FALSE)
jy_408_IN <- FindNeighbors(jy_408_IN, dims = 1:30)
jy_408_IN <- FindClusters(jy_408_IN, resolution = 0.8)
jy_408_IN <- RunUMAP(jy_408_IN, dims = 1:30)

DimPlot(jy_408_IN, reduction = "umap", group.by = 'seurat_clusters')
```
```{r}
jy_408_IN[["XY"]] <- CreateDimReducObject(embeddings = xycords[jy_408$gad1_true, ], key = "pixel_", assay = DefaultAssay(jy_408_IN))
```

```{r}
DimPlot(jy_408_IN, #cells = grepl('CC', df_408$area), 
        #cols = c('grey', 'purple', 'blue', 'red', 'hotpink1'), 
        reduction = "XY", pt.size = 1) + scale_y_reverse() + scale_x_reverse() 
```



```{r}
jy_408_IN.markers <- FindAllMarkers(jy_408_IN, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
jy_408_IN.markers %>%
   group_by(cluster) %>%
   slice_max(n = 32, order_by = avg_log2FC)
```

## Adjust to get the right overlay

```{r}
image_names = unique(df_408$IMAGE.NAME)
# Preset these variables to negative values so I can easily check if they were updated later
df_408$X = -1
df_408$Y = -1
# set some normalization variables
## This is the size of the image when the pixel values are taken from top left down
IMAGE_SIZE = 1024
## This is the size of an image in the global coordinate space
IMAGE_LEN = 20

# Load the dataframe with global and relative coordinates
img_cords = read.table(file.path(meta_dir, '408_pixel_coordinates.csv'), sep = ',', header = TRUE)

images = list.files(meta_dir)
for(image_name in image_names){
    if(grepl('164', image_name)){
      next
    }
    split_names = strsplit(image_name, '_')
    cortex = toupper(split_names[[1]][1])
    number = split_names[[1]][2]
    number_csv = paste0('_', number, '.csv')
    filename = images[grepl(cortex, images) & grepl(number_csv, images)]
    coordinates = read.table(file.path(meta_dir, filename), sep = ',', header = TRUE)
    ## checked already that lists are equal, missing 1, 18, 19 for now, layer 1 and others
    if(cortex == 'CC'){ 
      #print(paste('cc', filename, image_name))
      x_adj = 20
      y_adj = 188
    } else if(as.numeric(number) <= 10){
      #print(paste('tc<11', filename, image_name))
      x_adj = 410#img_cords[img_cords$Name == 'G_TC_1', 'x']
      y_adj = 470 #img_cords[img_cords$Name == 'G_TC_1', 'y']
    }else{
      #print(paste('tc>=11', filename, image_name))
      x_adj = 590#img_cords[img_cords$Name == 'G_TC_11', 'x']
      y_adj = 790 #img_cords[img_cords$Name == 'G_TC_11', 'y']
    }
    
    ## so this is a little tricky, so need to get it right
    ## Remember, it is the top right that the coordinate is coming from, but
    ## the bottom right is the new coordinate space.
    ## so first when we get the original coordinate space, to set to relative
    ## of bottom would be the same X, but 1024 - Y
    
    ## push out the coordinates for better visualization
    #x_repelled <- (512 - coordinates$X_Coordinate_In_pixels)
    
    
    df_408[df_408$IMAGE.NAME == image_name, 'X'] = (coordinates$X_Coordinate_In_pixels / 
                                                      IMAGE_SIZE * IMAGE_LEN) + 
                                                    img_cords[img_cords$Name == image_name, 'x']/1.5 + x_adj
    df_408[df_408$IMAGE.NAME == image_name, 'Y'] = ((1024-coordinates$Y_Coordinate_In_pixels) / 
                                                      IMAGE_SIZE * IMAGE_LEN) + 
                                                    img_cords[img_cords$Name == image_name, 'y'] + y_adj    
}

xycords = df_408 %>% select(c('X', 'Y')) %>% as.matrix()
colnames(xycords) <- c('pixel_1', 'pixel_2')

jy_408[["XY"]] <- CreateDimReducObject(embeddings = xycords, key = "pixel_", assay = DefaultAssay(jy_408))
```


```{r}
#https://stackoverflow.com/questions/9917049/inserting-an-image-to-ggplot2

theme_set(theme_cowplot())

bad_colors <- DimPlot(jy_408, cols = c('greenyellow', 'lightgoldenrodyellow', 'aquamarine4', 'orange1', 'dodgerblue3', 'tomato', 'violetred3'),  reduction = "XY", pt.size = 0.01, order = c(6, 4, 3, 2, 0, 1, 5)) + scale_y_reverse() + scale_x_reverse() + xlim(852, 0) + ylim(1242, 0) + NoLegend() + coord_fixed() + NoAxes()

#xorig = -852
#yorig = -1242

ggdraw() +
  draw_image('~/st/arc_profiling/st_analysis/hand_annotated_data/images/408_slice_noboxes_nocolor.png',
             x = 0, y = 0) +
  draw_plot(bad_colors)
```
```{r}
DimPlot(jy_408, reduction = "XY", pt.size = 0.1)+ scale_y_reverse() + scale_x_reverse()   + xlim(852, 0) + ylim(1242, 0) # + NoLegend() + NoAxes()
```
```{r}
jy_408_sp <- df_408 %>%
  dplyr::select(-c(area, IMAGE.NAME)) %>%
  t() %>%
  CreateSeuratObject()
jy_408_sp <- FindVariableFeatures(jy_408_sp, selection.method = "vst")
all.genes <- rownames(jy_408)
jy_408_sp <- ScaleData(jy_408_sp, features = all.genes)
jy_408_sp <- RunPCA(jy_408_sp, approx = FALSE)
jy_408_sp <- FindNeighbors(jy_408_sp, dims = 1:30)
jy_408_sp <- FindClusters(jy_408_sp, resolution = 0.8)
jy_408_sp <- RunUMAP(jy_408_sp, dims = 1:30)

DimPlot(jy_408_sp, reduction = "umap", group.by = 'seurat_clusters')
```
```{r}
jy_408_sp[["XY"]] <- CreateDimReducObject(embeddings = xycords, key = "pixel_", assay = DefaultAssay(jy_408_sp))
```

```{r}
DimPlot(jy_408_sp, reduction = "XY", split.by = 'seurat_clusters')
```


```{r}
FeaturePlot(jy_408_sp, c('X', 'Y'))
```

```{r}
reln <- normed['VLDLR',] != 0 & normed['LRP8',] == 0 & jy_408$gad1_true 
lrp8 <- normed['VLDLR',] == 0 & normed['LRP8',] != 0 & jy_408$gad1_true 
relnboth <- normed['VLDLR',] != 0 & normed['LRP8',] != 0 & jy_408$gad1_true 
relnneither <- normed['VLDLR',] == 0 & normed['LRP8',] == 0 & jy_408$gad1_true 
non_interneuron <- !jy_408$gad1_true 

jy_408$reln_signaling = 'error'
jy_408$reln_signaling[reln] = 'VLDLR'
jy_408$reln_signaling[lrp8] = 'LRP8'
jy_408$reln_signaling[relnboth] = 'VLDLR & LRP8'
jy_408$reln_signaling[relnneither] = 'Neither'
jy_408$reln_signaling[non_interneuron] = 'Non-IN'
```


```{r}
## just define sets of cells that I want to plot
cingulate_MS = grepl('CC', df_408$IMAGE.NAME) 
dorsal_TC_MS = df_408$IMAGE.NAME %in% outer('TC_', 2:10, FUN=paste0)
ventral_TC_MS = !cingulate_MS & !dorsal_TC_MS
```

```{r}
FeaturePlot(jy_408, cells = which(ventral_TC_MS), reduction = "XY", features = 'TBR1') + scale_y_reverse() + scale_x_reverse() 
```
```{r}
FeaturePlot(jy_408, cells = which(ventral_TC_MS), reduction = "XY", features = 'LRP8') + scale_y_reverse() + scale_x_reverse() 
```


```{r}
FeaturePlot(jy_408, cells = which(dorsal_TC_MS), reduction = "XY", features = c('CXCR4', 'CALB2'), order = TRUE) + scale_y_reverse() + scale_x_reverse() 
```
```{r}
FeaturePlot(jy_408, cells = which(ventral_TC_MS), reduction = "XY", features = c('CXCR4', 'CALB2'), order = TRUE) + scale_y_reverse() + scale_x_reverse() 
```
```{r}
FeaturePlot(jy_408, cells = which(cingulate_MS), reduction = "XY", features = c('NKX2.1'), order = TRUE) + scale_y_reverse() + scale_x_reverse() 
```


```{r}
FeaturePlot(jy_408, cells = which(ventral_TC_MS), reduction = "XY", features = c('CXCR4', 'CALB2'), order = TRUE) +
  stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE) +
  scale_fill_distiller(palette=4, direction=-1) 
```

```{r}
normed_data = t(as.matrix(GetAssayData(jy_408, slot = 'data'))) 
norm_bools = normed_data > 0

density_df = as.data.frame(cbind(xycords, norm_bools, jy_408$seurat_clusters))
colnames(density_df) = c('X', 'Y', colnames(norm_bools), 'cluster')
density_df$fov = 'error'
density_df$fov[dorsal_TC_MS] = 'dMS_TC'
density_df$fov[ventral_TC_MS] = 'vMS_TC'
density_df$fov[cingulate_MS] = 'MS_CC'
```

```{r}
density_df %>%
  ggplot(aes(x = X, y = Y))  +
  geom_bin2d(bins = 20) +
  scale_fill_continuous(type = "viridis") +
  theme_bw()

```


```{r}
DimPlot(jy_408, #cells = grepl('CC', df_408$area), 
        #cols = c('grey', 'purple', 'blue', 'red', 'hotpink1'), 
        reduction = "XY", pt.size = 0.1, split.by = 'reln_signaling', 
        cells.highlight = list(vldlr = which(reln), lrp8 = which(lrp8), both = which(relnboth)),
        cols.highlight = c('orange1','hotpink1', 'black'), 
        order = which(jy_408$gad1_true)) + scale_y_reverse() + scale_x_reverse()
```


## LEts do the functional graphs
```{r}
goi_primary = c('VIP', 'SST', 'CXCR4')
goi = c('VIP', 'SST', 'CXCR4', 'CXCR7', 'CXCL14', 'CXCL12', 'LRP8', 'VLDLR', 'RELN')
goi = c('DCDC2', 'KIA0319')
```

## Let's compare SP8 vs COUPTF2 average expression of these markers
```{r}
fxn_genes  = as.data.frame(normed_data[, goi])
fxn_genes$cge = jy_408$cge_lineage
fxn_genes$fov = density_df$fov

fxn_genes %>%
  filter(fov == 'dMS_TC') %>%
  pivot_longer(!c(cge, fov), names_to = "gene", values_to = "expr") %>%
  ggplot(aes(x = gene, y = expr, fill = cge)) + geom_boxplot()# geom_bar(position="dodge", stat="identity")
```

```{r}
fxn_genes %>%
  filter(fov == 'vMS_TC') %>%
  pivot_longer(!c(cge, fov), names_to = "gene", values_to = "expr") %>%
  ggplot(aes(x = gene, y = expr, fill = cge)) + geom_boxplot()# geom_bar(position="dodge", stat="identity")
```

```{r}
cfov = 'MS_CC'
fxn_genes %>%
  filter(fov == cfov) %>%
  pivot_longer(!c(cge, fov), names_to = "gene", values_to = "expr") %>%
  ggplot(aes(x = gene, y = expr, fill = cge)) + geom_bar(position="dodge", stat="identity") +
  scale_fill_manual(values=c("green","gray","gray","blue", "red")) + ggtitle(cfov)
```
```{r}
cfov = 'vMS_TC'
fxn_genes %>%
  filter(fov == cfov) %>%
  pivot_longer(!c(cge, fov), names_to = "gene", values_to = "expr") %>%
  ggplot(aes(x = gene, y = expr, fill = cge)) + geom_bar(position="dodge", stat="identity") +
  scale_fill_manual(values=c("green","gray","gray","blue", "red")) + ggtitle(cfov)
```

```{r}
cfov = 'dMS_TC'
fxn_genes %>%
  filter(fov == cfov) %>%
  pivot_longer(!c(cge, fov), names_to = "gene", values_to = "expr") %>%
  ggplot(aes(x = gene, y = expr, fill = cge)) + geom_bar(position="dodge", stat="identity") +
  scale_fill_manual(values=c("green","gray","gray","blue", "red")) + ggtitle(cfov)
```
```{r}
fxn_genes  = as.data.frame(norm_bools[, goi])
fxn_genes$cge = jy_408$cge_lineage
fxn_genes$fov = density_df$fov

fxn_genes %>%
  filter(fov == 'dMS_TC') %>%
  pivot_longer(!c(cge, fov), names_to = "gene", values_to = "expr") %>%
  ggplot(aes(x = gene, y = as.numeric(expr), fill = cge)) + geom_bar(position="dodge", stat="summary", fun = "mean") +
  xlab("pct") + ggtitle('dMS_TC')
```

```{r}
fxn_genes  = as.data.frame(norm_bools[, goi])
fxn_genes$cge = jy_408$cge_lineage
fxn_genes$fov = density_df$fov

cfov = 'vMS_TC'

fxn_genes %>%
  filter(fov == cfov) %>%
  select(-fov) %>%
  pivot_longer(!mge, names_to = "gene", values_to = "expr") %>%
  data_summary(varname="expr", groupnames=c("gene", "mge")) %>%
  ggplot(aes(x=gene, y=expr, fill=mge)) + geom_bar(stat="identity", color="black", position=position_dodge())  + geom_errorbar(aes(ymin=expr-sem, ymax=expr+sem), width=.2, position=position_dodge(.9)) +
  ylab("pct") + ggtitle(cfov) + scale_fill_manual(values=c("cadetblue1","brown2","darkslateblue","grey", "khaki1")) +
  theme_classic()

#c("cadetblue1","brown2","darkslateblue","grey", "khaki1") for mge
```

```{r}
#http://www.sthda.com/english/wiki/ggplot2-error-bars-quick-start-guide-r-software-and-data-visualization
library(plotrix)
data_summary <- function(data, varname, groupnames){
  require(plyr)
  summary_func <- function(x, col){
    c(mean = mean(x[[col]], na.rm=TRUE),
      sem = std.error(x[[col]], na.rm=TRUE))
  }
  data_sum<-ddply(data, groupnames, .fun=summary_func,
                  varname)
  data_sum <- rename(data_sum, c("mean" = varname))
 return(data_sum)
}
```
```{r}
df2 <- fxn_genes %>%
  select(-fov) %>%
  pivot_longer(!cge, names_to = "gene", values_to = "expr") %>%
  data_summary(varname="expr", 
                    groupnames=c("gene", "cge"))
```

```{r}
 ggplot(df2, aes(x=gene, y=expr, fill=cge)) + 
  geom_bar(stat="identity", color="black", position=position_dodge()) +
  geom_errorbar(aes(ymin=expr-sem, ymax=expr+sem), width=.2,
                 position=position_dodge(.9)) 
```

```{r}
 ggplot(df2, aes(x=gene, y=expr, fill=cge)) + 
  geom_bar(stat="identity", color="black", position=position_dodge()) +
  geom_errorbar(aes(ymin=expr-sem, ymax=expr+sem), width=.2,
                 position=position_dodge(.9)) 
```

```{r}
FeaturePlot(jy_408_IN, reduction = 'XY', features = c('DCDC2', 'KIA0319'), order = TRUE)
```
```{r}
fxn_genes %>%
  select(-c(fov, mge)) %>%
  pivot_longer(!cge, names_to = "gene", values_to = "expr") %>%
  data_summary(varname="expr", groupnames=c("gene", "cge")) %>%
  ggplot(aes(x=gene, y=expr, fill=cge)) + geom_bar(stat="identity", color="black", position=position_dodge())  + geom_errorbar(aes(ymin=expr-sem, ymax=expr+sem), width=.2, position=position_dodge(.9)) +
  ylab("pct") + scale_fill_manual(values=c("darkolivegreen1","orange2","rosybrown4","gray96", "grey")) +
  theme_classic()
```
```{r}
sum(fxn_genes$cge == 'SP8 & COUPTF2')
sum(jy_408$gad1_true)

print(206/388)
```

## Order the images
```{r}
unique(df_408$IMAGE.NAME)
images_ordered = c('TC_20', 'TC_17', 'TC_16', 'TC_15', 'TC_14', 'TC_13', 'TC_12', 'TC_11',
           'TC_10', 'TC_9', 'TC_8', 'TC_7', 'TC_6', 'TC_4', 'TC_4', 'TC_3', 'TC_2',
           'CC_4', 'CC_5', 'CC_6', 'CC_6', 'CC_8', 'CC_9', 'CC_10', 'CC_11', 'CC_12',
           'CC_L2-1', 'CC_L2-2', 'CC_L2-3', 'CC_Cortical1', 'CC_Cortical2')
```

```{r}
x_horz = 1:length(images_ordered) * 25
y_horz = rep(0, length(images_ordered))
horz_embedding = data.frame()
df_408$X_horz = -1
df_408$Y_horz = -1


images = list.files(meta_dir)
for(i in 1:length(images_ordered)){
    image_name = images_ordered[i]
    split_names = strsplit(image_name, '_')
    cortex = toupper(split_names[[1]][1])
    number = split_names[[1]][2]
    number_csv = paste0('_', number, '.csv')
    filename = images[grepl(cortex, images) & grepl(number_csv, images)]
    coordinates = read.table(file.path(meta_dir, filename), sep = ',', header = TRUE)
    ## checked already that lists are equal, missing 1, 18, 19 for now, layer 1 and others
 
    ## so this is a little tricky, so need to get it right
    ## Remember, it is the top right that the coordinate is coming from, but
    ## the bottom right is the new coordinate space.
    ## so first when we get the original coordinate space, to set to relative
    ## of bottom would be the same X, but 1024 - Y
    
    ## push out the coordinates for better visualization
    #x_repelled <- (512 - coordinates$X_Coordinate_In_pixels)
    
    
    df_408[df_408$IMAGE.NAME == image_name, 'X_horz'] = (coordinates$X_Coordinate_In_pixels / 
                                                      IMAGE_SIZE * IMAGE_LEN) + y_horz[i]
    df_408[df_408$IMAGE.NAME == image_name, 'Y_horz'] = ((1024-coordinates$Y_Coordinate_In_pixels) / 
                                                      IMAGE_SIZE * IMAGE_LEN) + x_horz[i]
}
```

```{r}
hcoords = df_408 %>% dplyr::select(c('X_horz', 'Y_horz')) %>% as.matrix()
colnames(hcoords) <- c('pixel_1', 'pixel_2')

jy_408[["H"]] <- CreateDimReducObject(embeddings = hcoords, key = "pixel_", assay = DefaultAssay(jy_408))
```

```{r}
jy_408$satb1_true = !jy_408$gad1_true
DimPlot(jy_408, cols = c('grey', 'purple'), reduction = "H", pt.size = 0.25, group.by = 'gad1_true', order = which(jy_408$gad1_true)) + coord_fixed(ratio = 0.5) + NoAxes() + NoLegend()
```
```{r}
DimPlot(jy_408, reduction = "H", pt.size = 0.25, group.by = 'mge_lineage', order = "NKX2.1 & LHX6", cells.highlight = which(jy_408$mge_lineage == 'NKX2.1 & LHX6'), cols.highlight = 'red') + coord_fixed(ratio = 1) +  NoLegend() + NoAxes()
```

```{r}
theme_Publication <- function(base_size=14, base_family="helvetica") {
      library(grid)
      library(ggthemes)
      (theme_foundation(base_size=base_size, base_family=base_family)
       + theme(plot.title = element_text(face = "bold",
                                         size = rel(1.2), hjust = 0.5),
               text = element_text(),
               panel.background = element_rect(colour = NA),
               plot.background = element_rect(colour = NA),
               panel.border = element_rect(colour = NA),
               axis.title = element_text(face = "bold",size = rel(1)),
               axis.title.y = element_text(angle=90,vjust =2),
               axis.title.x = element_text(vjust = -0.2),
               axis.text = element_text(), 
               axis.line = element_line(colour="black"),
               axis.ticks = element_line(),
               panel.grid.major = element_line(colour="#f0f0f0"),
               panel.grid.minor = element_blank(),
               legend.key = element_rect(colour = NA),
               legend.position = "bottom",
               legend.direction = "horizontal",
               legend.key.size= unit(0.2, "cm"),
               legend.margin = unit(0, "cm"),
               legend.title = element_text(face="italic"),
               plot.margin=unit(c(10,5,5,5),"mm"),
               strip.background=element_rect(colour="#f0f0f0",fill="#f0f0f0"),
               strip.text = element_text(face="bold")
          ))
      
}

scale_fill_Publication <- function(...){
      library(scales)
      discrete_scale("fill","Publication",manual_pal(values = c("#386cb0","#fdb462","#7fc97f","#ef3b2c","#662506","#a6cee3","#fb9a99","#984ea3","#ffff33")), ...)

}

scale_colour_Publication <- function(...){
      library(scales)
      discrete_scale("colour","Publication",manual_pal(values = c("#386cb0","#fdb462","#7fc97f","#ef3b2c","#662506","#a6cee3","#fb9a99","#984ea3","#ffff33")), ...)

}
```


```{r}
FeaturePlot(jy_408, pt.size=0.1, reduction = "H", features = 'LRP8') + coord_fixed(ratio = 0.5) +  theme_Publication() + NoLegend() + NoAxes()
```

