---
title: "st_profiling_clean"
output: html_notebook
---

Written by Aunoy Poddar
May 23rd, 2022

# Process the puncta quantified raw data
```{r eval=FALSE}
current_file <- rstudioapi::getActiveDocumentContext()$path
output_file <- stringr::str_replace(current_file, '.Rmd', '.R')
knitr::purl(current_file, output = output_file)
file.edit(output_file)
```

## Import packages and functions
```{r}
library(Seurat)
library(tictoc)
library(ggplot2)
library(patchwork)
library(pheatmap)
library(RColorBrewer)
library(tidyverse)
library(gridExtra)
```

## Load the data
```{r}
data_dir = '/home/aunoy/st/arc_profiling/st_analysis/hand_annotated_data/rethresholded'
output_dir_plot = '/home/aunoy/st/arc_profiling/st_analysis/results/plots'
output_dir_tbls = '/home/aunoy/st/arc_profiling/st_analysis/results/tables'
```

### Merge both datasets and generate a metadata column that corresponds
### to the cell #
```{r}
df = data.frame()
for (file_name in list.files(data_dir)){
  print(file_name)
  #if(grepl('408_TC', file_name) | grepl('408_vMS', file_name)){
  #  next
  #}
  df_to_append <- read.table(file.path(data_dir, file_name), sep = ',', header = TRUE)
  while(length(ind <- which(df_to_append$Image.Name == "")) > 0){
    df_to_append$Image.Name[ind] <- df_to_append$Image.Name[ind -1]
  }
  #df_to_append <- df_to_append %>%
  #  dplyr::select(-1)
  if(grepl('164', file_name)){
    df_to_append <- df_to_append %>%
      dplyr::select(-X)
  }
  colnames(df_to_append) <- toupper(colnames(df_to_append))
  df_to_append <- df_to_append %>%
    mutate(area = strsplit(file_name, '.csv')[[1]])
  if(!is_empty(df)){
    df_to_append <- df_to_append %>%
          dplyr::select(colnames(df))
  }
  df <- rbind(df, df_to_append)
}
```

```{r}
### right now i want experiment # for the day and overwrite to be false
# 
# ## Write to file
# date <- gsub('-', '', Sys.Date())
# exp_num <- '1'
# folder <- paste0(date, '_', exp_num)
# 
# ## check if folder exists, if not, then proceed
# expltdir <- file.path(output_dir_plot, folder)
# extbldir <- file.path(output_dir_plot, folder)
# 
# 
# if(dir.exists(expltdir) || dir.exists(extbldir)){
#   quit('Folder exists. Set --overwrite to TRUE to replace folder')
# }
# 
# ## Create the directories
# dir.create(expltdir)
# dir.create(extbldir)
```


### Add the cellnames as rownames
```{r}
rownames(df) <- c(outer(c('C'), 1:dim(df)[1], FUN=paste0))
```

## Define the different gene sets based on conversation with JY
```{r}
migra = toupper(c('Dcx', 'Lrp8', 'Reln', 'Dcdc2', 'Ncam1', 'Kia0319', 'Vldlr'))
#CGE = toupper(c('Egfr', 'Vip', 'Prox1'))
#LGE = toupper(c('Tshz1', 'Gsx2', 'Emx1'))
#MGE = toupper(c('Lhx6', 'Maf1', 'Sst'))
CGE = toupper(c('Egfr', 'Prox1'))
LGE = toupper(c('Tshz1', 'Gsx2', 'Emx1'))
MGE = toupper(c('Lhx6', 'Maf1', 'Nkx2.1'))
CGE_LGE = toupper(c('Scgn', 'Couptf2', 'Sp8', 'Calb2', 'Pax6'))
GABA = toupper(c('Dlx2', 'Gad1'))
mature_IN = toupper(c('Gad1', 'Vip', 'Sst'))
progen_IN = toupper(c('Dlx2'))
Excit = toupper(c('Eomes', 'Tbr1', 'Satb2'))
ligand = toupper(c('Reln', 'Cxcl12', 'Cxcl14'))
recept = toupper(c('Lrp8', 'Cxcr7', 'Cxcr4', 'Vldlr'))
```

## Heatmaps

### Rearrange the data to wide for heatmap
```{r}
df_longer <- df %>%
  rownames_to_column('Cell') %>%
  dplyr::select(-c(area, IMAGE.NAME)) %>%
  pivot_longer(!Cell, names_to = 'Gene', values_to = "Puncta2Nuc_IR")

df_wide <- df %>%
  rownames_to_column('Cell')%>%
  dplyr::select(-c(area, IMAGE.NAME)) %>%
  pivot_longer(!Cell, names_to = 'Gene', values_to = "Puncta2Nuc_IR") %>%
  pivot_wider(names_from = Gene, values_from = Puncta2Nuc_IR)
```


## some quick heatmap business

```{r}
### log(x+1) function
log1 <- function(x) {
   return(log(x+1))
}

### Scale and then log+1
log1_and_mult <- function(x) {
   return(log1(x*1e4))
}

### Get the numeric values only
df_num <- df_wide %>%
  column_to_rownames('Cell')

### Normalize to cell total
### Log + Multiply
### Center and scale
scaled_mat <- df_num %>%
  sweep(1, rowSums(df_num), '/') %>%
  log1_and_mult() %>%
  apply(1, scale)



### Apply separate clustering, need to look into why 
hr <- hclust(as.dist(1-cor(t(scaled_mat), method="pearson")), method = "complete")
hc <- hclust(as.dist(1-cor(scaled_mat[,good_cells], method="spearman")), method="complete")

annotation <- data.frame(area = factor(df[good_cells,]$area))
rownames(annotation) <- rownames(df[good_cells, ]) # check out the row names of annotation

rownames(scaled_mat) <- colnames(df_num)
scaled_mat[,good_cells] %>%
  pheatmap(annotation_col = annotation, 
           color = colorRampPalette(rev(brewer.pal(n = 7, name = "RdYlBu")))(100),
  #breaks = seq(from= -5, to = 5, by = 11/100.), 
  cluster_rows = hr, cluster_cols = hc, 
  #cluster_rows = TRUE, cluster_cols = TRUE, 
  #clustering_distance_rows = "correlation", 
  #clustering_distance_cols = "correlation",
  fontsize_row = 8, fontsize_col = 4, show_colnames = FALSE,
           show_rownames = TRUE, cell_width = 6, cellheight = 8)#,
          #filename = file.path(output_dir, 'log.png'))
```
### By area, not dendogram
```{r}
rownames(scaled_mat) <- colnames(df_num)
annotation <- data.frame(clust = Idents(jyobj))
scaled_mat %>%
  pheatmap(annotation_col = annotation, 
           color = colorRampPalette(rev(brewer.pal(n = 7, name = "RdYlBu")))(100),
  #breaks = seq(from= -5, to = 5, by = 11/100.), 
  cluster_rows = hr, cluster_cols = TRUE, 
  #cluster_rows = TRUE, cluster_cols = TRUE, 
  #clustering_distance_rows = "correlation", 
  #clustering_distance_cols = "correlation",
  fontsize_row = 8, fontsize_col = 4, show_colnames = FALSE,
           show_rownames = TRUE, cell_width = 6, cellheight = 8)#,
          # filename = '/home/aunoy/pheatmap_logz_norm.png')
```


```{r}
dist_mat <- as.dist(1-cor(scaled_mat, method="spearman"))
dist_mat %>%
pheatmap(annotation_col = annotation,
         color = colorRampPalette(rev(brewer.pal(n = 7, name = "RdYlBu")))(100),
        cluster_rows = TRUE, cluster_cols = TRUE,
fontsize_row = 8, fontsize_col = 4, show_colnames = FALSE,
         show_rownames = FALSE, cell_width = 0.1, cellheight = 0.3)#,
    #filename = file.path(output_dir, 'spearmann_log.png'))
```


```{r}
df_longer %>%
  filter(Gene == 'Gsx2') %>%
  ggplot(aes(x=Puncta2Nuc_IR)) + 
  geom_histogram(color="black", fill="white")
```
```{r}
plots = list()
save = FALSE
all_genes <- df %>% 
  dplyr::select(-area) %>%
  colnames()

for (i in 1:length(all_genes)){
  plots[[i]] <- df_longer %>%
  filter(Gene == all_genes[i]) %>%
  mutate(log_norm = log1_and_mult(Puncta2Nuc_IR)) %>%
  ggplot(aes(x=log_norm, label = Gene)) + 
  geom_histogram(color="black", fill="white") + 
  labs(title=all_genes[i])+
  theme_classic()
}

#gridExtra::grid.arrange(grobs = plots, ncol = 4, nrow = 8, lengths=2:6)
if (save){
  ml <- marrangeGrob(plots, nrow=2, ncol=2)
  ggsave("/home/aunoy/raw_histograms.pdf", ml)
} else{
  marrangeGrob(plots, nrow=2, ncol=2)
}
```

### process data in Seurat object

```{r}
jyobj <- df[good_cells, ] %>%
  dplyr::select(-c(area, IMAGE.NAME)) %>%
  t() %>%
  CreateSeuratObject()
```


```{r}
jyobj <- NormalizeData(jyobj, scale.factor = 1e5) ###
sum(jyobj@assays$RNA[,] < 1)

```
### plot highly variable genes
```{r}
jyobj <- FindVariableFeatures(jyobj, selection.method = "vst")

# Identify the 10 most highly variable genes
top10 <- head(VariableFeatures(jyobj), 10)

# plot variable features with and without labels
plot1 <- VariableFeaturePlot(jyobj) + theme(axis.title.x = element_text(size = 10), axis.text.x = element_text(size = 6))
plot2 <- LabelPoints(plot = plot1, points = top10, repel = TRUE) + theme(axis.title.x = element_text(size = 10), axis.text.x = element_text(size = 6))
plot1 + plot2 + theme(axis.title.y = element_text(size = 10))
#ggsave(file.path(output_dir, 'vst_plot.png'))
```

```{r}
all.genes <- rownames(jyobj)
jyobj <- ScaleData(jyobj, features = all.genes)
```

```{r}
jyobj <- RunPCA(jyobj, features = VariableFeatures(object = jyobj), approx = FALSE)
print(jyobj[["pca"]], dims = 1:5, nfeatures = 5)
```
```{r}
VizDimLoadings(jyobj, dims = 1:2, reduction = "pca")
```

```{r}
jyobj$area <- df[good_cells,]$area
DimPlot(jyobj, reduction = "pca", group.by = 'area')

```

```{r}
ElbowPlot(jyobj)
```

# PC30,resolution 0.8

```{r}
jyobj <- FindNeighbors(jyobj, dims = 1:30)
jyobj <- FindClusters(jyobj, resolution = 1.4)
```


```{r}
jyobj <- RunUMAP(jyobj, dims = 1:30)

DimPlot(jyobj, reduction = "umap", group.by = 'seurat_clusters')
```

## Compute scores for groups of genes

```{r}
jyobj.markers <- FindAllMarkers(jyobj, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
jyobj.markers %>%
   group_by(cluster) %>%
   slice_max(n = 32, order_by = avg_log2FC)
```
```{r}
VlnPlot(jyobj,c("SATB2","GAD1"))
```

DCX
GAD1
COUPTF2
SP8
TSHZ1
NKX2.1
```{r}
# DCX
# GAD1
```

```{r}
breakpoints = c(0.2, 0.25, 0.45, 0.5, 0.55, 0.6, 0.65,
                0.7, 0.75, 0.8, 0.9, 0.95, 1, 1.05, 1.4, 1.45, 1.6, 1.65, 1.85, 1.9)

plots = list()
jyobj <- FindNeighbors(jyobj, dims = 1:30)
i = 1
for (breakpoint in breakpoints){
  jyobj <- FindClusters(jyobj, resolution = breakpoint)
  jyobj <- RunUMAP(jyobj, dims = 1:30)
  jyobj.markers <- FindAllMarkers(jyobj, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
  labels = jyobj.markers %>%
   group_by(cluster) %>%
   slice_max(n = 1, order_by = avg_log2FC)
  new.cluster.ids <- labels$gene
  names(new.cluster.ids) <- levels(jyobj)
  jyobj <- RenameIdents(jyobj, new.cluster.ids)
  plots[[i]] = DimPlot(jyobj, reduction = "umap", pt.size = 1, label = TRUE) + NoAxes() + NoLegend()
  i = i + 1
}

marrangeGrob(plots, nrow=2, ncol=2)
```


