---
title: "Integration_Analysis"
output: html_notebook
---

## Aunoy Poddar
## Friday December 22, 2023
## This notebook is designed to take cca-integrated data from Shi et al
## and from our human arc data and quantify the extent of co-clustering
## between celltypes in order to identify relationships between early interneuron
## progenitors and migratory inhibitory neuroblasts identified in the arc.
## Next, this data along with lineage inference data generated from CellRank
## is merged into a sankey diagram to visualize the trajectories of cells from
## the GE, to the Arc, and finally to cortical, striatal, and olfactory bulb
## terminal fates. This makes up the bulk of the analysis shown in Fig. 2.

```{r}
library(Seurat)
#library(SeuratData)
library(SeuratWrappers)
#library(SeuratDisk)
#library(SeuratData)
library(tictoc)
library(plyr)
library(dplyr)
library(tidyr)
library(tidyverse)
library(ggplot2)
library(cowplot)
library(pracma)
library(slingshot)
options(Seurat.Object.assay.version = "v5")
options(future.globals.maxSize = 8000 * 1024^2)
library(data.table)
library(paletteer)
library(ggsankey)
source("/wynton/home/paredes/aunoy/src/visualization_helper.R")
```

# CCA Integration with GE prenatal and late prenatal Arc data
```{r}
## Load data
arc_shi <- readRDS("/wynton/group/paredes/Aunoy/integrations_w_IPC/arc_shi.rds")
```


```{r}
## Generate nearest neighbor graph, cca_clusters, and UMAP
arc_shi <- JoinLayers(arc_shi)
arc_shi <- FindNeighbors(arc_shi, reduction = "integrated.cca", dims = 1:30)
arc_shi <- FindClusters(arc_shi, resolution = 1.5, cluster.name = "cca_clusters")
arc_shi <- RunUMAP(arc_shi, reduction = "integrated.cca", dims = 1:30, reduction.name = "umap.cca")
```

```{r}
## Visualize data
DimPlot(
  arc_shi,
  reduction = "umap.cca",
  group.by = c("class"),
  split.by = "dataset",
  label = TRUE,
  combine = FALSE, label.size = 2
)
```

```{r}
## Visualize split by dataset
DimPlot(arc_shi, reduction = "umap.scvi", group.by = "class", split.by = "dataset", label = TRUE) + 
  NoLegend()
```


```{r}
## Assign labels based on clustering
arc_shi$identity = "error"
arc_shi$identity[arc_shi$cca_clusters %in% c("23", "28", "27",
                                             "12", "21", "19",
                                             "15", "29", "25")] = "Progenitor"
arc_shi$identity[arc_shi$cca_clusters %in% c("17", "13", "16")] = "Glia"
arc_shi$identity[arc_shi$cca_clusters %in% c("30")] = "Endothelial"
arc_shi$identity[arc_shi$cca_clusters %in% c("26")] = "OPC"
arc_shi$identity[arc_shi$cca_clusters %in% c("24")] = "Microglia"
arc_shi$identity[arc_shi$cca_clusters %in% c("3")] = "Exc/Thalamic"
arc_shi$identity[arc_shi$cca_clusters %in% c("22", "20", "14", "9", "11", "4")] = "LGE-Derived"
arc_shi$identity[arc_shi$cca_clusters %in% c("5", "7", "8", "2", "18", "6")] = "MGE-Derived"
arc_shi$identity[arc_shi$cca_clusters %in% c("0", "1", "10", "31")] = "CGE-Derived"
## Check that all were assigned.
print(unique(arc_shi$cca_clusters[arc_shi$identity == "error"]))
DimPlot(arc_shi, reduction = "umap.cca", group.by= "identity", label = TRUE)
```


```{r}
## Visualize assignments
DimPlot(arc_shi, reduction = "umap.cca", group.by= "class", label = TRUE, shuffle = TRUE)
```

```{r}
## Pull out arc specific barcodes for the sankey diagram
arc = arc_shi[, arc_shi$dataset == "arc"]
```

## Sankey Diagram
```{r}
## Take the "identity" label taken from the previous cca co_clustering
sankey_df = arc@meta.data[c("identity", "class")]
```

```{r}
## Use the make_long function from gg_sankey to format for plotting
sdf = sankey_df %>%
  #filter(class %in% c("Inh CGE", "Inh LGE", "Inh MGE", "Inh CGE/LGE")) %>%
  #filter(fate != "error") %>%
  make_long(identity, class)
```


```{r}
## Order the nodes

node_order = c(rev(c("Progenitor", "OPC","Microglia",
               "MGE-Derived","CGE-Derived","LGE-Derived","Glia","Endothelial","Exc/Thalamic")), 
               rev(c("Inh MGE", "Inh CGE","Inh CGE/LGE", "Inh LGE")))#, 
              # rev(c("MGE_Str", "MGE_Ctx", "CGE_Ctx", "LGE_OB","LGE_MSN")))

node_order =  c(rev(c("Progenitor", "OPC","Microglia",
               "MGE-Derived","CGE-Derived","LGE-Derived","Glia","Endothelial","Exc/Thalamic")),
               "Ast", "Ast/Rgl", "Cpl", "End", "Epd", "Exc", "Gli IPC", "Inh CGE", 
               "Inh CGE/LGE", "Inh IPC", "Inh LGE", "Inh MGE", "Mcg",  "Oli", "Rbc")

sdf$node = factor(sdf$node, levels = c(node_order))
```

```{r}
## Want to remove connections between nodes that make up less than 5% of the
## origins for a particular arc class. For example, if less than 5% of Arc
## CGE-derived neurons co-cluster with GE microglia, then that connection will
## not be visualized even if it is non-zero. 

sdf_quants = sdf %>%
  filter(!is.na(next_node)) %>%
  group_by(node, next_node) %>%
  summarise(group_count = n()) %>%
  mutate(total_rows_next_node = sum(group_count)) %>%
  group_by(node) %>%
  mutate(
    is_greater_than_5_percent = group_count > 0.05 * total_rows_next_node,
    percent_of_total = group_count / total_rows_next_node * 100
  ) %>%
  ungroup()
cell_table = table(arc$class)
sdf_quants$cellcount = cell_table[sdf_quants$next_node]
bad = sdf_quants[sdf_quants$group_count < 0.05 * sdf_quants$cellcount,]
```

```{r}
## Remove things less than 5%
bad = bad[!is.na(bad$node), ]
for(i in 1:nrow(bad)){
  sdf = sdf[!(sdf$node == as.character(bad$node[i]) & 
                          sdf$next_node == as.character(bad$next_node[i])), ]
}
```


## THIS IS FOR FULL GRAPH

```{r}
## Load the fate probabilities generated from CellRank
fate_probs = as.data.frame(read_csv("/wynton/group/paredes/Aunoy/fate_df.csv"))
```

```{r}
## Classify terminal fate for Arc cell based on the maximally probable outcome
## computed from CellRank

fp_ix = match(colnames(arc), sub("_[^_]+$", "", fate_probs$barcode))
fp_arc = fate_probs[fp_ix[!is.na(fp_ix)], ]

fp_max =  colnames(fp_arc[, 2:ncol(fp_arc)])[apply(fp_arc[, 2:ncol(fp_arc)],1,which.max)]

fp_arc$fate = fp_max
```

```{r}
## Assign to error to check if any were unassigned
arc$fate = "error"
## Assign fate based on barcode similarity between fp_arc dataframe and arc dataframe
arc$fate[colnames(arc) %in% sub("_[^_]+$", "", fp_arc$barcode)] = fp_arc$fate[fp_ix[!is.na(fp_ix)]]
#match(colnames(arc),sub("_[^_]+$", "", fp_arc$barcode))
```

```{r}
## Now incorporate terminal fate data
sankey_df = arc@meta.data[c("identity", "class", "fate")]
```


```{r}
## Create sankey diagram with only Inh neuroblast classes visualized
sdf = sankey_df %>%
  filter(class %in% c("Inh CGE", "Inh LGE", "Inh MGE", "Inh CGE/LGE")) %>%
  filter(fate != "error") %>%
  make_long(identity, class, fate)
```

```{r}
node_order =  c(rev(c("Progenitor", "OPC","Microglia",
               "MGE-Derived","CGE-Derived","LGE-Derived","Glia","Endothelial","Exc/Thalamic")),
               "Ast", "Ast/Rgl", "Cpl", "End", "Epd", "Exc", "Gli IPC", "Inh CGE", 
               "Inh CGE/LGE", "Inh IPC", "Inh LGE", "Inh MGE", "Mcg",  "Oli", "Rbc",
               rev(c("MGE_Str", "MGE_Ctx", "CGE_Ctx", "LGE_OB","LGE_MSN")))
sdf$node = factor(sdf$node, levels = c(node_order))

```


```{r}
# Chart 1
pl <- ggplot(sdf, aes(x = x
                     , next_x = next_x
                     , node = node
                     , next_node = next_node
                     , fill = factor(node)
                     , label = node)
             )
pl <- pl +geom_sankey(flow.alpha = 0.5
                      , node.color = "black"
                      ,show.legend = FALSE)
#pl <- pl +geom_sankey_label(size = 3, color = "black", fill= "white", hjust = -0.5)
pl <- pl +  theme_bw()
pl <- pl + theme(legend.position = "none")
pl <- pl +  theme(axis.title = element_blank()
                  , axis.text.y = element_blank()
                  , axis.ticks = element_blank()  
                  , panel.grid = element_blank())
#pl <- pl + scale_fill_viridis_d(option = "inferno")
pl <- pl + scale_fill_manual(values = c('MGE-Derived'    = "#e377c2",
                                        'CGE-Derived'    = "#98df8a",
                                        'LGE-Derived'    = "#aec7e8",
                                        'Inh MGE'    = "#ff9896",
                                        'Inh CGE'    = "#2ca02c",
                                        'Inh CGE/LGE'    = "#17becf",
                                        'Inh LGE'    = "#1f77b4",
                                        'MGE_Str'    = "#ff7f0e",
                                        'MGE_Ctx'    = "#d62728",
                                        'CGE_Ctx'    = "#165016",
                                        'LGE_OB'    =  "#1f77b4",
                                        'LGE_MSN'    = "#aec7e8"))

color_mapping <- data.table(
  color = c(
    "#1f77b4", "#17becf", "#aec7e8", # CGE Colors
    "#98df8a", "#9467bd", # CGE/LGE and inh ipc
    "#bcbd22", "#ffbb78", "#2ca02c", #LGE
    "#8c564b", "#d62728", "#ff9896", "#ff7f0e",
    "#e377c2", "#7f7f7f")
)
                                        
                                        
pl <- pl + labs(fill = 'Nodes')
pl
```



