---
title: "marcos_wgcna"
output: html_notebook
---

# Details
Aunoy Poddar
May 12th, 2024
This is a notebook to pre-process cellranger data. The chunks iteratively
will display quality control metrics and ask the user to input the thresholds
that should be used to generate a final dataset.

Currently, these metrics will include:
- min genes per cell
- ribosomal RNA % per cell
- mitochondrial content per cell
- number of RNA counts per cell

I sort of like David Wu's approach to do a PCA and just see how the cells arrange
themselves as well.


```{r setup}
require(knitr)
#opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

```{r eval=FALSE}
current_file <- rstudioapi::getActiveDocumentContext()$path
output_file <- stringr::str_replace(current_file, '.Rmd', '.R')
knitr::purl(current_file, output = output_file)
file.edit(output_file)
```

# Import Libraries and declare file paths
```{r}
library(Seurat)
library(tictoc)
library(plyr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(cowplot)
#library(harmony)
library(SeuratObject)
library(SeuratWrappers)
library(limma)
library(pracma)
library(monocle3)
#library(DoubletFinder)
#library(DOSE)
#library(clusterProfiler)
#source("/wynton/home/paredes/aunoy/src/preprocess_helper.R")
```

# hdWGCNA
This analysis followed the tutorial by Sam Morabito at https://smorabit.github.io/hdWGCNA/articles/basic_tutorial.html 

## Loading Libraries
```{r}

# plotting and data science packages
library(tidyverse)
library(cowplot)
library(patchwork)
library(viridis)
library(grDevices)
library(writexl)

# co-expression network analysis packages:
library(WGCNA)
library(hdWGCNA)

# using the cowplot theme for ggplot
theme_set(theme_cowplot())

# set random seed for reproducibility
set.seed(12345)

#Variables to keep plots consistent:
simple = NoAxes() + NoLegend()

mysc = scale_color_viridis(option = "A")
region.pal = c("#5EBFA2", "#F69663", "#731DD8",  "#FB7C7E")

#Custom functions
ggsave <- function(..., bg = "white") ggplot2::ggsave(..., bg = bg)

#interneurons = readRDS("/wynton/group/paredes/Aunoy/integrations_w_IPC/merged_annot.rds")
```

```{r}
DimPlot(interneurons, group.by = "scvi_clusters2", reduction = "umap.scvi", label = TRUE)
```

```{r}
interneurons <- JoinLayers(interneurons)
interneurons <- FindNeighbors(interneurons, reduction = "integrated.scvi", dims = 1:30)
interneurons <- FindClusters(interneurons, resolution = 1.5, cluster.name = "scvi_clusters")
```


```{r}
interneurons$scvi_fate = interneurons$scvi_class


interneurons$scvi_fate[interneurons$scvi_clusters %in% c("12", "2", "6", "5", "27")] = "MGE_Pallial"
interneurons$scvi_fate[interneurons$scvi_clusters %in% c("33", "18", "31", "16")] = "MGE_Cortical"
interneurons$scvi_fate[interneurons$scvi_clusters %in% c("29", "28")] = "MGE_Striatal"
interneurons$scvi_fate[interneurons$scvi_clusters %in% c("3", "14", "11")] = "CGE_Pallial"
interneurons$scvi_fate[interneurons$scvi_clusters %in% c("30", "19", "13")] = "CGE_Cortical"
interneurons$scvi_fate[interneurons$scvi_clusters %in% c("1")] = "CGE_Subpallial"
interneurons$scvi_fate[interneurons$scvi_clusters %in% c("0")] = "MGE_Subpallial"
interneurons$scvi_fate[interneurons$scvi_clusters %in% c("32", "25", "26", "8", "21", "9")] = "Progenitor"
interneurons$scvi_fate[interneurons$scvi_clusters %in% c("4")] = "CGE/LGE"
interneurons$scvi_fate[interneurons$scvi_clusters %in% c("20", "7")] = "LGE D1 MSN"
interneurons$scvi_fate[interneurons$scvi_clusters %in% c("15", "23", "35", "34")] = "LGE OB"
interneurons$scvi_fate[interneurons$scvi_clusters %in% c("10")] = "LGE D1 MSN PDYN"
interneurons$scvi_fate[interneurons$scvi_clusters %in% c("24")] = "Inh IPC"
interneurons$scvi_fate[interneurons$scvi_clusters %in% c("17")] = "MGE Subpallial Cholinergic"
#interneurons$scvi_class[interneurons$scvi_clusters %in% c("0", "9")] = "MGE_Pallial"
unique(interneurons$scvi_clusters[interneurons$scvi_fate == "MGE"])
```


```{r}
## from merge datasets not modified

interneurons$scvi_fate = interneurons$scvi_class

interneurons$scvi_fate[interneurons$scvi_clusters %in% c("25", "2", "10", "3", "9")] = "MGE_Pallial"
interneurons$scvi_fate[interneurons$scvi_clusters %in% c("20", "18", "31", "29")] = "MGE_Cortical"
interneurons$scvi_fate[interneurons$scvi_clusters %in% c("26", "28")] = "MGE_Striatal"
interneurons$scvi_fate[interneurons$scvi_clusters %in% c("5", "8", "16")] = "CGE_Pallial"
interneurons$scvi_fate[interneurons$scvi_clusters %in% c("17", "15")] = "CGE_Cortical"
interneurons$scvi_fate[interneurons$scvi_clusters %in% c("1", "27")] = "CGE_Subpallial"
interneurons$scvi_fate[interneurons$scvi_clusters %in% c("0")] = "MGE_Subpallial"
interneurons$scvi_fate[interneurons$scvi_clusters %in% c("14", "22", "6")] = "Progenitor"
interneurons$scvi_fate[interneurons$scvi_clusters %in% c("4", "23")] = "CGE/LGE"
interneurons$scvi_fate[interneurons$scvi_clusters %in% c("21", "7")] = "LGE D1 MSN"
interneurons$scvi_fate[interneurons$scvi_clusters %in% c("12")] = "LGE OB"
interneurons$scvi_fate[interneurons$scvi_clusters %in% c("11")] = "LGE D1 MSN PDYN"
interneurons$scvi_fate[interneurons$scvi_clusters %in% c("24")] = "Inh IPC"
interneurons$scvi_fate[interneurons$scvi_clusters %in% c("19")] = "MGE Subpallial Cholinergic"
#interneurons$scvi_class[interneurons$scvi_clusters %in% c("0", "9")] = "MGE_Pallial"
unique(interneurons$scvi_clusters[interneurons$scvi_fate == "MGE"])
```


```{r}
DimPlot(interneurons, reduction = "umap.scvi", group.by = "scvi_fate", label= FALSE)
```

```{r}
cds = as.cell_data_set(interneurons[, interneurons$scvi_fate != "LGE D1 MSN PDYN"])
```
## Need to add partition, cluster, and umap embedding
```{r}
### 
rec.part <- c(rep(1, length(cds@colData@rownames)))
names(rec.part) <- cds@colData@rownames
rec.part <- as.factor(rec.part)
```

```{r}
cds@clusters$UMAP$partitions <- rec.part
```

```{r}
list_cluster <- interneurons$scvi_clusters#Idents(human_arc[, Idents(human_arc) %in% groups])
cds@clusters$UMAP$clusters <- list_cluster
```

```{r}
#cds@int_colData@listData$reducedDims$UMAP
cds@int_colData@listData$reducedDims$UMAP = cds@int_colData@listData$reducedDims$UMAP.SCVI
```

```{r}
cluster_before_traj <- plot_cells(cds,
           color_cells_by = 'cluster',
           label_groups_by_cluster = FALSE,
           group_label_size = 5) +
theme(legend.position = "right")

cluster_names <- plot_cells(cds,
                                 color_cells_by = 'cluster',
                                 label_groups_by_cluster = FALSE,
                                 group_label_size = 5) +
 #scale_color_manual(values = c('red', 'blue', 'green', 'maroon', 'yellow', 'grey', 'cyan')) + 
  theme(legend.position = "right")

cluster_before_traj | cluster_names
```


```{r}
new_partitions <-  function(cds, cell_type_2_remove){
  clusters_to_remove = c()
  bads = unique(cds@clusters$UMAP$clusters[colData(cds)$scvi_fate == cell_type_2_remove])
  for(bad in bads) {
      bad_table = table(colData(cds)$scvi_fate[cds@clusters$UMAP$clusters == bad])
     percentage = bad_table[cell_type_2_remove] / sum(bad_table)
     print(percentage)
     if(percentage > .9){
       clusters_to_remove = c(clusters_to_remove, bad)
       print(clusters_to_remove)
     }
  }
  return(clusters_to_remove)
}

print(new_partitions(cds, "LGE D1 MSN PDYN"))
```


```{r}
reducedDim(cds)[["LSI"]] = Embeddings(interneurons, "integrated.scvi")
```


```{r}
cds@clusters$UMAP

cds <- learn_graph(cds, verbose = TRUE)

b <- plot_cells(cds,
           color_cells_by = 'CGE_Cortical_Lin',
           label_groups_by_cluster = FALSE,
           label_branch_points = FALSE,
           label_roots = FALSE,
           label_leaves = FALSE,
           group_label_size = 5)
b
ggsave('w_cluster_mge_pseudotime.pdf', b)
```


```{r}
cds <- order_cells(cds)
```

```{r}
plot_cells(cds,
           color_cells_by = "pseudotime",
           label_cell_groups=FALSE,
           label_leaves=FALSE,
           label_branch_points=FALSE,
           label_roots = F,
           trajectory_graph_segment_size = 0.7,
           trajectory_graph_color = "cyan",
           graph_label_size=1.5) + 
  scale_color_viridis(name = "Pseudotime")+
  coord_fixed() +
  NoAxes() + 
  theme(legend.position = "bottom")
```
```{r}
CGE_Cortical_Cells = choose_graph_segments(cds, return_list = T) 
MGE_Cortical_Cells = choose_graph_segments(cds, return_list = T)
LGE_D1_MSN = choose_graph_segments(cds, return_list = T)
LGE_D1_MSN_PDYN = choose_graph_segments(cds, return_list = T)
LGE_OB = choose_graph_segments(cds, return_list = T)
MGE_Subpallial_Cholinergic = choose_graph_segments(cds, return_list = T)
MGE_Striatal_Cells = choose_graph_segments(cds, return_list = T)
```


```{r}
lineages = c("CGE_Cortical_Lin", "MGE_Cortical_Lin", "LGE_D1_MSN_Lin",
             "LGE_OB_Lin",  "MGE_Striatal_Cells_Lin")

for(lineage in lineages){
  interneurons[[lineage]] = NA
}

interneurons$CGE_Cortical_Lin[colnames(interneurons) %in% CGE_Cortical_Cells$cells] = "CGE_Cortical"
interneurons$MGE_Cortical_Lin[colnames(interneurons) %in% MGE_Cortical_Cells$cells] = "MGE_Cortical"
interneurons$LGE_D1_MSN_Lin[colnames(interneurons) %in% LGE_D1_MSN$cells] = "LGE_D1_MSN"
interneurons$LGE_D1_MSN_PDYN_Lin[colnames(interneurons) %in% LGE_D1_MSN_PDYN$cells] = "LGE_D1_MSN_PDYN"
interneurons$LGE_OB_Lin[colnames(interneurons) %in% LGE_OB$cells] = "LGE_OB"
interneurons$MGE_Subpallial_Cholinergic_Lin[colnames(interneurons) %in% MGE_Subpallial_Cholinergic$cells] = "MGE_Subpallial_Cholinergic"
interneurons$MGE_Striatal_Cells_Lin[colnames(interneurons) %in% MGE_Striatal_Cells$cells] = "MGE_Striatal_Cells"


interneurons$lineage[colnames(interneurons) %in% CGE_Cortical_Cells$cells] = "CGE_Cortical"
interneurons$lineage[colnames(interneurons) %in% MGE_Cortical_Cells$cells] = "MGE_Cortical"
interneurons$lineage[colnames(interneurons) %in% LGE_D1_MSN$cells] = "LGE_D1_MSN"
interneurons$lineage[colnames(interneurons) %in% LGE_D1_MSN_PDYN$cells] = "LGE_D1_MSN_PDYN"
interneurons$lineage[colnames(interneurons) %in% LGE_OB$cells] = "LGE_OB"
interneurons$lineage[colnames(interneurons) %in% MGE_Subpallial_Cholinergic$cells] = "MGE_Subpallial_Cholinergic"
interneurons$lineage[colnames(interneurons) %in% MGE_Striatal_Cells$cells] = "MGE_Striatal_Cells"
interneurons$pseudotime = cds@principal_graph_aux@listData$UMAP$pseudotime


#inter.exp_step3<- AddMetaData(
#  object = inter.exp_step2,
#  metadata = inter.exp_cds@principal_graph_aux@listData$UMAP$pseudotime,
#  col.name = "pseudotime"
#)
#inter.exp_step3@meta.data$pseudotime = as.numeric(gsub("Inf", NA, inter.exp_step2@meta.data$pseudotime))
saveRDS(interneurons, "/wynton/group/paredes/Aunoy/integrations_w_IPC/reviewer_fig2_wgcna_subtype.rds")
```

```{r fig.height = 10, fig.width = 12}
umap.coords = interneurons@reductions$umap.scvi@cell.embeddings
cells.meta = interneurons@meta.data
data = cbind(umap.coords, cells.meta)

lins = unique(lineages)
lins = lins[lins != "error"]

ptsize = 0.2
p = list()

for(i in 1:length(lins)) {
  p[[i]] <- ggplot(data, aes(umapscvi_1, umapscvi_2)) + 
    geom_point(color = "grey90", size = ptsize) +
    geom_point(data = data %>% filter(!is.na(!!sym(lins[i]))), aes(col = pseudotime), size = ptsize) +
    scale_color_viridis() + 
    theme_void() + 
    coord_fixed() + 
    labs(title = lins[i]) + 
    NoLegend()
}

cowplot::plot_grid(plotlist = p)
```
```{r}
ggplot(data, aes(umapscvi_1, umapscvi_2)) + 
    geom_point(color = "grey90", size = ptsize) +
    geom_point(data = data %>% filter(!is.na(!!sym(lins[i]))), aes(col = pseudotime), size = ptsize) +
    scale_color_viridis() + 
    theme_void() + 
    coord_fixed() + 
    labs(title = lins[i]) + 
    NoLegend()
```

```{r}
mgestr <- cds[,!is.na(colData(cds)$mge_striatal_cell_lin)]
pr_graph_test_res <- graph_test(mgestr, neighbor_graph="knn", cores=1)
pr_deg_ids <- row.names(subset(pr_graph_test_res, q_value < 0.05))
```

```{r}
colData(cds)$MGE_Striatal_Cells_Lin = interneurons[, interneurons$scvi_fate != "LGE D1 MSN PDYN"]@meta.data[["MGE_Striatal_Cells_Lin"]]
colData(cds)$CGE_Cortical_Lin = interneurons[, interneurons$scvi_fate != "LGE D1 MSN PDYN"]@meta.data[["CGE_Cortical_Lin"]]
colData(cds)$MGE_Cortical_Lin = interneurons[, interneurons$scvi_fate != "LGE D1 MSN PDYN"]@meta.data[["MGE_Cortical_Lin"]]
colData(cds)$LGE_D1_MSN_Lin = interneurons[, interneurons$scvi_fate != "LGE D1 MSN PDYN"]@meta.data[["MGE_Striatal_Cells_Lin"]]
colData(cds)$LGE_D1_MSN_PDYN_Lin = interneurons[, interneurons$scvi_fate != "LGE D1 MSN PDYN"]@meta.data[["MGE_Striatal_Cells_Lin"]]
colData(cds)$MGE_Subpallial_Cholinergic_Lin = interneurons[, interneurons$scvi_fate != "LGE D1 MSN PDYN"]@meta.data[["MGE_Striatal_Cells_Lin"]]
saveRDS(cds, "/wynton/group/paredes/Aunoy/integrations_w_IPC/fig2_monocle_cds.rds")

```


```{r rename}
# Project PC dimensions to whole data set
interneurons <- ProjectDim(interneurons, reduction = "pca")

# Create an expression matrix
expression_matrix <- interneurons[["RNA"]]$counts

# get gene annotations
gene_annotation <- data.frame(gene_short_name = rownames(interneurons[["RNA"]]), row.names = rownames(interneurons[["RNA"]]))

# Get cell metadata
cell_metadata <- interneurons@meta.data

# Seurat-derived CDS
cds <- new_cell_data_set(expression_matrix,
                            cell_metadata = cell_metadata,
                            gene_metadata = gene_annotation)
# Transfer Seurat embeddings

# Note that these may be calculated on the Integrated object, not the counts
#   and thus will involve fewer genes
reducedDim(cds, type = "PCA") <- interneurons@reductions$pca@cell.embeddings 
cds@reduce_dim_aux$prop_var_expl <- interneurons@reductions$pca@stdev
#plot_pc_variance_explained(my.cds)

# Transfer Seurat UMAP embeddings
cds@int_colData@listData$reducedDims$UMAP <- interneurons@reductions$umap.scvi@cell.embeddings
plot_cells(cds)

# Copy cluster info from Seurat
cds@clusters$UMAP_so$clusters <-interneurons@meta.data$scvi_clusters

cds <- cluster_cells(cds, reduction_method = "UMAP", resolution = 1e-3)

# Copy cluster info from Seurat
cds@clusters$UMAP_so$clusters <-interneurons@meta.data$scvi_clusters

# Fix from https://gitmemory.com/cole-trapnell-lab
rownames(cds@principal_graph_aux$UMAP$dp_mst) <- NULL
colnames(cds@int_colData@listData$reducedDims$UMAP) <- NULL

plot_cells(cds, color_cells_by = "partition", group_label_size = 3.5)
plot_cells(cds, color_cells_by = "scvi_fate", show_trajectory_graph = FALSE, group_label_size = 3.5)

cds = readRDS("/wynton/group/paredes/Aunoy/integrations_w_IPC/fig2_monocle_cds.rds")

cds <- learn_graph(cds, use_partition = T, verbose = TRUE)

#my.cds <-order_cells(my.cds, reduction_method = "UMAP", root_cells = colnames(cds[, clusters(cds) == 'Replicating_IN']))
plot_cells(cds, color_cells_by = 'clusters', show_trajectory_graph = TRUE, group_label_size = 3.5)
```


```{r}
b <- list()

vals = c(5, 10, 20, 30)
eu_drs = c(0.5, 1, 3, 5)
count = 1
combos = length(vals)*length(eu_drs)

for(val in vals) {
  for(eudr in eu_drs){
    print(paste0(count, " of ", combos))
    cds <- learn_graph(cds, use_partition = FALSE,
                   #close_loop = T, 
                    learn_graph_control = list(#nn.k = 10,
                   minimal_branch_len = val,
                   euclidean_distance_ratio = eudr, 
                   geodesic_distance_ratio = 1/3), verbose = TRUE)
    b[[count]] <-plot_cells(cds,
           color_cells_by = 'cluster',
           label_groups_by_cluster = FALSE,
           label_branch_points = FALSE,
           label_roots = FALSE,
           label_leaves = FALSE,
           group_label_size = 5) + ggtitle(paste0("minimal_branch_len: ",
                                                            val, "; eu_d_ratio: ",
                                           eudr))
    count = count + 1
  }
}

cowplot::plot_grid(plotlist = b)
```

    
```{r}
cds = cluster_cells(reduction_method = "UMAP", cluster_method = "louvain", cds, k = 50,
                    verbose = TRUE)
```

    
```{r}
#cds = readRDS("/wynton/group/paredes/Aunoy/integrations_w_IPC/fig2_monocle_cds.rds")
cds = readRDS("/wynton/group/paredes/Aunoy/integrations_w_IPC/fig2_monocle_cds_special.rds")
cds@clusters$UMAP_so$clusters <-interneurons@meta.data$scvi_fate

cds <- learn_graph(cds, use_partition = T, learn_graph_control = list())

names(rec.part) = cds@colData@rownames
rec.part <- as.factor(rec.part)
cds@clusters$UMAP$partitions <- rec.part

plot_cells(cds, color_cells_by = 'cluster', show_trajectory_graph = TRUE, group_label_size = 3.5)
```



```{r}
new_partitions <-  function(cds, cell_type_2_remove, threshold = 0.9){
  clusters_to_remove = c()
  bads = unique(cds@clusters$UMAP$clusters[colData(cds)$scvi_class == cell_type_2_remove])
  for(bad in bads) {
      bad_table = table(colData(cds)$scvi_class[cds@clusters$UMAP$clusters == bad])
     percentage = bad_table[cell_type_2_remove] / sum(bad_table)
     if(percentage > threshold){
       clusters_to_remove = c(clusters_to_remove, bad)
       print(clusters_to_remove)
     }
  }
  return(clusters_to_remove)
}

rec.part <- c(rep(1, length(cds@colData@rownames)))

groups_to_remove = c("LGE D1 MSN PDYN")
partition_num = 2
for(badgrp in groups_to_remove){
    bad_clusters = new_partitions(cds, badgrp, threshold = 0.1)
    rec.part[cds@clusters$UMAP$clusters %in% bad_clusters] = partition_num
    partition_num = partition_num + 1
}
```

    
```{r}
#deg_ids <- row.names(subset(deg_cge, q_value == 0))
cds@reduce_dim_aux[['PCA']][['model']][['svd_v']] <- interneurons@reductions[["pca"]]@feature.loadings.projected
# Transfer PCs stdevs
cds@reduce_dim_aux[['PCA']][['model']][['svd_sdev']] <- interneurons@reductions$pca@stdev
# Transfer PCs cell embeddings (not necessary if UMAP transferred from Seurat used)
reducedDim(cds, type = "PCA") <-   interneurons@reductions$pca@cell.embeddings
```

```{r}
CGE_Cortical_Cells = choose_graph_segments(cds, return_list = T) 
MGE_Cortical_Cells = choose_graph_segments(cds, return_list = T)
LGE_D1_MSN = choose_graph_segments(cds, return_list = T)
LGE_D1_MSN_PDYN = choose_graph_segments(cds, return_list = T)
LGE_OB = choose_graph_segments(cds, return_list = T)
MGE_Subpallial_Cholinergic = choose_graph_segments(cds, return_list = T)
MGE_Striatal_Cells = choose_graph_segments(cds, return_list = T)
```

```{r}
colData(cds)$CGE_CX_LIN = NA
colData(cds)$MGE_CX_LIN = NA
colData(cds)$LGE_MSN_LIN = NA
colData(cds)$LGE_MSN2_LIN = NA
colData(cds)$LGE_OB_LIN = NA
colData(cds)$MGE_SC_LIN = NA
colData(cds)$MGE_ST_LIN = NA


colData(cds)$CGE_CX_LIN[rownames(colData(cds)) %in% CGE_Cortical_Cells$cells] = "CGE_CX_LIN"
colData(cds)$MGE_CX_LIN[rownames(colData(cds)) %in% MGE_Cortical_Cells$cells] = "MGE_CX_LIN"
colData(cds)$LGE_MSN_LIN[rownames(colData(cds)) %in% LGE_D1_MSN$cells] = "LGE_MSN_LIN"
colData(cds)$LGE_MSN2_LIN[rownames(colData(cds)) %in% LGE_D1_MSN_PDYN$cells] = "LGE_MSN2_LIN"
colData(cds)$LGE_OB_LIN[rownames(colData(cds)) %in% LGE_OB$cells] = "LGE_OB_LIN"
colData(cds)$MGE_SC_LIN[rownames(colData(cds)) %in% MGE_Subpallial_Cholinergic$cells] = "MGE_SC_LIN"
colData(cds)$MGE_ST_LIN[rownames(colData(cds)) %in% MGE_Striatal_Cells$cells] = "MGE_ST_LIN"
```


## GGPLOT stacked for dataset
x axis = binned pseudotime
y axis = counts of each categorical variable
```{r}
#my.cds_subset = cds[,!is.na(colData(cds)$MGE_CX_LIN)]
ggplot(colData(cds) %>% as.data.frame() %>%
         filter(!is.na(MGE_ST_LIN)), aes(pseudotime, fill = dataset)) + 
    geom_histogram(bins = 10, position = "fill") + 
    scale_fill_manual(values = c("#FF66AE", "#B88CC2", "#058E8E", "#C1F1AD")) +
    scale_y_continuous(label = scales::percent,  expand = c(0,0), name = "Percentage of cells") +
    scale_x_continuous(expand = c(0,0), name = "Pseudotime")  + 
    #labs(title = "CGE-VIP/RELN Lineage") + 
    theme(plot.title = element_text(family = "Arial", face = "bold", hjust = 0.5), legend.title = element_blank())
```
```{r fig.height = 6, fig.width = 12}
umap.coords = reducedDim(cds, "UMAP")
cells.meta = colData(cds)
data = as.data.frame(cbind(umap.coords, cells.meta))

lins = c("CGE_CX_LIN", "MGE_CX_LIN", "LGE_MSN_LIN", #"LGE_MSN2_LIN",
"LGE_OB_LIN", "MGE_SC_LIN", "MGE_ST_LIN")

ptsize = 0.2
p = list()

for(i in 1:length(lins)) {
  p[[i]] <- ggplot(data, aes(V1, V2)) + 
    geom_point(color = "grey90", size = ptsize) +
    geom_point(data = data %>% filter(!is.na(!!sym(lins[i]))), aes(col = pseudotime), size = ptsize) +
    scale_color_viridis(option = "A") + 
    theme_void() + 
    coord_fixed(ratio = 0.5) + 
    labs(title = lins[i]) + 
    NoLegend()
}

cowplot::plot_grid(plotlist = p, ncol = 6)
```


```{r}
saveRDS(cds, "/wynton/group/paredes/Aunoy/integrations_w_IPC/fig2_monocle_cds_special1.rds")
```



```{r}
resolution = 1e-2
my.cds_subset = cds[,!is.na(colData(cds)$MGE_SC_LIN)]
pr_deg_ids <- row.names(subset(sc_test_graph_test, q_value < 0.05))
gene_module_df <- find_gene_modules(my.cds_subset[pr_deg_ids,], resolution=resolution)
```

```{r}
cell_group_df <- tibble::tibble(cell=row.names(colData(my.cds_subset)), 
                                cell_group=colData(my.cds_subset)$scvi_fate)
agg_mat <- aggregate_gene_expression(my.cds_subset, gene_module_df, cell_group_df)
row.names(agg_mat) <- stringr::str_c("Module ", row.names(agg_mat))
pheatmap::pheatmap(agg_mat,
                   scale="column", clustering_method="ward.D2", main = paste0("Resolution:", resolution))
```

```{r}
agg_mat <- aggregate_gene_expression(my.cds_subset, gene_module_df)
module_dendro <- hclust(dist(agg_mat))
gene_module_df$module <- factor(gene_module_df$module, 
                                levels = row.names(agg_mat)[module_dendro$order])

plot_cells(my.cds_subset,
           genes=gene_module_df,
           label_cell_groups=FALSE,
           show_trajectory_graph=FALSE)
```

```{r}
plot_dataset_by_lin <- function(cds_obj){
  my_
}
```

```{r}
my_df = as.data.frame(t(agg_mat))
my_df$pseudotime = colData(my.cds_subset)$pseudotime
```

```{r}
my_df$bins = as.numeric(my_df$pseudotime %>% Hmisc::cut2(g=50))
```

```{r}
p1 = ggplot(my_df, aes(x = bins, y = mod3, color=dataset)) +
  geom_point() +
  geom_smooth() +
  scale_color_manual(values=c("red", "grey", "grey", "grey"))+
  xlab('Pseudotime') +
  ylab('Module_Score') +
  theme(
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank()
  ) +
  NoLegend()

p1 + facet_wrap(~dataset, ncol=1)
```
```{r}
cge_genes = c("GBX2", "DSCAM", "ZIC1","LHX8")


p <- FeaturePlot(interneurons, reduction = "umap.scvi", features = cge_genes,
                 combine = FALSE)

for(i in 1:length(p)) {
  p[[i]] <- p[[i]] + NoLegend() + NoAxes()
}

cowplot::plot_grid(plotlist = p)
```

```{r fig.width = 3, fig.height = 6}
cge_genes = c("LHX8", "ISL1", "ZIC1", "GBX2")
#cge_genes = mydf_2$id[11:25]

mplot = plot_cells(my.cds_subset,
           genes=cge_genes,
           label_cell_groups=FALSE,
           show_trajectory_graph=FALSE)

mplot + facet_wrap(~feature_label, ncol=1)
```

```{r}
genes_to_label = c("ISLR2", "TAC1", "PENK", "FOXP1", "CNTNAP2")
gene_module_df$labeling = gene_module_df$id
gene_module_df$labeling[!gene_module_df$labeling %in% genes_to_label] = ""

gene_module_df %>%
  filter(module == 5 & dim_1 < -12.5) %>%
  ggplot(aes(x = dim_1, y = dim_2, label = id, color = module)) + 
  geom_point() + 
  geom_label_repel(max.overlaps = 100)
```


```{r}
my.cds_subset <- order_cells(my.cds_subset)
```

```{r}
plot_genes_in_pseudotime(my.cds_subset[rowData(my.cds_subset)$gene_short_name %in% c("GRM7", "KAZN"), ],
                         color_cells_by="scvi_fate",
                         min_expr=0.5)
```
```{r}
plot_genes_in_pseudotime(my.cds_subset[rowData(my.cds_subset)$gene_short_name %in% c("MEF2C-AS1", "MAF"), ],
                         color_cells_by="dataset",
                         min_expr=0.5)
```
```{r}

```


## Setup
```{r}
#inter.exp_step3 = readRDS("/wynton/group/paredes/Aunoy/integrations_w_IPC/merged_annot.rds")
interneurons@misc$active_wgcna = NULL
interneurons@misc$inter_fraction_0.05 = NULL


interneurons <- SetupForWGCNA(
  interneurons,
  gene_select = "fraction", # the gene selection approach
  fraction = 0.05, # fraction of cells that a gene needs to be expressed in order to be included
  wgcna_name = "interneuron_expression_modules", # the name of the hdWGCNA experiment
  group.by = 'dataset')

ncol(interneurons) #20470 cells
```
```{r}
length(GetWGCNAGenes(interneurons))

interneurons$celltype = "interneuron_lineage"

# construct metacells:
interneurons <- MetacellsByGroups(
  seurat_obj = interneurons,
  group.by = c("dataset", "celltype"),
  k = 25,
  reduction = 'integrated.scvi',
  ident.group = 'celltype'
)

interneurons <- NormalizeMetacells(interneurons)

# set up a gene expression matrix list for each study
interneurons <- SetMultiExpr(
  interneurons,
  group_name = "interneuron_lineage",
  group.by = "cell_type",
  multi.group.by = "Study",
  multi_groups = NULL
)

# test the soft power threshold
interneurons <- TestSoftPowersConsensus(
  interneurons,
  group.by='cell_type',
  group_name="MG",
  setDatExpr=FALSE
)

plot_list <-  PlotSoftPowers(interneurons)

pdf(paste0(fig_dir, 'test_softpower_ggplot2.pdf'), width=10, height=8)
wrap_plots(plot_list[[1]], ncol=2) + plot_annotation(
  title = 'Morabito & Miyoshi',theme = theme(plot.title = element_text(hjust=0.5)))

wrap_plots(plot_list[[2]], ncol=2) + plot_annotation(
  title = 'Mathys',theme = theme(plot.title = element_text(hjust=0.5)))

wrap_plots(plot_list[[3]], ncol=2) + plot_annotation(
  title = 'Zhou',theme = theme(plot.title = element_text(hjust=0.5)))
dev.off()


interneurons <- ConstructNetwork(
  interneurons,
  soft_power=c(6,6,8),
  consensus=TRUE,
  setDatExpr=FALSE,
  detectCutHeight=0.999999
)

# plot the dendrogram
pdf(paste0(fig_dir, "MG_dendro.pdf"),height=3, width=6)
PlotDendrogram(interneurons, main='MG Consensus Dendrogram')
dev.off()

interneurons <- ModuleEigengenes(
  interneurons,
  group.by.vars="Study", # snRNAseq batch
  verbose=FALSE
)

# compute module connectivity:
interneurons <- ModuleConnectivity(interneurons)

# run RenameModules
interneurons <- ResetModuleNames(
  interneurons,
  new_name = "MG-M"
)
print(names(GetModules(interneurons)))
```

```{r}
plot_list[[4]]
```



```{r}
DimPlot(interneurons, group.by = "scvi_clusters", reduction = "umap.scvi",
        label = TRUE) + NoLegend()
```
```{r}
interneurons$scvi_fate = interneurons$scvi_class

interneurons$scvi_fate[interneurons$scvi_clusters %in% c("25", "2", "10", "3", "9")] = "Imm-MGE"
interneurons$scvi_fate[interneurons$scvi_clusters %in% c("20", "18", "31", "29")] = "cortical MGE"
interneurons$scvi_fate[interneurons$scvi_clusters %in% c("26", "28")] = "striatal MGE"
interneurons$scvi_fate[interneurons$scvi_clusters %in% c("5", "8", "16")] = "Imm-CGE"
interneurons$scvi_fate[interneurons$scvi_clusters %in% c("17", "15")] = "cortical CGE"
interneurons$scvi_fate[interneurons$scvi_clusters %in% c("1", "27")] = "CGE"
interneurons$scvi_fate[interneurons$scvi_clusters %in% c("0")] = "MGE"
interneurons$scvi_fate[interneurons$scvi_clusters %in% c("14", "22", "6", "13")] = "Progenitor"
interneurons$scvi_fate[interneurons$scvi_clusters %in% c("4", "23")] = "Imm-CGE/LGE"
interneurons$scvi_fate[interneurons$scvi_clusters %in% c("21", "7")] = "LGE D1 MSN"
interneurons$scvi_fate[interneurons$scvi_clusters %in% c("12", "32", "33")] = "OB-LGE"
interneurons$scvi_fate[interneurons$scvi_clusters %in% c("11")] = "LGE D1 MSN PDYN"
interneurons$scvi_fate[interneurons$scvi_clusters %in% c("24")] = "In-IPC"
interneurons$scvi_fate[interneurons$scvi_clusters %in% c("19")] = "cholinergic MGE"
```


```{r}
unique(interneurons$scvi_clusters[interneurons$scvi_fate == "CGE/LGE"])
```

```{r}
color_mapping <- data.table::data.table(
  color = c("#165016", "#2ca02c", "#98df8a", # CGE Colors
    "#17becf", "#9467bd", # CGE/LGE and inh ipc
    "#aec7e8", "cornflowerblue", "#1f77b4", #LGE
    "#8c564b", "#d62728", "#ff9896", "#ff7f0e",
    "#e377c2", "#7f7f7f")
)
interneurons$scvi_fate = factor(interneurons$scvi_fate,
        levels = c("cortical CGE", "Imm-CGE", "CGE", 
                   "Imm-CGE/LGE", "In-IPC",
                   "LGE D1 MSN", "LGE D1 MSN PDYN", "OB-LGE",
                   "cholinergic MGE", "cortical MGE", "Imm-MGE", "striatal MGE",
                   "MGE", "Progenitor"))
DimPlot(interneurons, reduction = "umap.scvi", pt.size = 0.1, alpha = 0.7,
        cols = color_mapping$color, group.by = "scvi_fate", raster = FALSE) +
  NoLegend() + NoAxes() + 
    coord_fixed(ratio = 0.8) 
```

```{r fig.height = 8, fig.width = 3}
Idents(interneurons) = "class"


VlnPlot(interneurons[, interneurons$dataset == "arc"], features = c("TOP2A", "CENPF", "MKI67",
                                   "GAD1", "DCX", "DLX1", 
                                   "DLX2", "DLX5", "DLX6-AS1",
                                   "ARX", "PROX1", "NR2F2-AS1",
                                   "MEIS2", "FOXP2", "TSHZ1",
                                   "ERBB4", "PDZRN3", "TOX3",
                                   "KAZN", "MAF", "MAFB", "MEF2C"),
        idents = c("Inh IPC"), stack = TRUE, flip = TRUE) + NoLegend()
```

### 
cge = 6 6 6 5
mge = 5 6 6 6 

```{r}
interneurons = readRDS("/wynton/group/paredes/Aunoy/integrations_w_IPC/reviewer_fig2_wgcna.rds")
interneurons = readRDS("/wynton/group/paredes/Aunoy/integrations_w_IPC/mgewgcna.rds")
interneurons = readRDS("/wynton/group/paredes/Aunoy/integrations_w_IPC/cgewgcna.rds")
```

```{r}
saveRDS(interneurons, "/wynton/group/paredes/Aunoy/integrations_w_IPC/reviewer_fig2_wgcna.rds")
```


```{r}
interneurons$dataset
```


```{r}
library("ggbeeswarm")
#interneurons$grouped_age = interneurons$age
#interneurons$age = as.character(interneurons$grouped_age)
interneurons$age[grepl("GW09", interneurons$orig.ident)] = "9"
interneurons$age[grepl("GW12", interneurons$orig.ident)] = "12"
interneurons$age[grepl("GW13", interneurons$orig.ident)] = "13"
interneurons$age[grepl("GW16", interneurons$orig.ident)] = "16"
interneurons$age[grepl("GW18", interneurons$orig.ident)] = "18"
interneurons$age[interneurons$orig.ident %in% c("9C", "9G")] = "17"
interneurons$age[interneurons$orig.ident %in% c("24C", "24G")] = "18"
interneurons$age[interneurons$orig.ident %in% c("26C", "26G")] = "19"
interneurons$age[interneurons$orig.ident %in% c("11C", "11G")] = "20"
interneurons$age[interneurons$orig.ident %in% c("56C", "56G")] = "21"
interneurons$age[interneurons$orig.ident %in% c("30C", "30G")] = "22"
interneurons$age[interneurons$orig.ident %in% c("63C", "63G")] = "23"
interneurons$age[interneurons$orig.ident %in% c("34G", "34C")] = "21"
interneurons$age[interneurons$orig.ident %in% c("23C", "23G")] = "24"
interneurons$age[interneurons$orig.ident %in% c("62C", "62G")] = "25"
interneurons$age[interneurons$orig.ident %in% c("64C", "64G")] = "26"
interneurons$age[interneurons$orig.ident %in% c("3C", "3G")] = "26"
interneurons$age[interneurons$orig.ident %in% c("60C", "60G")] = "33"
interneurons$age[interneurons$orig.ident %in% c("10C", "10G")] = "33"
interneurons$age[interneurons$orig.ident %in% c("6C", "6G")] = "38"
interneurons$age[grepl("023_Arc", interneurons$orig.ident)] = "30"
interneurons$age[grepl("003_", interneurons$orig.ident)] = "40"
interneurons$age[grepl("2014", interneurons$orig.ident)] = "40"
interneurons$age = as.numeric(interneurons$age)

interneurons$normed_age = (interneurons$age - min(interneurons$age)) / (max(interneurons$age) - min(interneurons$age))
```

```{r fig.height = 8, fig.width = 5}
age_df = interneurons@meta.data[, c("age", "scvi_fate")]

ap = list()
i = 1

for(fate in levels(interneurons$scvi_fate)){
  ap[[i]] = age_df %>%
  filter(scvi_fate == fate) %>%
  ggplot(aes(x = age, y = scvi_fate, color = age)) +
  #geom_violin() +
  geom_beeswarm(cex = 0.5) +#
  #geom_jitter(width = 0.75, height = 0.4, alpha = 0.1) + 
  NoLegend() + theme_classic() + 
  #paletteer::scale_color_paletteer_c("pals::ocean.matter")+
  coord_fixed(ratio = 0.8) + 
  #theme(text = element_text(size = 8),
  #      axis.text.x = element_text(angle = 90, hjust = 1)) +xlab("") + ylab("")
  i = i + 1
}

cowplot::plot_grid(plotlist = ap[], ncol = 2)

```

```{r fig.height = 1.3, fig.width = 1.79}
age_df = interneurons@meta.data[, c("scvi_fate", "age")]

age_df %>%
  filter(scvi_fate %in% c("Imm-CGE", "Imm-MGE", "Imm-CGE/LGE", "OB-LGE", "In-IPC")) %>%
  ggplot(aes(x = factor(scvi_fate, level = rev(c("Imm-CGE", "Imm-MGE", "Imm-CGE/LGE", "OB-LGE", "In-IPC"))), fill = age)) +
  geom_bar(position="stack") + xlab("") + paletteer::scale_fill_paletteer_d("NineteenEightyR::miami2") +
  theme_classic()  + NoLegend() + RotatedAxis()
```


```{r fig.height = 1.3, fig.width = 2.1}
age_df = interneurons@meta.data[, c("dataset", "scvi_fate")]

age_df %>%
  filter(scvi_fate %in% c("Imm-CGE", "Imm-MGE", "Imm-CGE/LGE", "OB-LGE", "In-IPC")) %>%
  ggplot(aes(x = factor(scvi_fate, level = rev(c("Imm-CGE", "Imm-MGE", "Imm-CGE/LGE", "OB-LGE", "In-IPC"))), fill = dataset)) +
  geom_bar(position="fill") + xlab("") +
  theme_classic() + coord_flip() + scale_fill_manual(values = c("#FF66AE", "#B88CC2", "#058E8E", "#C1F1AD")) + NoLegend() + RotatedAxis()
```

```{r}
umap.coords = interneurons@reductions$umap.scvi@cell.embeddings
meta_cols = colnames(interneurons@meta.data)
cells.meta = interneurons@meta.data[, meta_cols[grepl("MGE", meta_cols)]]
data = as.data.frame(cbind(umap.coords, cells.meta))
myplots = list()
i = 1
pt.size = 0.01
for(column in sort(colnames(cells.meta))){
  myplots[[i]] <- ggplot(data, aes(umapscvi_1, umapscvi_2)) + 
  geom_point(color = "grey90", size = pt.size) +
  geom_point(data = data  %>% filter(!is.na(!!sym(column))) %>% arrange(!!sym(column)), 
             aes(col = !!sym(column)), size = pt.size, alpha = 0.8) +
  #scale_colour_gradient(low = "grey90", high = "#2ca02c") +#d62728
    scale_colour_gradient(low = "grey90", high = "#d62728") + 
  theme_void() + 
  coord_fixed(ratio = 0.8) + 
  labs(title = column) + #+ 
  NoLegend()
    i = i + 1
}

cowplot::plot_grid(plotlist = myplots, ncol = 2, scale = 0.7)
```



```{r}

```


```{r}
age_df %>%
  filter(scvi_fate == "CGE") %>%
  ggplot(aes(x = age, y = scvi_fate, color = age)) +
  geom_violin() + geom_beeswarm() +#
  #geom_jitter(width = 0.75, height = 0.4, alpha = 0.1) + 
  NoLegend() + theme_classic() + 
  paletteer::scale_color_paletteer_c("pals::ocean.matter")+
  coord_fixed(ratio = 0.5)

```


```{r}
PlotDendrogram(interneurons, main='Inh Consensus Dendrogram')
```

```{r}
print(names(GetModules(interneurons)))
```


```{r}
library(MetBrewer)

modules <- GetModules(interneurons)
mods <- levels(modules$module)
mod_colors <- dplyr::select(modules, c(module, color)) %>%
  distinct %>% arrange(module) %>% .$color
n_colors <- length(mod_colors) -1

new_colors <- paste0(met.brewer("Renoir", n=n_colors, type='discrete'))
interneurons <- ResetModuleColors(interneurons, new_colors)
```


```{r}
ixs = plot_df %>%
  group_by(variable) %>%
  summarise(max = max(value, na.rm=TRUE)) %>%
  arrange(desc(max))

bin_order = plot_df[match(ixs$max, plot_df$value), ] %>%
  arrange(bin)

bin_order$variable
```


```{r}
# compute the average ME score in each bin:

interneurons <- BinPseudotime(interneurons, n_bins=c(5,50,100))


features <- mods
avg_scores <- interneurons@meta.data %>%
  group_by(pseudotime_bins_50) %>%
  select(all_of(features)) %>%
  summarise_all(mean)

colnames(avg_scores)[1] <- 'bin'

plot_df <- reshape2::melt(avg_scores)

mods

plot_df$variable = as.character(plot_df$variable)
plot_df$variable = factor(plot_df$variable, levels = as.character(bin_order$variable))

color_ixs = match(levels(plot_df$variable)[levels(plot_df$variable) != "grey"], mods[mods != "grey"], )

p1 <- plot_df %>%
  filter(variable != "grey") %>%
  ggplot(aes(x = as.numeric(bin), y = value, color= variable)) +
  geom_point() +
  geom_smooth() +
  scale_color_manual(values=new_colors[color_ixs])+
  xlab('Pseudotime') +
  ylab('hME') +
  theme(
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank()
  ) +
  NoLegend()
p1 + facet_wrap(~variable, ncol=4, scales='free')
```


```{r}

plot_list <- ModuleFeaturePlot(interneurons, order=TRUE, raster=TRUE, raster_dpi=400, alpha=0.7,
                               reduction = "umap.scvi")
#pdf("figures/MG_featureplot_hMEs.pdf",height=4, width=16)
wrap_plots(plot_list, ncol=4)
#dev.off()

mes = GetMEs(interneurons)

interneurons@meta.data = cbind(interneurons@meta.data, mes)
plot_list <- ModuleFeaturePlot(interneurons, order=TRUE, raster=TRUE, reduction = "umap.scvi", 
                               raster_dpi=400, alpha=0.7, features='MEs')
#pdf("figures/MG_featureplot_MEs.pdf",height=4, width=16)
wrap_plots(plot_list, ncol=4)
#dev.off()
```


```{r}
mods = GetModules(interneurons)
mods <- levels(mods$module)

arc_data = interneurons@meta.data[, c("dataset", mods)]


#rev_bov = as.character(bin_order$variable)
#rev_bov = rev_bov[rev_bov != "grey"]

#color_ixs = match(rev_bov, mods[mods != "grey"], )


arc_data %>%
  pivot_longer(!dataset, names_to = "module", values_to = "score") %>%
  filter(dataset == "arc") %>%
  filter(module != "grey") %>%
  ggplot(aes(x = factor(module, levels = rev_bov), y = score, fill = factor(module,
                                                                            levels = rev_bov),
             color = factor(module, levels = rev_bov))) +
  scale_fill_manual(values=new_colors[color_ixs])+
  scale_color_manual(values=new_colors[color_ixs])+
  geom_boxplot(notch = TRUE,color = "black", outlier.alpha = 0.3, outlier.shape = NA) + #limy(0, 18) + 
  #geom_violin() + 
  geom_jitter(size = 0.1, alpha = 0.3, width = 0.1) + 
  theme_classic() + NoLegend() + RotatedAxis()
```

```{r}
mods = GetModules(cge)
mods <- levels(mods$module)

arc_data = cge@meta.data[, c("dataset", mods)]


arc_data %>%
  pivot_longer(!dataset, names_to = "module", values_to = "score") %>%
  filter(dataset == "arc") %>%
  filter(module != "grey") %>%
  ggplot(aes(x = module, y = score, fill = module,
             color = module)) +
  #scale_fill_manual(values=new_colors[color_ixs])+
  #scale_color_manual(values=new_colors[color_ixs])+
  geom_boxplot(notch = TRUE,color = "black", outlier.alpha = 0.3, outlier.shape = NA) + #limy(0, 18) + 
  #geom_violin() + 
  geom_jitter(size = 0.1, alpha = 0.3, width = 0.1) + 
  theme_classic() + NoLegend() + RotatedAxis()
```
```{r}
cge_migs = cge_modules %>%
  filter(gene_name %in% nmig_genes) %>%
  filter(module == "CGE4")
mge_migs = mge_modules %>%
  filter(gene_name %in% nmig_genes) %>%
  filter(module == "MGE1")

cge_mge = intersect(cge_migs$gene_name, mge_migs$gene_name)
mge_unique = setdiff(mge_migs$gene_name, cge_migs$gene_name)
cge_unique = setdiff(cge_migs$gene_name, mge_migs$gene_name)
```

CGE1 / MGE 1:
"SEMA6C"  "ARHGEF2" "NAV1"    "PLXNA2"  "CTNNA2"  "GSK3B"   "NIPBL"   "MAPK8"   "PSEN1"   "PLXNB2"  "ARX"     "GPR173" 

MGE unique
 [1] "ACAP3"    "ASTN1"    "PLXNB1"   "ZSWIM6"   "PHACTR1"  "FYN"      "PLXNA4"   "LRP12"    "PTK2"     "LHX6"     "ZMIZ1"    "MARK2"   
[13] "ULK1"     "DCLK1"    "SOX1"     "PAFAH1B1" "STAT3"    "CDKL5"    "PLXNA3"  

CGE unique
"MYH10" "DCX"  

CGE/MGE 2
"DAB1"   "CAMK2A" "CAMK2B" "NTRK2"  "NRG3"   "MDGA2" 

MGE unique:
"SLIT2" "PRKG1" "UNC5C" "RELN" 

CGE unique:
"NTNG1"  "SEMA4A" "CCK"    "ROBO1"  "APBB2"  "MEF2C"  "PLXNA4" "SEMA4D" "ASTN2"  "NSMF"   "FAT3"   "SEMA6D" "NTRK3"  "ITGA3"  "SEMA6B"
 "VLDLR"

3:
MGE unique: "CXCR4"  "TUBA1A" "NKX2-1"
CGE unique: "NDN"


4:
"ERBB4" "UNC5D"

mge unique: "SEMA6A" "MDGA1" 
cge unique: "ASTN1"   "DISC1"   "CHL1"    "SPOCK1"  "PHACTR1" "AUTS2"   "SEMA3C"  "SEMA3A"  "KIRREL3" "DCLK1"   "FLRT2"   "MAPT"    "FGF13"  



```{r}
library(igraph)

# individual module networks
ModuleNetworkPlot(
  interneurons,
  mods = "all",
  #label_center=TRUE,
  outdir = paste0("~/src/", 'CGEIN_hubNetworks/')
)
```

```{r}
interneurons <- RunModuleUMAP(
  interneurons,
  n_hubs = 10,
  n_neighbors=15,
  min_dist=0.3,
  spread=5
)

# get the hub gene UMAP table from the seurat object
umap_df <- GetModuleUMAP(
  interneurons
)

#label_genes <- c('NKX2-1', 'LHX6', 'DLX2', 'DLX5', 'ARX', 'DLX6-AS1',
#                 'CXCR4', 'ACKR3', 'MEF2C', 'TOP2A', 'MAFB', 'NRXN3')
label_genes <- c('NR2F2-AS1', 'PROX1', 'DLX2', 'DLX5', 'ARX', 'DLX6-AS1',
                 'CXCR4', 'SP8', 'CNR1', 'SCGN')

library(reshape2)
#library(igraph)
pdf(paste0("~/src", 'CGEIN_hubgene_umap_igraph.pdf'), width=15, height=15)
ModuleUMAPPlot(
  interneurons,
  edge.alpha=0.5,
  sample_edges=TRUE,
  keep_grey_edges=FALSE,
  edge_prop=0.075, # taking the top 20% strongest edges in each module
  label_genes = label_genes,
  label_hubs=10 # how many hub genes to plot per module?
)
dev.off()
```

```{r}
p <- PlotKMEs(interneurons, ncol=3)

p
```




```{r}
mge_modules <- GetModules(interneurons) %>% subset(module !=  "grey")
cge_modules <- GetModules(cge) %>% subset(module !=  "grey")

mge_genes = mge_modules %>% filter(module == "MGE1")
cge_genes = cge_modules %>% filter(module == "CGE2")
```

```{r}
cge_genes$gene_name
```

```{r}
mge_tfs %>% arrange(desc(kME_MGE1)) %>% filter(! gene_name %in% cge_modules$ge)
```



```{r}
cge_tfs = cge_modules %>%
  filter(gene_name %in% tfs) %>%
  filter(module == "CGE4")
mge_tfs = mge_modules %>%
  filter(gene_name %in% tfs) %>%
  filter(module == "MGE4")

mge_unique = setdiff(mge_tfs$gene_name, cge_tfs$gene_name)
cge_unique = setdiff(cge_tfs$gene_name, mge_tfs$gene_name)
```
```{r}
mge_tfs %>% arrange(desc(kME_MGE4)) %>% filter(gene_name %in% mge_unique)
```
```{r}
cge_tfs %>% arrange(desc(kME_CGE3))
```

```{r}
cge_rcp = cge_modules %>%
  filter(gene_name %in% receptor_genes$Gene) %>%
  filter(module == "CGE2")
mge_rcp = mge_modules %>%
  filter(gene_name %in% receptor_genes$Gene) %>%
  filter(module == "MGE2")

mge_unique_rcp = setdiff(mge_rcp$gene_name, cge_rcp$gene_name)
cge_unique_rcp = setdiff(cge_rcp$gene_name, mge_rcp$gene_name)
```

```{r}
mge_rcp %>% arrange(desc(kME_MGE2)) %>% filter(gene_name %in% mge_unique_rcp)
```
```{r}
cge_rcp %>% arrange(desc(kME_CGE2)) %>% filter(gene_name %in% cge_unique_rcp)
```

```{r}
shared = intersect(mge_genes$gene_name, cge_genes$gene_name)
not_shared = 
```

```{r}
cge_mods = unique(cge_modules$module)
mge_mods = unique(mge_modules$module)

i = 1
overlaps = c()
cges = c()
mges = c()

for(cge_moddo in cge_mods){
  for(mge_moddo in mge_mods){
    mge_genes = mge_modules %>% filter(module == mge_moddo)
    cge_genes = cge_modules %>% filter(module == cge_moddo)
    overlaps = c(overlaps, length(intersect(mge_genes$gene_name, cge_genes$gene_name)))
    cges = c(cges, cge_moddo)
    mges = c(mges, mge_moddo)
  }
}

corr_df = as.data.frame(cbind(overlaps, cges, mges))
colnames(corr_df) = c("intersections", "cge_module", "mge_module")
```

```{r fig.height = 1.8, fig.width = 4}
corr_df %>%
  ggplot(aes(x = cges, y = mges, fill = as.numeric(intersections))) + 
  geom_tile(color = "white") + viridis::scale_fill_viridis() + theme_classic() + RotatedAxis()# +
```
```{r}
mge_genes = mge_modules %>% filter(module == "MGE2")
cge_genes = cge_modules %>% filter(module == "CGE2")
module_two = c(setdiff(mge_genes$gene_name, cge_genes$gene_name),
               setdiff(cge_genes$gene_name, mge_genes$gene_name))
```

```{r}
print(module_two[module_two %in% cge_genes$gene_name])
#print(module_two[module_two %in% mge_genes$gene_name])
```



```{r}
library(enrichR)
#devtools::install_github("wjawaid/enrichR")

dbs <-c('GO_Biological_Process_2021','GO_Cellular_Compponent_2021','GO_Molecular_Function_2021','LINCS_L1000_Chem_Pert_up','LINCS_L1000_Chem_Pert_down', 'WikiPathway_2021_Human', 'KEGG_2021_Human')

dbs <-c('GO_Biological_Process_2021','GO_Cellular_Compponent_2021','GO_Molecular_Function_2021', 'WikiPathway_2021_Human', 'KEGG_2021_Human')

# compute GO terms:
interneurons <- RunEnrichr(interneurons, dbs=dbs)

enrichrtable = GetEnrichrTable(interneurons)

# make GO term plots:
EnrichrBarPlot(
  interneurons,
  outdir = "~/src/IN_enrichr_plots",
  n_terms = 25, plot_size = c(4,16),
  logscale=TRUE
)

# enrichr dotplot
p <- EnrichrDotPlotCustom(
  interneurons, mods = mods[2:length(mods)],
  database = dbs[1], n_terms=5,
  break_ties=TRUE
)
```
```{r fig.width = 10, fig.height = 8}
p
```


```{r}
modules
```



```{r}
FeaturePlot(interneurons, features = "ERBB4", reduction = "umap.scv i")
```


```{r}
EnrichrDotPlotCustom <- function(
  seurat_obj, database, mods="all",
  n_terms = 3, break_ties=TRUE,
   logscale=TRUE, wgcna_name=NULL, ...
){

  # get data from active assay if wgcna_name is not given
  if(is.null(wgcna_name)){wgcna_name <- seurat_obj@misc$active_wgcna}

  # get modules:
  modules <- GetModules(seurat_obj, wgcna_name)

  # using all modules?
  #if(mods == 'all'){
  #  mods <- levels(modules$module)
  #  mods <- mods[mods != 'grey']
  #}

  # get Enrichr table
  enrichr_df <- GetEnrichrTable(seurat_obj, wgcna_name)

  # add color to enrich_table
  mod_colors <- dplyr::select(modules, c(module, color)) %>% dplyr::distinct()
  enrichr_df$color <- mod_colors[match(enrichr_df$module, mod_colors$module), 'color']

  # helper function to wrap text
  wrapText <- function(x, len) {
      sapply(x, function(y) paste(strwrap(y, len), collapse = "\n"), USE.NAMES = FALSE)
  }

  # get data to plot
  plot_df <- enrichr_df %>%
    subset(db == database & module %in% mods) %>%
    group_by(module) %>%
    top_n(n_terms, wt=Combined.Score)

  # sometimes top_n returns more than the desired number if there are ties. so here
  # we just randomly sample to break ties:
  if(break_ties){
    plot_df <- do.call(rbind, lapply(plot_df %>% group_by(module) %>% group_split, function(x){x[sample(n_terms),]}))
  }

  plot_df$Term <- wrapText(plot_df$Term, 45)

  # set modules factor and re-order:
  plot_df$module <- factor(
    as.character(plot_df$module),
    levels=levels(modules$module)
  )
  plot_df <- arrange(plot_df, module)

  # set Terms factor
  plot_df$Term <- factor(
    as.character(plot_df$Term),
    levels = unique(as.character(plot_df$Term))
  )

  # logscale?
  if(logscale){
    plot_df$Combined.Score <- log(plot_df$Combined.Score)
    lab <- 'Enrichment\nlog(combined score)'
    x <- 0.2
  } else{lab <- 'Enrichment\n(combined score)'; x <- 5}


  p <- plot_df  %>%
    ggplot(aes(x=module, y=Term)) +
    geom_point(aes(size=Combined.Score), color=plot_df$color) +
    RotatedAxis() +
    ylab('') + xlab('') + labs(size=lab) +
    scale_y_discrete(limits=rev) +
    ggtitle(database) +
    theme(
      plot.title = element_text(hjust = 0.5),
      axis.line.x = element_blank(),
      axis.line.y = element_blank(),
      panel.border = element_rect(colour = "black", fill=NA, size=1)
    )

  p
}
```


```{r}
plot_list <- OverlapBarPlot(overlap_df)

# stitch plots with patchwork
wrap_plots(plot_list, ncol=3)
```

```{r}
p <- EnrichrDotPlotCustom(
  interneurons, mods = c("Inh3", "Inh9", "Inh11", "Inh2"),
  database = dbs[1], n_terms=3,
  break_ties=TRUE
)
```

```{r fig.height = 9, fig.width = 7}
p #+ scale_x_discrete(c('Inh1', 'Inh12', 'Inh7', 'Inh4'))
```
```{r}
enrichrtable
```
```{r}
modules <- GetModules(seurat_mg)
mods <- levels(modules$module)
mods <- mods[mods!='grey']
module_colors <- modules %>% dplyr::select(c(module, color)) %>% distinct()
rownames(module_colors) <- module_colors$module
mod_colors <- module_colors[mods, 'color']
names(mod_colors) <- mods

# helper function to wrap text
wrapText <- function(x, len) {
    sapply(x, function(y) paste(strwrap(y, len), collapse = "\n"), USE.NAMES = FALSE)
}

selected_terms <- read.csv('data/AD_MG_enrichr_selected.csv')

# remove GO Term ID
selected_terms$Term <- str_replace(selected_terms$Term, " \\s*\\([^\\)]+\\)", "")

selected_terms <- selected_terms %>%
  group_by(module) %>%
  arrange(Combined.Score)

selected_terms$wrap <- wrapText(selected_terms$Term, 35)

idx = which(enrichrtable$Term %in% final_terms$Term)
selected_terms$Combined.Score = enrichrtable[]

p <- selected_terms  %>%
  ggplot(aes(x=log(Combined.Score), y=reorder(wrap, Combined.Score), fill=module))+
  geom_bar(stat='identity', position='identity', color='white') +
  geom_text(aes(label=wrap), x=.1, color='black', size=3.5, hjust='left') +
  #scale_fill_manual(values=mod_colors) +
  ylab('Term') + xlab('log(Enrichment)') +
  scale_x_continuous(expand = c(0, 0), limits = c(0, NA)) +
  theme(
    panel.grid.major=element_blank(),
    panel.grid.minor=element_blank(),
    legend.title = element_blank(),
    axis.ticks.y=element_blank(),
    axis.text.y=element_blank(),
    axis.line.y=element_blank(),
    plot.title = element_text(hjust = 0.5)
  )

pdf(paste0(fig_dir, 'MG_selected_GO_terms.pdf'), width= 6, height=7 , useDingbats=FALSE)
p + facet_wrap(~module, ncol=2, scales='free') + NoLegend()
dev.off()
```



FINAL DOTPLOTS


```{r}
final_terms = readxl::read_excel("~/my_genes.xlsx", col_names = FALSE)

# enrichr dotplot
p <- EnrichrDotPlot(
  en,
  database = final_terms$...1, n_terms=3,
  break_ties=TRUE
)
```
```{r}
# subset selected terms

final_terms$...2 = paste0("Inh", final_terms$...2)

colnames(final_terms) = c("Term", "modules")
final_terms$group = factor(final_terms$modules, levels = levels(selected_terms$group))

term_order = final_terms %>% arrange(group)

terms2 = strsplit(term_order$Term, split = "\\(GO:")
term_order$Term<- unlist(map(terms2, 1))

term_order$Term


selected_terms = final_terms
# remove GO Term ID
terms = strsplit(selected_terms$Term, split = "\\(GO:")
selected_terms$Term<- unlist(map(terms, 1))
selected_terms$go_id <- unlist(map(terms, 2))

selected_terms$score = -1
selected_terms$logp = -1

for(i in 1:nrow(selected_terms)){
  goid = selected_terms$go_id[i]
  ix = which(grepl(goid, enrichrtable$Term) & enrichrtable$module == selected_terms$modules[i])
  selected_terms$score[i] = enrichrtable$Combined.Score[ix]
  selected_terms$logp[i] <- enrichrtable$P.value[ix]
}

selected_terms <- selected_terms %>%
  arrange(group)


selected_terms$wrap <- wrapText(selected_terms$Term, 35)

selected_terms$Term <- factor(selected_terms$Term,
  levels = term_order$Term)

selected_terms$group = factor(selected_terms$group, 
                              levels = c("Inh1", "Inh12", "Inh7", "Inh4",
                                         "Inh8", "Inh5", "Inh6", "Inh9",
                                         "Inh10", "Inh3", "Inh2", "Inh11"))

# GO Term dot plot

p <- selected_terms %>%
  ggplot(aes(x = group, y = Term, color =logp, size=log(score))) +
  geom_point() +
  scale_color_stepsn(colors=rev(magma(256))) +
  RotatedAxis() + xlab('') + ylab('') +
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    panel.border = element_rect(size=1, color='black', fill=NA),
    axis.line.x = element_blank(),
    axis.line.y = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    plot.margin = margin(0,0,0,0),
    panel.grid = element_line(size=0.25, color='lightgrey')
  )

mod_ixs = match(levels(selected_terms$group), mods[mods!="grey"])

color_df <- data.frame(
  colour = new_colors[mod_ixs],
  group = mods[mods!="grey"][mod_ixs]
)

# make the colorbar as its own heatmap
color_df$var <- 1
cp <- color_df$colour; names(cp) <- color_df$group
colorbar <- color_df %>%
  ggplot(aes(x=factor(group, levels = levels(selected_terms$group)), y=var, fill=group)) +
  geom_tile() +
  scale_fill_manual(values=cp) +
  coord_equal() +
  NoLegend() + RotatedAxis() +
  theme(
    plot.title=element_blank(),
    axis.line=element_blank(),
    axis.ticks.y =element_blank(),
    axis.text.y = element_blank(),
    axis.title = element_blank(),
    plot.margin=margin(0,0,0,0),
  )
```


```{r fig.height = 6, fig.width = 10}
p / colorbar
```


```{r}
interneurons <- MetacellsByGroups(
  interneurons = interneurons,
  group.by = c("orig.ident"), # specify the columns in interneurons@meta.data to group by
  reduction = 'integrated.scvi', # select the dimensionality reduction to perform KNN on
  k = 25, # nearest-neighbors parameter
  max_shared = 10, # maximum number of shared cells between two metacells
  ident.group = 'orig.ident' # set the Idents of the metacell seurat object
)

interneurons = NormalizeMetacells(interneurons)

```

```{r}
interneurons <- NormalizeMetacells(interneurons)
interneurons = FindVariableFeatures(interneurons)
interneurons <- ScaleMetacells(interneurons, features=VariableFeatures(interneurons))
interneurons <- RunPCAMetacells(interneurons, features=VariableFeatures(interneurons))
interneurons <- RunHarmonyMetacells(interneurons, group.by.vars='orig.ident')
interneurons <- RunUMAPMetacells(interneurons, reduction='harmony', dims=1:15)


#p1 <- DimPlotMetacells(interneurons, group.by='scvi_class') + umap_theme() + ggtitle("Cell Type")
p2 <- DimPlotMetacells(interneurons, group.by='dataset') + umap_theme() + ggtitle("Sample")

p2
```



## Constructing Metacells
```{r}
# construct metacells  in each group
inter.exp_step3 = inter.exp_step3 %>% MetacellsByGroups(
  group.by = c("scvi_class", "orig.ident"), # specify the columns in interneurons@meta.data to group by
  k = 20, # nearest-neighbors parameter
  reduction = "umap.scvi",
  max_shared = 10, # maximum number of shared cells between two metacells
  ident.group = "scvi_class", # set the Idents of the metacell seurat object
)

# normalize metacell expression matrix:
inter.exp_step3 = NormalizeMetacells(inter.exp_step3)
```

## Process the Metacell Seurat Object
Optional step, but may be useful since metacells are pseudobulk cells with way less sparsity and noise than the original nuclei
```{r}
metacell_objnew <- GetMetacellObject(inter.exp_step3)

inter.exp_step3 <- NormalizeMetacells(inter.exp_step3)
inter.exp_step3 <- ScaleMetacells(inter.exp_step3, features=VariableFeatures(inter.exp_step3))
inter.exp_step3 <- RunPCAMetacells(inter.exp_step3, features=VariableFeatures(inter.exp_step3))
inter.exp_step3 <- RunUMAPMetacells(inter.exp_step3, reduction='pca', dims=1:20)


p1 <- DimPlotMetacells(inter.exp_step3, group.by='scvi_class') + umap_theme() + ggtitle("Cell Type")
p2 <- DimPlotMetacells(inter.exp_step3, group.by='dataset') + umap_theme() + ggtitle("Sample")

p2
```


## Co-expression network analysis
```{r}
interneurons = interneurons %>%  SetDatExpr(
  group_name = unique(interneurons$scvi_class), # the name of the group of interest in the group.by column
  group.by='scvi_class', # the metadata column containing the cell type info. This same column should have also been used in MetacellsByGroups
  assay = 'RNA', # using RNA assay
  slot = 'data' # using normalized data
)
```

## Select soft-power threshold
```{r}
# Test different soft powers:
interneurons <- TestSoftPowers(
  interneurons,
  networkType = 'signed' # you can also use "unsigned" or "signed hybrid"
)
```

```{r}
#interneurons = readRDS("/wynton/group/paredes/Aunoy/integrations_w_IPC/mgewgcna.rds")
# plot the results:
#plot_list <- PlotSoftPowers(interneurons)

# assemble with patchwork
wrap_plots(plot_list[[1]], ncol=2) + plot_annotation(
  title = 'Morabito & Miyoshi',theme = theme(plot.title = element_text(hjust=0.5)))

wrap_plots(plot_list[[2]], ncol=2) + plot_annotation(
  title = 'Mathys',theme = theme(plot.title = element_text(hjust=0.5)))

wrap_plots(plot_list[[3]], ncol=2) + plot_annotation(
  title = 'Zhou',theme = theme(plot.title = element_text(hjust=0.5)))

wrap_plots(plot_list[[4]], ncol=2) + plot_annotation(
  title = 'Zhou',theme = theme(plot.title = element_text(hjust=0.5)))
```
```{r}
PlotSoftPowers(interneurons)
```

## Construct co-expression network
```{r}
# construct co-expression network:
interneurons <- ConstructNetwork(
  interneurons, soft_power=4, #select the appropriate soft power determined in the previous code chunk
  setDatExpr=FALSE,
  tom_name = 'INTER', # name of the topoligical overlap matrix written to disk
  overwrite_tom = T 
)

PlotDendrogram(interneurons, main='topo_1 hdWGCNA Dendrogram')
```

```{r}
saveRDS(inter.exp_step3, "/wynton/group/paredes/Aunoy/interexpstep3.rds")
```


## Topological Overlap Matrix (TOM)
```{r}
TOM <- GetTOM(interneurons)
```

```{r}
TOM
```


## Compute module eigengenes
```{r}
# compute all MEs in the full single-cell dataset
interneurons <- ModuleEigengenes(
 interneurons,
 exclude_grey = T
)
```
```{r}
saveRDS(inter.exp_step3, "/wynton/group/paredes/Aunoy/interexpstep3.rds")
```

```{r}
hMEs <- GetMEs(interneurons)
```


## Compute module connectivity
```{r}
# compute eigengene-based connectivity (kME):
interneurons <- ModuleConnectivity(
  interneurons,
  group.by = 'scvi_fate', 
  group_name = 'Interneurons'
)

# rename the modules
inter.exp_step3 <- ResetModuleNames(
  inter.exp_step3,
  new_name = "INH-M"
)

# plot genes ranked by kME for each module
p <- PlotKMEs(interneurons, ncol=7, text_size = 4)

for(m in 1:2) {
  wrap_plots(p[[m]])
  ggsave(paste0("plots/module-connectivity_M", m, ".png"), width = 4, height = 4, scale = 1)
}
```
```{r}
PlotKMEs(interneurons, ncol=2, text_size = 4)
```


## Getting the module assignment table
```{r}
# get the module assignment table:
modules <- GetModules(interneurons)

# show the first rows:
head(modules)

# get hub genes
hub_df <- GetHubGenes(interneurons, n_hubs = 200)

#Exporting as an excel file:
hub_df = hub_df %>% mutate(paper_module = module)
hub_df = hub_df %>% arrange(paper_module, -kME) %>% select(paper_module, gene_name, kME)
colnames(hub_df) = c("module", "gene", "kME")
#write_xlsx(hub_df, path = "wgcna_modules_genes.xlsx")
```

Straight from Marcos

```{r}
inter.exp_cds = SeuratWrappers::as.cell_data_set(interneurons)

# Transfer Seurat UMAP embeddings
inter.exp_cds@int_colData@listData$reducedDims$UMAP <- interneurons@reductions$umap.scvi@cell.embeddings
plot_cells(inter.exp_cds)

inter.exp_cds = cluster_cells(reduction_method = "UMAP", cluster_method = "louvain", inter.exp_cds, k = 50)
plot_cells(inter.exp_cds, color_cells_by = "cluster")
plot_cells(inter.exp_cds, color_cells_by = "partition")

rec.part <- c(rep(1, length(inter.exp_cds@colData@rownames)))
rec.part[inter.exp_cds@clusters$UMAP$clusters == "43"] = 2
names(rec.part) <- inter.exp_cds@colData@rownames
rec.part <- as.factor(rec.part)

inter.exp_cds@clusters$UMAP$partitions <- rec.part

inter.exp_cds = learn_graph(inter.exp_cds, verbose = TRUE, close_loop = T, 
                            learn_graph_control = list(nn.k = 10,
                                                       minimal_branch_len = 10,
                                                       euclidean_distance_ratio = 3, 
                                                       geodesic_distance_ratio = 1))

```

```{r}
plot_cells(cds,#inter.exp_cds,
           color_cells_by = "cluster",
           label_groups_by_cluster=FALSE,
           label_leaves=F,
           label_branch_points=F,
           label_roots = F,
           trajectory_graph_color = "cyan") + 
  coord_fixed()
```
```{r}
plot_cells(inter.exp_cds, color_cells_by = "dataset")
```

```{r}
saveRDS(inter.exp_cds, "/wynton/group/paredes/Aunoy/FINAL_CDS_MONOCLE.rds")
```

```{r}
inter.exp_cds <- order_cells(inter.exp_cds)

```

```{r}
plot_cells(inter.exp_cds,
           color_cells_by = "pseudotime",
           label_cell_groups=FALSE,
           label_leaves=FALSE,
           label_branch_points=FALSE,
           label_roots = F,
           trajectory_graph_segment_size = 0.7,
           trajectory_graph_color = "cyan",
           graph_label_size=1.5) + 
  scale_color_viridis(name = "Pseudotime")+
  coord_fixed() +
  NoAxes() + 
  theme(legend.position = "bottom")
```
### So what I want to do is to find transcription factors enriched
### in specific clusters

TF Genes


```{r}
### So four way venn diagram
keys = c("Inh CGE", "Inh MGE", "Inh LGE", "Inh CGE/LGE")
pairwise = combn(keys, 2)

df_list = list()

for(n in 1:ncol(pairwise)){
  markers = FindMarkers(interneurons, group.by = "class", ident.1 = pairwise[1, n],
                        ident.2 = pairwise[2, n])
  df_list[[n]] = markers
}
```

```{r}
FeaturePlot(interneurons, reduction = "umap.scvi", features = "PROX1")
```


```{r}
get_gene_list_from_DEG = function(df_list, key, pairings, threshold = 0.01){
   relev_compars_a = which(key == pairings[1, ])
   relev_compars_b = which(key == pairings[2, ])
   
   gene_list = c()
   
   for(n in relev_compars_a){
     curr_df = df_list[[n]]
     curr_df = curr_df %>% filter(avg_log2FC > 0) %>%
       filter(p_val_adj < 0.05) %>% filter(pct.1 > threshold)
     gene_list = c(gene_list, rownames(curr_df))
   }
   
   for(n in relev_compars_b){
     curr_df = df_list[[n]]
     curr_df = curr_df %>% filter(avg_log2FC < 0) %>%
       filter(p_val_adj < 0.05) %>% filter(pct.2 > threshold)
     gene_list = c(gene_list, rownames(curr_df))
   }
   
   gene_list = gene_list[!duplicated(gene_list)]
   return(gene_list)
}



MGE_Only = get_gene_list_from_DEG(df_list, "Inh MGE", pairwise, threshold = 0.1)
CGE_Only = get_gene_list_from_DEG(df_list, "Inh CGE", pairwise, threshold = 0.1)
LGE_Only= get_gene_list_from_DEG(df_list, "Inh LGE", pairwise, threshold = 0.1)
CGELGE_Only = get_gene_list_from_DEG(df_list, "Inh CGE/LGE", pairwise, threshold = 0.1)

```

```{r}
tfs = read_table("~/TF_names_v_1.01.txt", col_names = FALSE)
tfs = tfs$X1
```
```{r}
MGE_TFs = MGE_Only[MGE_Only %in% tfs]
CGE_TFs = CGE_Only[CGE_Only %in% tfs]
LGE_TFs = LGE_Only[LGE_Only %in% tfs]
CGELGE_TFs = CGELGE_Only[CGELGE_Only %in% tfs]
```


```{r}
receptor_genes = read_tsv("~/receptor.tsv")
```


```{r}
nmig_genes = read_table("~/nmig_genes.txt", col_names = FALSE)
nmig_genes = toupper(nmig_genes$X2)
nmig_genes = c(nmig_genes, "SEMA3A", "SEMA3B", "SEMA3C", "SEMA3D", "SEMA3E", "SEMA3F", "SEMA3G",
                 "SEMA4A", "SEMA4B", "SEMA4C", "SEMA4D", "SEMA4F", "SEMA4G",
                 "SEMA5A", "SEMA5B",
                 "SEMA6A", "SEMA6B", "SEMA6C", "SEMA6D",
                 "SEMA7A", 'NRP1', 'NRP2', 'PLXNA1', 'PLXNA2', 'PLXNA3', 'PLXNA4',
               'PLXNB1', 'PLXNB2', 'PLXNB3', 'PLXNC1', 'PLXND1', 'SLIT1', 'SLIT2', 'ROBO1', 'ROBO2',
               'ROBO3', "LRP8", "VLDLR", 'HGF','BDNF','NTF4')
```

```{r}
MGE_Mig = MGE_Only[MGE_Only %in% nmig_genes]
CGE_Mig = CGE_Only[CGE_Only %in% nmig_genes]
LGE_Mig = LGE_Only[LGE_Only %in% nmig_genes]
CGELGE_Mig = CGELGE_Only[CGELGE_Only %in% nmig_genes]
```



CGE_Only
LGE_Only
MGE_Only
CGELGE_Only

CGE_LGE
CGE_MGE



https://stackoverflow.com/questions/56551261/what-is-the-best-way-to-find-all-possible-intersections-of-multiple-sets
```{r}
sets = list(CGE_TFs, MGE_TFs, LGE_TFs, CGELGE_TFs)
for (comboSize in 2:length(sets)){
  combos = combn(1:length(sets), comboSize)
  for(i in 1:ncol(combos)){
    intersection = sets[[combos[1, i]]]
    for(j in 2:nrow(combos)){
      intersection = intersect(intersection, sets[[combos[j, i]]])
    }
    print(paste0("Intersection of ", keys[combos[, i]]))
    #intersection = intersection[!intersection %in% sets[[(1:length(sets))[!(1:length(sets)) 
                                                                       #   %in% combos[, 1]]]]]
    intersection = intersection[!intersection %in% interneuron_genes$genes]
    print(length(intersection))
  }
}

```

interneuron genes
=  "DLX6-AS1" "MYT1L"    "SOX11"    "SOX4"     "ZNF704"   "ZEB2"     "SETBP1"   "PBX1"     "TCF4"     "NFIB"     "FOXN3"    "TCF12"    "GTF2I"  
13





402 genes

```{r}
cons = FindConservedMarkers(interneurons, grouping.var = "class", ident.1 = c("Inh CGE", "Inh MGE"))
```


```{r}
human_arc = JoinLayers(human_arc)
interneuron_markers = FindMarkers(human_arc, group.by = "class", ident.1 = c("Inh CGE", "Inh MGE", "Inh LGE", "Inh CGE/LGE"))
remove(human_arc)
```

```{r}
yap %>%
  filter(avg_log2FC > 1) %>%
  ggplot(aes(x = pct.1)) +
  geom_histogram()
```
```{r}
interneuron_markers$genes = rownames(interneuron_markers)
interneuron_genes = interneuron_markers %>%
  filter(avg_log2FC > 2) %>%
  filter(pct.1 > 0.75) %>%
  #filter(pct.2 < 0.50) %>%
  dplyr::select(genes)
```


```{r}
tfs = c(tfs, paste0(tfs, "-AS1"))
int_tfs = interneuron_genes$genes[interneuron_genes$genes %in% tfs]
all_genes = unique(c(CGE_TFs, MGE_TFs, LGE_TFs, CGELGE_TFs, int_tfs))

gene_df = as.data.frame(matrix(data = 0, nrow = length(all_genes), ncol = 4))
rownames(gene_df) = all_genes 
colnames(gene_df) = keys
gene_df[rownames(gene_df) %in% int_tfs, ]= c(1, 1, 1, 1)
gene_df$`Inh CGE`[rownames(gene_df) %in% CGE_TFs] = 1
gene_df$`Inh MGE`[rownames(gene_df) %in% MGE_TFs] = 1
gene_df$`Inh LGE`[rownames(gene_df) %in% LGE_TFs] = 1
gene_df$`Inh CGE/LGE`[rownames(gene_df) %in% CGELGE_TFs] = 1
```


```{r}
cge_genes = rownames(gene_df)[gene_df$`Inh CGE` == 1 & gene_df$`Inh MGE` == 0 & 
                    gene_df$`Inh LGE` == 0 & gene_df$`Inh CGE/LGE` == 0]

mge_genes = rownames(gene_df)[gene_df$`Inh MGE` == 1 & gene_df$`Inh CGE` == 0 & 
                    gene_df$`Inh LGE` == 0 & gene_df$`Inh CGE/LGE` == 0]

lge_genes = rownames(gene_df)[gene_df$`Inh LGE` == 1 & gene_df$`Inh MGE` == 0 & 
                    gene_df$`Inh CGE` == 0 & gene_df$`Inh CGE/LGE` == 0]

cgelge_genes = rownames(gene_df)[gene_df$`Inh CGE/LGE` == 1 & gene_df$`Inh MGE` == 0 & 
                    gene_df$`Inh LGE` == 0 & gene_df$`Inh CGE` == 0]

cm= rownames(gene_df)[gene_df$`Inh CGE` == 1 & gene_df$`Inh MGE` == 1 & 
                    gene_df$`Inh LGE` == 0 & gene_df$`Inh CGE/LGE` == 0]

cl= rownames(gene_df)[gene_df$`Inh CGE` == 1 & gene_df$`Inh MGE` == 0 & 
                    gene_df$`Inh LGE` == 1 & gene_df$`Inh CGE/LGE` == 0]

cz= rownames(gene_df)[gene_df$`Inh CGE` == 1 & gene_df$`Inh MGE` == 0 & 
                    gene_df$`Inh LGE` == 0 & gene_df$`Inh CGE/LGE` == 1]

ml= rownames(gene_df)[gene_df$`Inh CGE` == 0 & gene_df$`Inh MGE` == 1 & 
                    gene_df$`Inh LGE` == 1 & gene_df$`Inh CGE/LGE` == 0]

mz= rownames(gene_df)[gene_df$`Inh CGE` == 0 & gene_df$`Inh MGE` == 1 & 
                    gene_df$`Inh LGE` == 0 & gene_df$`Inh CGE/LGE` == 1]

lz= rownames(gene_df)[gene_df$`Inh CGE` == 0 & gene_df$`Inh MGE` == 0 & 
                    gene_df$`Inh LGE` == 1 & gene_df$`Inh CGE/LGE` == 1]

cml= rownames(gene_df)[gene_df$`Inh CGE` == 1 & gene_df$`Inh MGE` == 1 & 
                    gene_df$`Inh LGE` == 1 & gene_df$`Inh CGE/LGE` == 0]

cmz= rownames(gene_df)[gene_df$`Inh CGE` == 1 & gene_df$`Inh MGE` == 1 & 
                    gene_df$`Inh LGE` == 0 & gene_df$`Inh CGE/LGE` == 1]

clz= rownames(gene_df)[gene_df$`Inh CGE` == 1 & gene_df$`Inh MGE` == 0 & 
                    gene_df$`Inh LGE` == 1 & gene_df$`Inh CGE/LGE` == 1]

mlz= rownames(gene_df)[gene_df$`Inh CGE` == 0 & gene_df$`Inh MGE` == 1 & 
                    gene_df$`Inh LGE` == 1 & gene_df$`Inh CGE/LGE` == 1]

```


```{r}
all_genes[!all_genes %in% c(cge_genes, lge_genes, mge_genes, cgelge_genes,
         cm, cl, cz, ml, mz, lz, cml, cmz, mlz, int_tfs, clz)]
```


```{r}
length(c(cge_genes, lge_genes, mge_genes, cgelge_genes,
         cm, cl, cz, ml, mz, lz, cml, cmz, mlz, int_tfs, clz))
```

CGE = 11
MGE = 19
LGE = 99
ZGE = 60

CM = 6
CL = 4
CZ = 26
ML = 10
MZ = 8
LZ = 71

CML = 16
CMZ = 39
CLZ = 25
MLZ = 5

all = 3

```{r}
#tfs = c(tfs, paste0(tfs, "-AS1"))
#int_tfs = interneuron_genes$genes[interneuron_genes$genes %in% tfs]
all_genes = unique(c(CGE_Mig, LGE_Mig, MGE_Mig, CGELGE_Mig))

gene_df = as.data.frame(matrix(data = 0, nrow = length(all_genes), ncol = 4))
rownames(gene_df) = all_genes 
colnames(gene_df) = keys
#gene_df[rownames(gene_df) %in% int_tfs, ]= c(1, 1, 1, 1)
gene_df$`Inh CGE`[rownames(gene_df) %in% CGE_Mig] = 1
gene_df$`Inh MGE`[rownames(gene_df) %in% MGE_Mig] = 1
gene_df$`Inh LGE`[rownames(gene_df) %in% LGE_Mig] = 1
gene_df$`Inh CGE/LGE`[rownames(gene_df) %in% CGELGE_Mig] = 1
```


```{r}
cge_genes = rownames(gene_df)[gene_df$`Inh CGE` == 1 & gene_df$`Inh MGE` == 0 & 
                    gene_df$`Inh LGE` == 0 & gene_df$`Inh CGE/LGE` == 0]

mge_genes = rownames(gene_df)[gene_df$`Inh MGE` == 1 & gene_df$`Inh CGE` == 0 & 
                    gene_df$`Inh LGE` == 0 & gene_df$`Inh CGE/LGE` == 0]

lge_genes = rownames(gene_df)[gene_df$`Inh LGE` == 1 & gene_df$`Inh MGE` == 0 & 
                    gene_df$`Inh CGE` == 0 & gene_df$`Inh CGE/LGE` == 0]

cgelge_genes = rownames(gene_df)[gene_df$`Inh CGE/LGE` == 1 & gene_df$`Inh MGE` == 0 & 
                    gene_df$`Inh LGE` == 0 & gene_df$`Inh CGE` == 0]

cm= rownames(gene_df)[gene_df$`Inh CGE` == 1 & gene_df$`Inh MGE` == 1 & 
                    gene_df$`Inh LGE` == 0 & gene_df$`Inh CGE/LGE` == 0]

cl= rownames(gene_df)[gene_df$`Inh CGE` == 1 & gene_df$`Inh MGE` == 0 & 
                    gene_df$`Inh LGE` == 1 & gene_df$`Inh CGE/LGE` == 0]

cz= rownames(gene_df)[gene_df$`Inh CGE` == 1 & gene_df$`Inh MGE` == 0 & 
                    gene_df$`Inh LGE` == 0 & gene_df$`Inh CGE/LGE` == 1]

ml= rownames(gene_df)[gene_df$`Inh CGE` == 0 & gene_df$`Inh MGE` == 1 & 
                    gene_df$`Inh LGE` == 1 & gene_df$`Inh CGE/LGE` == 0]

mz= rownames(gene_df)[gene_df$`Inh CGE` == 0 & gene_df$`Inh MGE` == 1 & 
                    gene_df$`Inh LGE` == 0 & gene_df$`Inh CGE/LGE` == 1]

lz= rownames(gene_df)[gene_df$`Inh CGE` == 0 & gene_df$`Inh MGE` == 0 & 
                    gene_df$`Inh LGE` == 1 & gene_df$`Inh CGE/LGE` == 1]

cml= rownames(gene_df)[gene_df$`Inh CGE` == 1 & gene_df$`Inh MGE` == 1 & 
                    gene_df$`Inh LGE` == 1 & gene_df$`Inh CGE/LGE` == 0]

cmz= rownames(gene_df)[gene_df$`Inh CGE` == 1 & gene_df$`Inh MGE` == 1 & 
                    gene_df$`Inh LGE` == 0 & gene_df$`Inh CGE/LGE` == 1]

clz= rownames(gene_df)[gene_df$`Inh CGE` == 1 & gene_df$`Inh MGE` == 0 & 
                    gene_df$`Inh LGE` == 1 & gene_df$`Inh CGE/LGE` == 1]

mlz= rownames(gene_df)[gene_df$`Inh CGE` == 0 & gene_df$`Inh MGE` == 1 & 
                    gene_df$`Inh LGE` == 1 & gene_df$`Inh CGE/LGE` == 1]

```


```{r}
all_genes[!all_genes %in% c(cge_genes, lge_genes, mge_genes, cgelge_genes,
         cm, cl, cz, ml, mz, lz, cml, cmz, mlz, int_tfs, clz)]
```


```{r}
length(c(cge_genes, lge_genes, mge_genes, cgelge_genes,
         cm, cl, cz, ml, mz, lz, cml, cmz, mlz, int_tfs, clz))
```


```{r}
cds = as.cell_data_set(merged)
```
## Need to add partition, cluster, and umap embedding
```{r}
### 
rec.part <- c(rep(1, length(cds@colData@rownames)))
names(rec.part) <- cds@colData@rownames
rec.part <- as.factor(rec.part)
```

```{r}
cds@clusters$UMAP$partitions <- rec.part
```

```{r}
list_cluster <- interneurons$scvi_clusters#Idents(human_arc[, Idents(human_arc) %in% groups])
cds@clusters$UMAP$clusters <- list_cluster
```

```{r}
#cds@int_colData@listData$reducedDims$UMAP
cds@int_colData@listData$reducedDims$UMAP = cds@int_colData@listData$reducedDims$UMAP.SCVI
```